### 2019-05-31 paper.tex
Add AAS Template

%%
%% Beginning of file 'paper.tex'
%%
%% Modified 2018 January
%%
%% This is a sample manuscript marked up using the
%% AASTeX v6.2 LaTeX 2e macros.
%%
%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
%% (Copyright 2000-2015).  See the classfile for details.

%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
%% All of these external packages should already be present in the modern TeX 
%% distributions.  If not they can also be obtained at www.ctan.org.

%% The first piece of markup in an AASTeX v6.x document is the \documentclass
%% command. LaTeX will ignore any data that comes before this command. The 
%% documentclass can take an optional argument to modify the output style.
%% The command below calls the preprint style  which will produce a tightly 
%% typeset, one-column, single-spaced document.  It is the default and thus
%% does not need to be explicitly stated.
%%
%%
%% using aastex version 6.2
\documentclass{aastex62}

%% The default is a single spaced, 10 point font, single spaced article.
%% There are 5 other style options available via an optional argument. They
%% can be envoked like this:
%%
%% \documentclass[argument]{aastex62}
%% 
%% where the layout options are:
%%
%%  twocolumn   : two text columns, 10 point font, single spaced article.
%%                This is the most compact and represent the final published
%%                derived PDF copy of the accepted manuscript from the publisher
%%  manuscript  : one text column, 12 point font, double spaced article.
%%  preprint    : one text column, 12 point font, single spaced article.  
%%  preprint2   : two text columns, 12 point font, single spaced article.
%%  modern      : a stylish, single text column, 12 point font, article with
%% 		  wider left and right margins. This uses the Daniel
%% 		  Foreman-Mackey and David Hogg design.
%%  RNAAS       : Preferred style for Research Notes which are by design 
%%                lacking an abstract and brief. DO NOT use \begin{abstract}
%%                and \end{abstract} with this style.
%%
%% Note that you can submit to the AAS Journals in any of these 6 styles.
%%
%% There are other optional arguments one can envoke to allow other stylistic
%% actions. The available options are:
%%
%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
%%  tighten      : Makes baselineskip slightly smaller, only works with 
%%                 the twocolumn substyle.
%%  times        : uses times font instead of the default
%%  linenumbers  : turn on lineno package.
%%  trackchanges : required to see the revision mark up and print its output
%%  longauthor   : Do not use the more compressed footnote style (default) for 
%%                 the author/collaboration/affiliations. Instead print all
%%                 affiliation information after each name. Creates a much
%%                 long author list but may be desirable for short author papers
%%
%% these can be used in any combination, e.g.
%%
%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
%%
%% AASTeX v6.* now includes \hyperref support. While we have built in specific
%% defaults into the classfile you can manually override them with the
%% \hypersetup command. For example,
%%
%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
%%
%% will change the color of the internal links to red, the links to the
%% bibliography to green, the file links to cyan, and the external links to
%% magenta. Additional information on \hyperref options can be found here:
%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
%%
%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
\newcommand{\vdag}{(v)^\dagger}
\newcommand\aastex{AAS\TeX}
\newcommand\latex{La\TeX}

%% Tells LaTeX to search for image files in the 
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figures/}}

%% Reintroduced the \received and \accepted commands from AASTeX v5.2
\received{January 1, 2018}
\revised{January 7, 2018}
\accepted{\today}
%% Command to document which AAS Journal the manuscript was submitted to.
%% Adds "Submitted to " the arguement.
\submitjournal{ApJ}

%% Mark up commands to limit the number of authors on the front page.
%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
%% an author in this case.
%
%\AuthorCollaborationLimit=3
%
%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
%% collaboration" on the front page of this example manuscript.
%%
%% Note that all of the author will be shown in the published article.
%% This feature is meant to be used prior to acceptance to make the
%% front end of a long author article more manageable. Please do not use
%% this functionality for manuscripts with less than 20 authors. Conversely,
%% please do use this when the number of authors exceeds 40.
%%
%% Use \allauthors at the manuscript end to show the full author list.
%% This command should only be used with \AuthorCollaborationLimit is used.

%% The following command can be used to set the latex table counters.  It
%% is needed in this document because it uses a mix of latex tabular and
%% AASTeX deluxetables.  In general it should not be needed.
%\setcounter{table}{1}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%
%% The following section outlines numerous optional output that
%% can be displayed in the front matter or as running meta-data.
%%
%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
\shorttitle{Sample article}
\shortauthors{Schwarz et al.}
%%
%% You can add a light gray and diagonal water-mark to the first page 
%% with this command:
% \watermark{text}
%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
%% long you can control the water-mark size with:
%  \setwatermarkfontsize{dimension}
%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document}

\title{EinsteinPy: Python for General Relativity\footnote{Released on January, 8th, 2018}}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire. In v6.2 you can include a footnote in the title.

%% A significant change from earlier AASTEX versions is in the structure for 
%% calling author and affilations. The change was necessary to implement 
%% autoindexing of affilations which prior was a manual process that could 
%% easily be tedious in large author manuscripts.
%%
%% The \author command is the same as before except it now takes an optional
%% arguement which is the 16 digit ORCID. The syntax is:
%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
%%
%% This will hyperlink the author name to the author's ORCID page. Note that
%% during compilation, LaTeX will do some limited checking of the format of
%% the ID to make sure it is valid.
%%
%% Use \affiliation for affiliation information. The old \affil is now aliased
%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
%% When a duplicate is found its index will be the same as its previous entry.
%%
%% Note that \altaffilmark and \altaffiltext have been removed and thus 
%% can not be used to document secondary affiliations. If they are used latex
%% will issue a specific error message and quit. Please use multiple 
%% \affiliation calls for to document more than one affiliation.
%%
%% The new \altaffiliation can be used to indicate some secondary information
%% such as fellowships. This command produces a non-numeric footnote that is
%% set away from the numeric \affiliation footnotes.  NOTE that if an
%% \altaffiliation command is used it must come BEFORE the \affiliation call,
%% right after the \author command, in order to place the footnotes in
%% the proper location.
%%
%% Use \email to set provide email addresses. Each \email will appear on its
%% own line so you can put multiple email address in one \email call. A new
%% \correspondingauthor command is available in V6.2 to identify the
%% corresponding author of the manuscript. It is the author's responsibility
%% to make sure this name is also in the author list.
%%
%% While authors can be grouped inside the same \author and \affiliation
%% commands it is better to have a single author for each. This allows for
%% one to exploit all the new benefits and should make book-keeping easier.
%%
%% If done correctly the peer review system will be able to
%% automatically put the author and affiliation information from the manuscript
%% and save the corresponding author the trouble of entering it by hand.

\correspondingauthor{Shreyas Bapat}
\email{shreyas@einsteinpy.org, bapat.shreyas@gmail.com}

\author[0000-0002-0870-4665]{Shreyas Bapat}
\affil{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
Mandi, Himachal Pradesh, 175005, India}

\author{August Muench}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}
\collaboration{(AAS Journals Data Scientists collaboration)}

\author{Butler Burton}
\affiliation{National Radio Astronomy Observatory}
\affiliation{AAS Journals Associate Editor-in-Chief}
\nocollaboration

\author{Amy Hendrickson}
\altaffiliation{Creator of AASTeX v6.2}
\affiliation{TeXnology Inc.}
\collaboration{(LaTeX collaboration)}

\author{Julie Steffen}
\affiliation{AAS Director of Publishing}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}

\author{Jeff Lewandowski}
\affiliation{IOP Senior Publisher for the AAS Journals}
\affiliation{IOP Publishing, Washington, DC 20005}

%% Note that the \and command from previous versions of AASTeX is now
%% depreciated in this version as it is no longer necessary. AASTeX 
%% automatically takes care of all commas and "and"s between authors names.

%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
%% provide the collaboration status of a group of authors. These commands 
%% can be used either before or after the list of corresponding authors. The
%% argument for \collaboration is the collaboration identifier. Authors are
%% encouraged to surround collaboration identifiers with ()s. The 
%% \nocollaboration command takes no argument and exists to indicate that
%% the nearby authors are not part of surrounding collaborations.

%% Mark off the abstract in the ``abstract'' environment. 
\begin{abstract}

This example manuscript is intended to serve as a tutorial and template for
authors to use when writing their own AAS Journal articles. The manuscript
includes a history of \aastex\ and documents the new features in the
previous versions as well as the new features in version 6.2. This
manuscript includes many figure and table examples to illustrate these new
features.  Information on features not explicitly mentioned in the article
can be viewed in the manuscript comments or more extensive online
documentation. Authors are welcome replace the text, tables, figures, and
bibliography with their own and submit the resulting manuscript to the AAS
Journals peer review system.  The first lesson in the tutorial is to remind
authors that the AAS Journals, the Astrophysical Journal (ApJ), the
Astrophysical Journal Letters (ApJL), and Astronomical Journal (AJ), all
have a 250 word limit for the abstract\footnote{Note that manuscripts 
submitted to the new Research Notes of the American Astronomical Society 
(RNAAS) do \textbf{not} have abstracts.}.  If you exceed this length the
Editorial office will ask you to shorten it.

\end{abstract}

%% Keywords should appear after the \end{abstract} command. 
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{editorials, notices --- 
miscellaneous --- catalogs --- surveys}

%% From the front matter, we move on to the body of the paper.
%% Sections are demarcated by \section and \subsection, respectively.
%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.
%%
%% We recommend that authors also use the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below.

\section{Introduction} \label{sec:intro}

\latex\ \footnote{\url{http://www.latex-project.org/}} is a document markup
language that is particularly well suited for the publication of
mathematical and scientific articles \citep{lamport94}. \latex\ was written
in 1985 by Leslie Lamport who based it on the \TeX\ typesetting language
which itself was created by Donald E. Knuth in 1978.  In 1988 a suite of
\latex\ macros were developed to investigate electronic submission and
publication of AAS Journal articles \citep{1989BAAS...21..780H}.  Shortly
afterwards, Chris Biemesdefer merged these macros and more into a \latex\
2.08 style file called \aastex.  These early \aastex\ versions introduced
many common commands and practices that authors take for granted today.
Substantial revisions
were made by Lee Brotzman and Pierre Landau when the package was updated to
v4.0.  AASTeX v5.0, written in 1995 by Arthur Ogawa, upgraded to \latex\ 2e
which uses the document class in lieu of a style file.  Other improvements
to version 5 included hypertext support, landscape deluxetables and
improved figure support to facilitate electronic submission.  
\aastex\ v5.2 was released in 2005 and introduced additional graphics
support plus new mark up to identifier astronomical objects, datasets and
facilities.

In 1996 Maxim Markevitch modified the AAS preprint style file, aaspp4.sty,
to closely emulate the very tight, two column style of a typeset
Astrophysical Journal article.  The result was emulateapj.sty.  A year
later Alexey Vikhlinin took over development and maintenance.  In 2001 he
converted emulateapj into a class file in \latex\ 2e and in 2003 Vikhlinin
completely rewrote emulateapj based on the APS Journal's RevTEX class.

During this time emulateapj gained growing acceptance in the astronomical
community as it filled an author need to obtain an approximate number of
manuscript pages prior to submission for cost and length estimates. The
tighter typeset also had the added advantage of saving paper when printing
out hard copies.

Even though author publication charges are no longer based on print pages
\footnote{see Section \ref{sec:pubcharge} in the Appendix for more details
about how current article costs are calculated.} the emulateapj class file
has proven to be extremely popular with AAS Journal authors.  An informal
analysis of submitted \latex\ manuscripts in 2015 revealed that $\sim$65\%
either called emulateapj or have a commented emulateapj classfile call
indicating it was used at some stage of the manuscript construction.
Clearly authors want to have access to a tightly typeset version of the
article when corresponding with co-authors and for preprint submissions.

When planning the next \aastex\ release the popularity of emulateapj played
an important roll in the decision to drop the old base code and adopt and
modify emulateapj for \aastex\ v6.+ instead.  The change brings \aastex\
inline with what the majority of authors are already using while still
delivering new and improved features.  \aastex\ v6.0 through v6.2 were written
by Amy Hendrickson and released in January 2016 (v6.0), October 2016 (v6.1),
and January 2018 (v6.2), respectively.  Some of the new features in v6.0 
included:

\begin{enumerate}
\item improved citations for third party data repositories and software,
\item easier construction of matrix figures consisting of multiple 
encapsulated postscript (EPS) or portable document format (PDF) files,
\item figure set mark up for large collections of similar figures,
\item color mark up to easily enable/disable revised text highlighting,
\item improved url support, and
\item numerous table options such as the ability to hide columns, column 
decimal alignment, automatic column math mode and numbering, plus splitting of
wide tables.
\end{enumerate}

The features in v6.1 were:

\begin{enumerate}
\item ORCID support for preprints,
\item improved author, affiliation and collaboration mark up,
\item reintroduced the old AASTeX v5.2 {\tt\string\received}, 
      {\tt\string\revised}, {\tt\string\accepted}, and
      {\tt\string\published} commands plus
      added the new {\tt\string\submitjournal} command to document
      which AAS Journal the manuscript was submitted to, plus
\item new typeset style options.
\end{enumerate}

The new features in v6.2 are:

\begin{enumerate}
\item A new RNAAS style option for Research Note manuscripts,
\item Titles no longer put in all caps,
\item No page skip between the title page and article body,
\item re-introduce RevTeX's widetext environment for long lines in
      two column style formats, and
\item upgrade to the {\tt\string\doi} command.
\end{enumerate}

The rest of this article provides information and examples on how to create
your own AAS Journal manuscript with v6.2.  Special emphasis is placed on
how to use the full potential of \aastex\ v6+.  The next section describes
the different manuscript styles available and how they differ from past
releases.  Section \ref{sec:floats} describes how tables and figures are
placed in a \latex\ document. Specific examples of tables, Section
\ref{subsec:tables}, and figures, Section \ref{subsec:figures}, are also
provided.  Section \ref{sec:displaymath} discusses how to display math and
incorporate equations in a manuscript while Section \ref{sec:highlight}
discuss how to use the new revision mark up.  The last section,
\ref{sec:cite}, shows how recognize software and external data as first
class references in the manuscript bibliography.  An appendix is included
to show how to construct one and provide some information on how article
charges are calculated.  Additional information is available both embedded
in the comments of this \latex\ file and in the online documentation at
\url{http://journals.aas.org/authors/aastex.html}.

\section{Manuscript styles} \label{sec:style}

The default style in \aastex\ v6.2 is a tight single column style, e.g.  10
point font, single spaced.  The single column style is very useful for
article with wide equations. It is also the easiest to style to work with
since figures and tables, see Section \ref{sec:floats}, will span the
entire page, reducing the need for address float sizing.

To invoke a two column style similar to the what is produced in
the published PDF copy use \\

\noindent {\tt\string\documentclass[twocolumn]\{aastex62\}}. \\

\noindent Note that in the two column style figures and tables will only
span one column unless specifically ordered across both with the ``*'' flag,
e.g. \\

\noindent{\tt\string\begin\{figure*\}} ... {\tt\string\end\{figure*\}}, \\
\noindent{\tt\string\begin\{table*\}} ... {\tt\string\end\{table*\}}, and \\
\noindent{\tt\string\begin\{deluxetable*\}} ... {\tt\string\end\{deluxetable*\}}. \\

\noindent This option is ignored in the onecolumn style.

Some other style options are outlined in the commented sections of this 
article.  Any combination of style options can be used.

Two style options that are needed to fully use the new revision tracking
feature, see Section \ref{sec:highlight}, are {\tt\string linenumbers} which 
uses the lineno style file to number each article line in the left margin and 
{\tt\string trackchanges} which controls the revision and commenting highlight
output.

There is also a new {\tt\string modern} option that uses a Daniel
Foreman-Mackey and David Hogg design to produce stylish, single column
output that has wider left and right margins. It is designed to have fewer
words per line to improve reader retention. It also looks better on devices
with smaller displays such as smart phones.

For a Research Note use the {\tt\string RNAAS} option which will produce a
manuscript with no abstract and in the {\tt\string modern} style.

\section{Floats} \label{sec:floats}

Floats are non-text items that generally can not be split over a page.
They also have captions and can be numbered for reference.  Primarily these
are figures and tables but authors can define their own. \latex\ tries to
place a float where indicated in the manuscript but will move it later if
there is not enough room at that location, hence the term ``float''.

Authors are encouraged to embed their tables and figures within the text as
they are mentioned.  Please do not place the figures and text at the end of
the article as was the old practice.  Editors and the vast majority of
referees find it much easier to read a manuscript with embedded figures and
tables.

Depending on the number of floats and the particular amount of text and
equations present in a manuscript the ultimate location of any specific
float can be hard to predict prior to compilation. It is recommended that
authors textbf{not} spend significant time trying to get float placement
perfect for peer review.  The AAS Journal's publisher has sophisticated
typesetting software that will produce the optimal layout during
production.

Note that authors of Research Notes are only allowed one float, either one
table or one figure.

\startlongtable
\begin{deluxetable}{c|cc}
\tablecaption{ApJ costs from 1991 to 2013\tablenotemark{a} \label{tab:table}}
\tablehead{
\colhead{Year} & \colhead{Subscription} & \colhead{Publication} \\
\colhead{} & \colhead{cost} & \colhead{charges\tablenotemark{b}}\\
\colhead{} & \colhead{(\$)} & \colhead{(\$/page)}
}
\colnumbers
\startdata
1991 & 600 & 100 \\
1992 & 650 & 105 \\
1993 & 550 & 103 \\
1994 & 450 & 110 \\
1995 & 410 & 112 \\
1996 & 400 & 114 \\
1997 & 525 & 115 \\
1998 & 590 & 116 \\
1999 & 575 & 115 \\
2000 & 450 & 103 \\
2001 & 490 &  90 \\
2002 & 500 &  88 \\
2003 & 450 &  90 \\
2004 & 460 &  88 \\
2005 & 440 &  79 \\
2006 & 350 &  77 \\
2007 & 325 &  70 \\
2008 & 320 &  65 \\
2009 & 190 &  68 \\
2010 & 280 &  70 \\
2011 & 275 &  68 \\
2012 & 150 &  56 \\
2013 & 140 &  55 \\
\enddata
\tablenotetext{a}{Adjusted for inflation}
\tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
\tablecomments{Note that {\tt \string \colnumbers} does not work with the 
vertical line alignment token. If you want vertical lines in the headers you
can not use this command at this time.}
\end{deluxetable}

For authors that do want to take the time to optimize the locations of
their floats there are some techniques that can be used.  The simplest
solution is to placing a float earlier in the text to get the position
right but this option will break down if the manuscript is altered, see
Table \ref{tab:table}.  A better method is to force \latex\ to place a
float in a general area with the use of the optional {\tt\string [placement
specifier]} parameter for figures and tables. This parameter goes after
{\tt\string \begin\{figure\}}, {\tt\string \begin\{table\}}, and
{\tt\string \begin\{deluxetable\}}.  The main arguments the specifier takes
are ``h'', ``t'', ``b'', and ``!''.  These tell \latex\ to place the float
\underline{h}ere (or as close as possible to this location as possible), at
the \underline{t}op of the page, and at the \underline{b}ottom of the page.
The last argument, ``!'', tells \latex\ to override its internal method of
calculating the float position.  A sequence of rules can be created by
using multiple arguments.  For example, {\tt\string \begin\{figure\}[htb!]}
tells \latex\ to try the current location first, then the top of the page
and finally the bottom of the page without regard to what it thinks the
proper position should be.  Many of the tables and figures in this article
use a placement specifier to set their positions.

Note that the \latex\ {\tt\string tabular} environment is not a float.  Only
when a {\tt\string tabular} is surrounded by {\tt\string\begin\{table\}} ...
{\tt\string\end\{table\}} is it a true float and the rules and suggestions
above apply.

In AASTeX v6.2 all deluxetables are float tables and thus if they are
longer than a page will spill off the bottom. Long deluxetables should
begin with the {\tt\string\startlongtable} command. This initiates a
longtable environment.  Authors might have to use {\tt\string\clearpage} to
isolate a long table or optimally place it within the surrounding text.

\begin{deluxetable*}{ccCrlc}[b!]
\tablecaption{Column math mode in an observation log \label{tab:mathmode}}
\tablecolumns{6}
\tablenum{2}
\tablewidth{0pt}
\tablehead{
\colhead{UT start time\tablenotemark{a}} &
\colhead{MJD start time\tablenotemark{a}} &
\colhead{Seeing} & \colhead{Filter} & \colhead{Inst.} \\
\colhead{(YYYY-mm-dd)} & \colhead{(d)} &
\colhead{(arcsec)} & \colhead{} & \colhead{}
}
\startdata
2012-03-26 & 56012.997 & \sim 0.\arcsec5 & H$\alpha$ & NOT \\
2012-03-27 & 56013.944 & 1.\arcsec5 & grism & SMARTS \\
2012-03-28 & 56014.984 & \nodata & F814M & HST \\
2012-03-30 & 56016.978 & 1.\arcsec5\pm0.25 & B\&C & Bok \\
\enddata
\tablenotetext{a}{At exposure start.}
\tablecomments{The ``C'' command column identifier in the 3 column turns on
math mode for that specific column. One could do the same for the next
column so that dollar signs would not be needed for H$\alpha$
but then all the other text would also be in math mode and thus typeset
in Latin Modern math and you will need to put it back to Roman by hand.
Note that if you do change this column to math mode the dollar signs already
present will not cause a problem. Table \ref{tab:mathmode} is published 
in its entirety in the machine readable format.  A portion is
shown here for guidance regarding its form and content.}
\end{deluxetable*}

\subsection{Tables} \label{subsec:tables}

Tables can be constructed with \latex's standard table environment or the
\aastex's deluxetable environment. The deluxetable construct handles long
tables better but has a larger overhead due to the greater amount of
defined mark up used set up and manipulate the table structure.  The choice
of which to use is up to the author.  Examples of both environments are
used in this manuscript. Table \ref{tab:table} is a simple deluxetable
example that gives the approximate changes in the subscription costs and
author publication charges from 1991 to 2013.

Tables longer than 200 data lines and complex tables should only have a
short example table with the full data set available in the machine
readable format.  The machine readable table will be available in the HTML
version of the article with just a short example in the PDF. Authors are
required to indicate to the reader where the data can be obtained in the
table comments.  Suggested text is given in the comments of Table
\ref{tab:mathmode}.  Authors are encouraged to create their own machine
readable tables using the online tool at
\url{http://authortools.aas.org/MRT/upload.html}.

\aastex\ v6 introduces five new table features that are designed to make
table construction easier and the resulting display better for AAS Journal
authors.  The items are:

\begin{enumerate}
\item Declaring math mode in specific columns,
\item Column decimal alignment, 
\item Automatic column header numbering,
\item Hiding columns, and
\item Splitting wide tables into two or three parts.
\end{enumerate}

Each of these new features are illustrated in following Table examples.
All five features work with the regular \latex\ tabular environment and in
\aastex's deluxetable environment.  The examples in this manuscript also
show where the two process differ.

\subsubsection{Column math mode}

Both the \latex\ tabular and \aastex\ deluxetable require an argument to
define the alignment and number of columns.  The most common values are
``c'', ``l'' and ``r'' for \underline{c}enter, \underline{l}eft, and
\underline{r}ight justification.  If these values are capitalized, e.g.
``C'', ``L'', or ``R'', then that specific column will automatically be in math
mode meaning that \$s are not required.  Note that having embedded dollar
signs in the table does not affect the output.  The third and forth columns
of Table \ref{tab:mathmode} shows how this math mode works.

\subsubsection{Decimal alignment}

Aligning a column by the decimal point can be difficult with only center,
left, and right justification options.  It is possible to use phantom calls
in the data, e.g. {\tt\string\phn}, to align columns by hand but this can
be tedious in long or complex tables.  To address this \aastex\ introduces
the {\tt\string\decimals} command and a new column justification option,
``D'', to align data in that column on the decimal.  In deluxetable the
{\tt\string\decimals} command is invoked before the {\tt\string\startdata}
call but can be anywhere in \latex's tabular environment.

Two other important thing to note when using decimal alignment is that each
decimal column \textit{must end with a space before the ampersand}, e.g.
``\&\&'' is not allowed.  Empty decimal columns are indicated with a decimal,
e.g. ``.''.  Do not use deluxetable's {\tt\string\nodata} command.

The ``D'' alignment token works by splitting the column into two parts on the
decimal.  While this is invisible to the user one must be aware of how it
works so that the headers are accounted for correctly.  All decimal column
headers need to span two columns to get the alignment correct. This can be
done with a multicolumn call, e.g {\tt\string\multicolumn2c\{\}} or
{\tt\string\multicolumn\{2\}\{c\}\{\}}, or use the new
{\tt\string\twocolhead\{\}} command in deluxetable.  Since \latex\ is
splitting these columns into two it is important to get the table width
right so that they appear joined on the page.  You may have to run the
\latex\ compiler twice to get it right.  Table \ref{tab:decimal}
illustrates how decimal alignment works in the tabular environment with a
$\pm$ symbol embedded between the last two columns.

%% Note that the \setcounter and \renewcommand are needed here because
%% this example is using a mix of deluxetable and tabular.  Here the
%% deluxetable counters are set with \tablenum but the situation is a bit
%% more complex for tabular.  Use the first command to set the Table number
%% to ONE LESS than it should be.  The next command will auto increment it
%% to the desired number.
\setcounter{table}{2}
\begin{table}[h!]
\renewcommand{\thetable}{\arabic{table}}
\centering
\caption{Decimal alignment made easy} \label{tab:decimal}
\begin{tabular}{cD@{$\pm$}D}
\tablewidth{0pt}
\hline
\hline
Column & \multicolumn2c{Value} & \multicolumn2c{Uncertainty}\\
\hline
\decimals
A & 1234     & 100.0     \\
B &  123.4   &  10.1     \\
C &  12.34   &   1.01    \\
D &   1.234  &   0.101   \\
E &    .1234 &   0.01001 \\
F &   1.0    &    .      \\
\hline
\multicolumn{5}{c}{NOTE. - Two decimal aligned columns}
\end{tabular}
\end{table}

\subsubsection{Automatic column header numbering} \label{subsubsec:autonumber}

The command {\tt\string\colnumbers} can be included to automatically number
each column as the last row in the header. Per the AAS Journal table format
standards, each column index numbers will be surrounded by parentheses. In
a \latex\ tabular environment the {\tt\string\colnumbers} should be invoked
at the location where the author wants the numbers to appear, e.g. after
the last line of specified table header rows. In deluxetable this command
has to come before {\tt\string\startdata}.  {\tt\string\colnumbers} will
not increment for columns hidden by the ``h'' command, see Section
\ref{subsubsec:hide}.  Table \ref{tab:table} uses this command to
automatically generate column index numbers.

Note that when using decimal alignment in a table the command 
{\tt\string\decimalcolnumbers} must be used instead of 
{\tt\string\colnumbers} and {\tt\string\decimals}. Table \ref{tab:messier}
illustrates this specific functionality.

\subsubsection{Hiding columns} \label{subsubsec:hide}

Entire columns can be \underline{h}idden from display simply by changing
the specified column identifier to ``h''.  In the \latex\ tabular environment
this column identifier conceals the entire column including the header
columns.   In \aastex's deluxetables the header row is specifically
declared with the {\tt\string\tablehead} call and each header column is
marked with {\tt\string\colhead} call.  In order to make a specific header
disappear with the ``h'' column identifier in deluxetable use 
{\tt\string\nocolhead} instead to suppress that particular column header.

Authors can use this option in many different ways.  Since column data can
be easily suppressed authors can include extra information and hid it
based on the comments of co-authors or referees.  For wide tables that will
have a machine readable version, authors could put all the information in
the \latex\ table but use this option to hid as many columns as needed until
it fits on a page. This concealed column table would serve as the
example table for the full machine readable version.  Regardless of how
columns are obscured, authors are responsible for removing any unneeded
column data or alerting the editorial office about how to treat these
columns during production for the final typeset article.

Table \ref{tab:messier} provides some basic information about the first ten
Messier Objects and illustrates how many of these new features can be used
together.  It has automatic column numbering, decimal alignment of the
distances, and one concealed column.  The Common name column
is the third in the \latex\ deluxetable but does not appear when the article
is compiled. This hidden column can be shown simply by changing the ``h'' in
the column identifier preamble to another valid value.  This table also
uses {\tt\string\tablenum} to renumber the table because a \latex\ tabular
table was inserted before it.

\begin{deluxetable*}{cchlDlc}
\tablenum{4}
\tablecaption{Fun facts about the first 10 messier objects\label{tab:messier}}
\tablewidth{0pt}
\tablehead{
\colhead{Messier} & \colhead{NGC/IC} & \nocolhead{Common} & \colhead{Object} &
\multicolumn2c{Distance} & \colhead{} & \colhead{V} \\
\colhead{Number} & \colhead{Number} & \nocolhead{Name} & \colhead{Type} &
\multicolumn2c{(kpc)} & \colhead{Constellation} & \colhead{(mag)}
}
\decimalcolnumbers
\startdata
M1 & NGC 1952 & Crab Nebula & Supernova remnant & 2 & Taurus & 8.4 \\
M2 & NGC 7089 & Messier 2 & Cluster, globular & 11.5 & Aquarius & 6.3 \\
M3 & NGC 5272 & Messier 3 & Cluster, globular & 10.4 & Canes Venatici &  6.2 \\
M4 & NGC 6121 & Messier 4 & Cluster, globular & 2.2 & Scorpius & 5.9 \\
M5 & NGC 5904 & Messier 5 & Cluster, globular & 24.5 & Serpens & 5.9 \\
M6 & NGC 6405 & Butterfly Cluster & Cluster, open & 0.31 & Scorpius & 4.2 \\
M7 & NGC 6475 & Ptolemy Cluster & Cluster, open & 0.3 & Scorpius & 3.3 \\
M8 & NGC 6523 & Lagoon Nebula & Nebula with cluster & 1.25 & Sagittarius & 6.0 \\
M9 & NGC 6333 & Messier 9 & Cluster, globular & 7.91 & Ophiuchus & 8.4 \\
M10 & NGC 6254 & Messier 10 & Cluster, globular & 4.42 & Ophiuchus & 6.4 \\
\enddata
\tablecomments{This table ``hides'' the third column in the \latex\ when compiled.
The Distance is also centered on the decimals.  Note that when using decimal
alignment you need to include the {\tt\string\decimals} command before
{\tt\string\startdata} and all of the values in that column have to have a
space before the next ampersand.}
\end{deluxetable*}

\subsubsection{Splitting a table into multiple horizontal components}

Since the AAS Journals are now all electronic with no print version there is
no reason why tables can not be as wide as authors need them to be.
However, there are some artificial limitations based on the width of a
print page.  The old way around this limitation was to rotate into 
landscape mode and use the smallest available table font
sizes, e.g. {\tt\string\tablewidth}, to get the table to fit.
Unfortunately, this was not alway enough but now along with the hide column
option outlined in Section \ref{subsubsec:hide} there is a new way to break
a table into two or three components so that it flows down a page by
invoking a new table type, splittabular or splitdeluxetable. Within these
tables a new ``B'' column separator is introduced.  Much like the vertical
bar option, ``$\vert$'', that produces a vertical table lines, e.g. Table
\ref{tab:table}, the new ``B'' separator indicates where to \underline{B}reak
a table.  Up to two ``B''s may be included.

Table 5 % \ref{tab:deluxesplit} this freaks it out when it is used!
shows how to split a wide deluxetable into three parts with
the {\tt\string\splitdeluxetable} command.  The {\tt\string\colnumbers}
option is on to show how the automatic column numbering carries through the
second table component, see Section \ref{subsubsec:autonumber}.

The last example, Table \ref{tab:tablesplit}, shows how to split the same
table but with a regular \latex\ tabular call and into two parts. Decimal
alignment is included in the third column and the ``Component'' column is
hidden to illustrate the new features working together.

\begin{splitdeluxetable*}{lccccBcccccBcccc}
\tabletypesize{\scriptsize}
\tablewidth{0pt} 
\tablenum{5}
\tablecaption{Measurements of Emission Lines: two breaks \label{tab:deluxesplit}}
\tablehead{
\colhead{Model} & \colhead{Component}& \colhead{Shift} & \colhead{FWHM} &
\multicolumn{10}{c}{Flux} \\
\colhead{} & \colhead{} & \colhead{($\rm
km~s^{-1}$)}& \colhead{($\rm km~s^{-1}$)} & \multicolumn{10}{c}{($\rm
10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
\cline{5-14}
\colhead{} & \colhead{} &
\colhead{} & \colhead{} & \colhead{Ly$\alpha$} & \colhead{N\,{\footnotesize
V}} & \colhead{Si\,{\footnotesize IV}} & \colhead{C\,{\footnotesize IV}} &
\colhead{Mg\,{\footnotesize II}} & \colhead{H$\gamma$} & \colhead{H$\beta$}
& \colhead{H$\alpha$} & \colhead{He\,{\footnotesize I}} &
\colhead{Pa$\gamma$}
} 
\colnumbers
\startdata 
{       }& BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\ 
{Model 1}& IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
{       }& NELs& \nodata &     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
\hline
{       }& BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
{Model 2}& IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
{       }& NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$&
     147$\pm       22$\\
\enddata
\tablecomments{This is an example of how to split a deluxetable. You can
split any table with this command into two or three parts.  The location of
the split is given by the author based on the placement of the ``B''
indicators in the column identifier preamble.  For more information please
look at the new \aastex\ instructions.}
\end{splitdeluxetable*}

%\clearpage

\setcounter{table}{5}
\begin{table*}[h!]
\renewcommand{\thetable}{\arabic{table}}
\caption{Measurements of Emission Lines: one break\label{tab:tablesplit}}
\begin{splittabular}{lhDccccBccccccc}
%\multicolumn{5}{c}{Table 6} \\
%\multicolumn{5}{c}{Measurements of Emission Lines} \\
\hline 
\hline 
Model & Component & \multicolumn2c{Shift} & FWHM & 
\multicolumn{10}{c}{Flux} \\
 & & \multicolumn2c{($\rm km~s^{-1}$)} & {($\rm km~s^{-1}$)} & 
\multicolumn{10}{c}{($\rm 10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
\cline{5-15}
 & & & & & {Ly$\alpha$} & {N\,{\footnotesize V}} & 
{Si\,{\footnotesize IV}} & {C\,{\footnotesize IV}} &
{Mg\,{\footnotesize II}} & {H$\gamma$} & {H$\beta$}
& {H$\alpha$} & {He\,{\footnotesize I}} & {Pa$\gamma$} \\
%\hline
\decimalcolnumbers
 & BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\
Model 1 & IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
 & NELs& . &     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
\hline
 & BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
Model 2 & IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
 & NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$& 147$\pm       22$\\
\hline
\end{splittabular}
\end{table*}

\subsection{Figures\label{subsec:figures}}

%% The "ht!" tells LaTeX to put the figure "here" first, at the "top" next
%% and to override the normal way of calculating a float position
\begin{figure}[ht!]
\plotone{cost-eps-converted-to.pdf}
\caption{The subscription and author publication costs from 1991 to 2013.
The data comes from Table \ref{tab:table}.\label{fig:general}}
\end{figure}

Authors can include a wide number of different graphics with their articles
in  encapsulated postscript (EPS) or portable document format (PDF).  These
range from general figures all authors are familiar with to new enhanced
graphics that can only be fully experienced in HTML.  The later include
animations, figure sets and interactive figures.  This portion of the
article provides examples for setting up all these graphics in with the
latest version of \aastex.

\subsection{General figures\label{subsec:general}}

\aastex\ has a {\tt\string\plotone} command to display a figure
consisting of one EPS/PDF file.  Figure \ref{fig:general} is an example
which uses the data from Table \ref{tab:table}. For a general figure
consisting of two EPS/PDF files the {\tt\string\plottwo} command can be
used to position the two image files side by side.  Figure \ref{fig:f2}
shows the Swift/XRT X-ray light curves of two recurrent novae.  The data
from Figures \ref{fig:f2} through \ref{fig:fig4} are taken from Table 2 of
\citet{2011ApJS..197...31S}.

\begin{figure}
\plottwo{RS_Oph-eps-converted-to.pdf}{U_Sco-eps-converted-to.pdf}
\caption{Swift/XRT X-ray light curves of RS Oph and U Sco which represent
the two canonical recurrent types, a long period system with a red giant
secondary and a short period system with a dwarf/sub-dwarf secondary,
respectively.\label{fig:f2}}
\end{figure}

Both {\tt\string\plotone} and {\tt\string\plottwo} take a
{\tt\string\caption} and an optional {\tt\string\figurenum} command to
specify the figure number\footnote{It is better to not use
{\tt\string\figurenum} and let LaTeX auto-increment all the figures. If you
do use this command you need to mark all of them accordingly.}.  Each is
based on the {\tt\string graphicx} package command,
{\tt\string\includegraphics}.  Authors are welcome to use
{\tt\string\includegraphics} along with its optional arguments that control
the height, width, scale, and position angle of a file within the figure.
More information on the full usage of {\tt\string\includegraphics} can be
found at \break
\url{https://en.wikibooks.org/wiki/LaTeX/Importing\_Graphics\#Including\_graphics}.

\subsection{Grid figures}

Including more than two EPS/PDF files in a single figure call can be tricky
easily format.  To make the process easier for authors \aastex\ v6 offers
{\tt\string\gridline} which allows any number of individual EPS/PDF file
calls within a single figure.  Each file cited in a {\tt\string\gridline}
will be displayed in a row.  By adding more {\tt\string\gridline} calls an
author can easily construct a matrix X by Y individual files as a
single general figure.

For each {\tt\string\gridline} command a EPS/PDF file is called by one of
four different commands.  These are {\tt\string\fig},
{\tt\string\rightfig}, {\tt\string\leftfig}, and {\tt\string\boxedfig}.
The first file call specifies no image position justification while the
next two will right and left justify the image, respectively.  The
{\tt\string\boxedfig} is similar to {\tt\string\fig} except that a box is
drawn around the figure file when displayed. Each of these commands takes
three arguments.  The first is the file name.  The second is the width that
file should be displayed at.  While any natural \latex\ unit is allowed, it
is recommended that author use fractional units with the
{\tt\string\textwidth}.  The last argument is text for a subcaption.

Figure \ref{fig:pyramid} shows an inverted pyramid of individual
figure constructed with six individual EPS files using the
{\tt\string\gridline} option.

\begin{figure*}
\gridline{\fig{V2491_Cyg-eps-converted-to.pdf}{0.3\textwidth}{(a)}
          \fig{CSS081007-eps-converted-to.pdf}{0.3\textwidth}{(b)}
          \fig{LMC_2009-eps-converted-to.pdf}{0.3\textwidth}{(c)}
          }
\gridline{\fig{RS_Oph-eps-converted-to.pdf}{0.3\textwidth}{(d)}
          \fig{U_Sco-eps-converted-to.pdf}{0.3\textwidth}{(e)}
          }
\gridline{\fig{KT_Eri-eps-converted-to.pdf}{0.3\textwidth}{(f)}}
\caption{Inverted pyramid figure of six individual files. The nova are
(a) V2491 Cyg, (b) HV Cet, (c) LMC 2009, (d) RS Oph, (e) U Sco, and
(f) KT Eri.\label{fig:pyramid}}
\end{figure*}

\subsection{Figure sets}

A large collection of similar style figures should be grouped together as a
figure set.  The derived PDF article will only shows an example figure
while the enhanced content is available in the figure set in the electronic
edition.  The advantage of a figure set gives the reader the ability to
easily sort through the figure collection to find individual component
figures.  All of the figure set components, along with their html framework,
are also available for download in a .tar.gz package.

Special \latex\ mark up is required to create a figure set.  Prior to
\aastex\ v6 the underlying mark up commands had to be inserted by hand
but is now included.  Note that when an article with figure set is compiled
in \latex\ none of the component figures are shown and a floating Figure
Set caption will appear in the resulting PDF.

\figsetstart
\figsetnum{4}
\figsettitle{Swift X-ray light curves}

\figsetgrpstart
\figsetgrpnum{1.1}
\figsetgrptitle{KT Eri}
\figsetplot{KT_Eri-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.2}
\figsetgrptitle{RS Oph}
\figsetplot{RS_Oph-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.3}
\figsetgrptitle{U Sco}
\figsetplot{U_Sco-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.4}
\figsetgrptitle{V2491 Cyg}
\figsetplot{V2491_Cyg-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.5}
\figsetgrptitle{Nova LMC 2009}
\figsetplot{LMC_2009-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.6}
\figsetgrptitle{HV Cet}
\figsetplot{CSS081007-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.7}
\figsetgrptitle{V2672 Oph}
\figsetplot{V2672_Oph-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetgrpstart
\figsetgrpnum{1.8}
\figsetgrptitle{V407 Cyg}
\figsetplot{V407_Cyg-eps-converted-to.pdf}
\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
outburst.}
\figsetgrpend

\figsetend

\begin{figure}
\plotone{KT_Eri-eps-converted-to.pdf}
\caption{The Swift/XRT X-ray light curve for the first year after
outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
the component figures are available in the Figure Set. \label{fig:fig4}}
\end{figure}

Authors are encouraged to use an online tool at
\url{http://authortools.aas.org/FIGSETS/make-figset.html} to generate their
own specific figure set mark up to incorporate into their \latex\ articles.

\subsection{Animations}

Authors may include animations in their articles.  A single still frame from 
the animation should be included as a regular figure to serve as an example.
The associated figure caption should indicate to the reader exactly what the
animation shows and that the animation is available online.

\begin{figure}
\plotone{video3-eps-converted-to.pdf}
\caption{Example image from the animation which is available in the electronic
edition.}
\end{figure}

\subsection{Interactive figures}

Interactive figures give the reader the ability to manipulate the
information contained in an image which can add clarity or help further the
author's narrative.  These figures consist of two parts, the figure file in
a specific format and a javascript and html frame work that provides the
interactive control.  An example of an interactive figure is a 3D model.
The underlying figure is a X3D file while x3dom.js is the javascript driver
that displays it. An author created interface is added via a html wrapper.
The first 3D model published by the AAS Journals using this technique was
\citet{2014ApJ...793..127V}.  Authors should consult the online tutorials
for more information on how to construct their own interactive figures.

As with animations authors should include a non-interactive regular figure
to use as an example.  The example figure should also indicate to the reader
that the enhanced figure is interactive and can be accessed online.

\section{Displaying mathematics} \label{sec:displaymath}

The most common mathematical symbols and formulas are in the amsmath
package.  \aastex\ requires this package so there is no need to
specifically call for it in the document preamble.  Most modern \latex\
distributions already contain this package.  If you do not have this
package or the other required packages, revtex4-1, latexsym, graphicx,
amssymb, longtable, and epsf, they can be obtained from 
\url{http://www.ctan.org}

Mathematics can be displayed either within the text, e.g. $E = mc^2$, or
separate from in an equation.  In order to be properly rendered, all inline
math text has to be declared by surrounding the math by dollar signs (\$).

A complex equation example with inline math as part of the explanation
follows.

\begin{equation}
\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
\hat a_nu(p_1,\sigma_1) ,
\end{equation}
where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
operator $(\tau = \pm1)$.  This produces a single line formula.  \latex\ will
auto-number this and any subsequent equations.  If no number is desired then
the {\tt\string equation} call should be replaced with {\tt\string displaymath}.

\latex\ can also handle a a multi-line equation.  Use {\tt\string eqnarray}
for more than one line and end each line with a
\textbackslash\textbackslash.  Each line will be numbered unless the
\textbackslash\textbackslash\ is preceded by a {\tt\string\nonumber}
command.  Alignment points can be added with ampersands (\&).  There should be
two ampersands per line. In the examples they are centered on the equal
symbol.

\begin{eqnarray}
\gamma^\mu  & = &
 \left(
\begin{array}{cc}
0 & \sigma^\mu_+ \\
\sigma^\mu_- & 0
\end{array}     \right) ,
 \gamma^5= \left(
\begin{array}{cc}
-1 &   0\\
0 &   1
\end{array}     \right)  , \\
\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , 
\end{eqnarray}

\begin{eqnarray}
\hat a & = & \left(
\begin{array}{cc}
0 & (\hat a)_+\\
(\hat a)_- & 0
\end{array}\right), \nonumber \\
(\hat a)_\pm & = & a_\mu\sigma^\mu_\pm 
\end{eqnarray}

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

\section{Revision tracking and color highlighting} \label{sec:highlight}

Authors sometimes use color to highlight changes to their manuscript in
response to editor and referee comments.  In \aastex\ new commands
have been introduced to make this easier and formalize the process.

The first method is through a new set of editing mark up commands that
specifically identify what has been changed.  These commands are
{\tt\string\added\{<text>\}}, {\tt\string\deleted\{<text>\}}, and
{\tt\string\replaced\{<old text>\}\{<replaced text>\}}. To activate these
commands the {\tt\string trackchanges} option must be used in the
{\tt\string\documentclass} call.  When compiled this will produce the
marked text in red.  The {\tt\string\explain\{<text>\}} can be used to add
text to provide information to the reader describing the change.  Its
output is purple italic font. To see how {\tt\string\added\{<important
added info>\}}, {\tt\string\deleted\{<this can be deleted text>\}},
{\tt\string\replaced\{<old data>\}\{<replaced data>\}}, and \break
{\tt\string\explain\{<text explaining the change>\}} commands will produce
\added{important added information}\deleted{, deleted text, and }
\replaced{old data}{and replaced data,} toggle between versions compiled with
and without the {\tt\string trackchanges} option.\explain{text explaining
the change}

A summary list of all these tracking commands can be produced at the end of
the article by adding the {\tt\string\listofchanges} just before the
{\tt\string\end\{document\}} call.  The page number for each change will be
provided. If the {\tt\string linenumbers} option is also included in the
documentcall call then not only will all the lines in the article be
numbered for handy reference but the summary list will also include the
line number for each change.

The second method does not have the ability to highlight the specific
nature of the changes but does allow the author to document changes over
multiple revisions.  The commands are {\tt\string\edit1\{<text>\}},
{\tt\string\edit2\{<text>\}} and {\tt\string\edit3\{<text>\}} and they
produce {\tt\string<text>} that is highlighted in bold red, italic blue and
underlined purple, respectively.  Authors should use the first command to
\edit1{indicated which text has been changed from the first revision.}  The
second command is to highlight \edit2{new or modified text from a second
revision}.  If a third revision is needed then the last command should be used 
\edit3{to show this changed text}.  Since over 90\% of all manuscripts are
accepted after the 3rd revision these commands make it easy to identify
what text has been added and when.  Once the article is accepted all the
highlight color can be turned off simply by adding the
{\tt\string\turnoffediting} command in the preamble. Likewise, the new commands
{\tt\string\turnoffeditone}, {\tt\string\turnoffedittwo}, and
{\tt\string\turnoffeditthree} can be used to only turn off the 
{\tt\string\edit1\{<text>\}}, {\tt\string\edit2\{<text>\}} and 
{\tt\string\edit3\{<text>\}}, respectively.

Similar to marking editing changes with the {\tt\string\edit} options there
are also the {\tt\string\authorcomments1\{<text>\}}, 
{\tt\string\authorcomments2\{<text>\}} and
{\tt\string\authorcomments3\{<text>\}} commands.  These produce the same
bold red, italic blue and underlined purple text but when the
{\tt\string\turnoffediting} command is present the {\tt\string<text>}
material does not appear in the manuscript.  Authors can use these commands
to mark up text that they are not sure should appear in the final
manuscript or as a way to communicate comments between co-authors when
writing the article.

\section{Software and third party data repository citations} \label{sec:cite}

The AAS Journals would like to encourage authors to change software and
third party data repository references from the current standard of a
footnote to a first class citation in the bibliography.  As a bibliographic
citation these important references will be more easily captured and credit
will be given to the appropriate people.

The first step to making this happen is to have the data or software in
a long term repository that has made these items available via a persistent
identifier like a Digital Object Identifier (DOI).  A list of repositories
that satisfy this criteria plus each one's pros and cons are given at \break
\url{https://github.com/AASJournals/Tutorials/tree/master/Repositories}.

In the bibliography the format for data or code follows this format: \\

\noindent author year, title, version, publisher, prefix:identifier\\

\citet{2015ApJ...805...23C} provides a example of how the citation in the
article references the external code at
\doi{10.5281/zenodo.15991}.  Unfortunately, bibtex does
not have specific bibtex entries for these types of references so the
``@misc'' type should be used.  The Repository tutorial explains how to
code the ``@misc'' type correctly.  The most recent aasjournal.bst file,
available with \aastex\ v6, will output bibtex ``@misc'' type properly.

%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.
\acknowledgments

We thank all the people that have made this AASTeX what it is today.  This
includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
for the new "modern" style design. Considerable help was provided via bug
reports and hacks from numerous people including Patricio Cubillos, Alex
Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
Gagne.

%% To help institutions obtain information on the effectiveness of their 
%% telescopes the AAS Journals has created a group of keywords for telescope 
%% facilities.
%
%% Following the acknowledgments section, use the following syntax and the
%% \facility{} or \facilities{} macros to list the keywords of facilities used 
%% in the research for the paper.  Each keyword is check against the master 
%% list during copy editing.  Individual instruments can be provided in 
%% parentheses, after the keyword, but they are not verified.

\vspace{5mm}
\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
CTIO:1.5m,CXO}

%% Similar to \facility{}, there is the optional \software command to allow 
%% authors a place to specify which programs were used during the creation of 
%% the manusscript. Authors should list each code and include either a
%% citation or url to the code inside ()s when available.

\software{astropy \citep{2013A&A...558A..33A},  
          Cloudy \citep{2013RMxAA..49..137F}, 
          SExtractor \citep{1996A&AS..117..393B}
          }

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc. The
%% Figure and Table counter will not reset.

\appendix

\section{Appendix information}

Appendices can be broken into separate sections just like in the main text.
The only difference is that each appendix section is indexed by a letter
(A, B, C, etc.) instead of a number.  Likewise numbered equations have
the section letter appended.  Here is an equation as an example.

\begin{equation}
I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
\end{equation}

Appendix tables and figures should not be numbered like equations. Instead
they should continue the sequence from the main article body.

\section{Author publication charges} \label{sec:pubcharge}

Finally some information about the AAS Journal's publication charges.
In April 2011 the traditional way of calculating author charges based on 
the number of printed pages was changed.  The reason for the change
was due to a recognition of the growing number of article items that could not 
be represented in print. Now author charges are determined by a number of
digital ``quanta''.  A single quantum is 350 words, one figure, one table,
and one enhanced digital item.  For the latter this includes machine readable
tables, figure sets, animations, and interactive figures.  The current cost
is \$27 per word quantum and \$30 for all other quantum type.

\section{Rotating tables} \label{sec:rotate}

The process of rotating tables into landscape mode is slightly different in
\aastex v6.2. Instead of the {\tt\string\rotate} command, a new environment
has been created to handle this task. To place a single page table in a
landscape mode start the table portion with
{\tt\string\begin\{rotatetable\}} and end with
{\tt\string\end\{rotatetable\}}.

Tables that exceed a print page take a slightly different environment since
both rotation and long table printing are required. In these cases start
with {\tt\string\begin\{longrotatetable\}} and end with
{\tt\string\end\{longrotatetable\}}. Table \ref{chartable} is an
example of a multi-page, rotated table.

\begin{longrotatetable}
\begin{deluxetable*}{lllrrrrrrll}
\tablecaption{Observable Characteristics of 
Galactic/Magellanic Cloud novae with X-ray observations\label{chartable}}
\tablewidth{700pt}
\tabletypesize{\scriptsize}
\tablehead{
\colhead{Name} & \colhead{V$_{max}$} & 
\colhead{Date} & \colhead{t$_2$} & 
\colhead{FWHM} & \colhead{E(B-V)} & 
\colhead{N$_H$} & \colhead{Period} & 
\colhead{D} & \colhead{Dust?} & \colhead{RN?} \\ 
\colhead{} & \colhead{(mag)} & \colhead{(JD)} & \colhead{(d)} & 
\colhead{(km s$^{-1}$)} & \colhead{(mag)} & \colhead{(cm$^{-2}$)} &
\colhead{(d)} & \colhead{(kpc)} & \colhead{} & \colhead{}
} 
\startdata
CI Aql & 8.83 (1) & 2451665.5 (1) & 32 (2) & 2300 (3) & 0.8$\pm0.2$ (4) & 1.2e+22 & 0.62 (4) & 6.25$\pm5$ (4) & N & Y \\
{\bf CSS081007} & \nodata & 2454596.5 & \nodata & \nodata & 0.146 & 1.1e+21 & 1.77 (5) & 4.45$\pm1.95$ (6) & \nodata & \nodata \\
GQ Mus & 7.2 (7) & 2445352.5 (7) & 18 (7) & 1000 (8) & 0.45 (9) & 3.8e+21  & 0.059375 (10) & 4.8$\pm1$ (9) & N (7) & \nodata \\
IM Nor & 7.84 (11) & 2452289 (2) & 50 (2) & 1150 (12) & 0.8$\pm0.2$ (4) & 8e+21 & 0.102 (13) & 4.25$\pm3.4$ (4) & N & Y \\
{\bf KT Eri} & 5.42 (14) & 2455150.17 (14) & 6.6 (14) & 3000 (15) & 0.08 (15) & 5.5e+20 & \nodata & 6.5 (15) & N & M \\
{\bf LMC 1995} & 10.7 (16) & 2449778.5 (16) & 15$\pm2$ (17) & \nodata & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
LMC 2000 & 11.45 (18) & 2451737.5 (18) & 9$\pm2$ (19) & 1700 (20) & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
{\bf LMC 2005} & 11.5 (21) & 2453700.5 (21) & 63 (22) & 900 (23) & 0.15 (203) & 1e+21 & \nodata & 50  & M (24) & \nodata \\
{\bf LMC 2009a} & 10.6 (25) & 2454867.5 (25) & 4$\pm1$  & 3900 (25) & 0.15 (203)  & 5.7e+20 & 1.19 (26) & 50 & N & Y \\
{\bf SMC 2005} & 10.4 (27) & 2453588.5 (27) & \nodata & 3200 (28) & \nodata & 5e+20  & \nodata & 61 & \nodata & \nodata \\
{\bf QY Mus} & 8.1 (29) & 2454739.90 (29) & 60:  & \nodata & 0.71 (30) & 4.2e+21  & \nodata & \nodata & M & \nodata \\
{\bf RS Oph} & 4.5 (31) & 2453779.44 (14) & 7.9 (14) & 3930 (31) & 0.73 (32) & 2.25e+21 & 456 (33) & 1.6$\pm0.3$ (33) & N (34) & Y \\
{\bf U Sco} & 8.05 (35) & 2455224.94 (35) & 1.2 (36) & 7600 (37) & 0.2$\pm0.1$ (4) & 1.2e+21 & 1.23056 (36) & 12$\pm2$ (4) & N & Y \\
{\bf V1047 Cen} & 8.5 (38) & 2453614.5 (39) & 6 (40) & 840 (38) & \nodata & 1.4e+22  & \nodata & \nodata & \nodata & \nodata \\
{\bf V1065 Cen} & 8.2 (41) & 2454123.5 (41) & 11 (42) & 2700 (43) & 0.5$\pm0.1$ (42) & 3.75e+21 & \nodata & 9.05$\pm2.8$ (42) & Y (42) & \nodata \\
V1187 Sco & 7.4 (44) & 2453220.5 (44) & 7: (45) & 3000 (44) & 1.56 (44) & 8.0e+21 & \nodata & 4.9$\pm0.5$ (44) & N & \nodata \\
{\bf V1188 Sco} & 8.7 (46) & 2453577.5 (46) & 7 (40) & 1730 (47) & \nodata & 5.0e+21  & \nodata & 7.5 (39) & \nodata & \nodata \\
{\bf V1213 Cen} & 8.53 (48) & 2454959.5 (48) & 11$\pm2$ (49) & 2300 (50) & 2.07 (30) & 1.0e+22 & \nodata & \nodata & \nodata & \nodata \\
{\bf V1280 Sco} & 3.79 (51) & 2454147.65 (14) & 21 (52) & 640 (53) & 0.36 (54) & 1.6e+21  & \nodata & 1.6$\pm0.4$ (54) & Y (54) & \nodata \\
{\bf V1281 Sco} & 8.8 (55) & 2454152.21 (55) & 15:& 1800 (56) & 0.7 (57) & 3.2e+21 & \nodata & \nodata & N & \nodata \\
{\bf V1309 Sco} & 7.1 (58) & 2454714.5 (58) & 23$\pm2$ (59) & 670 (60) & 1.2 (30) & 4.0e+21 & \nodata & \nodata & \nodata & \nodata \\
{\bf V1494 Aql} & 3.8 (61) & 2451515.5 (61) & 6.6$\pm0.5$ (61) & 1200 (62) & 0.6 (63) & 3.6e+21  & 0.13467 (64) & 1.6$\pm0.1$ (63) & N & \nodata \\
{\bf V1663 Aql} & 10.5 (65) & 2453531.5 (65) & 17 (66) & 1900 (67) & 2: (68) & 1.6e+22  & \nodata & 8.9$\pm3.6$ (69) & N & \nodata \\
V1974 Cyg & 4.3 (70) & 2448654.5 (70) & 17 (71) & 2000 (19) & 0.36$\pm0.04$ (71) & 2.7e+21  & 0.081263 (70) & 1.8$\pm0.1$ (72) & N & \nodata \\
{\bf V2361 Cyg} & 9.3 (73) & 2453412.5 (73) & 6 (40) & 3200 (74) & 1.2: (75) & 7.0e+21 & \nodata & \nodata & Y (40) & \nodata \\
{\bf V2362 Cyg} & 7.8 (76) & 2453831.5 (76) & 9 (77) & 1850 (78) & 0.575$\pm0.015$ (79) & 4.4e+21  & 0.06577 (80) & 7.75$\pm3$ (77) & Y (81) & \nodata \\
{\bf V2467 Cyg} & 6.7 (82) & 2454176.27 (82) & 7 (83) & 950 (82) & 1.5 (84) & 1.4e+22  & 0.159 (85) & 3.1$\pm0.5$ (86) & M (87) & \nodata \\
{\bf V2468 Cyg} & 7.4 (88) & 2454534.2 (88) & 10: & 1000 (88) & 0.77 (89) & 1.0e+22  & 0.242 (90) & \nodata & N & \nodata \\
{\bf V2491 Cyg} & 7.54 (91) & 2454567.86 (91) & 4.6 (92) & 4860 (93) & 0.43 (94) & 4.7e+21  & 0.09580: (95) & 10.5 (96) & N & M \\
V2487 Oph & 9.5 (97) & 2450979.5 (97) & 6.3 (98) & 10000 (98) & 0.38$\pm0.08$ (98) & 2.0e+21 & \nodata & 27.5$\pm3$ (99) & N (100) & Y (101) \\
{\bf V2540 Oph} & 8.5 (102) & 2452295.5 (102) & \nodata & \nodata & \nodata & 2.3e+21 & 0.284781 (103) & 5.2$\pm0.8$ (103) & N & \nodata \\
V2575 Oph & 11.1 (104) & 2453778.8 (104) & 20: & 560 (104) & 1.4 (105) & 3.3e+21 & \nodata & \nodata & N (105) & \nodata \\
{\bf V2576 Oph} & 9.2 (106) & 2453832.5 (106) & 8: & 1470 (106) & 0.25 (107) & 2.6e+21  & \nodata & \nodata & N & \nodata \\
{\bf V2615 Oph} & 8.52 (108) & 2454187.5 (108) & 26.5 (108) & 800 (109) & 0.9 (108) & 3.1e+21  & \nodata & 3.7$\pm0.2$ (108) & Y (110) & \nodata \\
{\bf V2670 Oph} & 9.9 (111) & 2454613.11 (111) & 15: & 600 (112) & 1.3: (113) & 2.9e+21  & \nodata & \nodata & N (114) & \nodata \\
{\bf V2671 Oph} & 11.1 (115) & 2454617.5 (115) & 8: & 1210 (116) & 2.0 (117) & 3.3e+21  & \nodata & \nodata & M (117) & \nodata \\
{\bf V2672 Oph} & 10.0 (118) & 2455060.02 (118) & 2.3 (119) & 8000 (118) & 1.6$\pm0.1$ (119) & 4.0e+21  & \nodata & 19$\pm2$ (119) & \nodata & M \\
V351 Pup & 6.5 (120) & 2448617.5 (120) & 16 (121) & \nodata & 0.72$\pm0.1$ (122) & 6.2e+21 & 0.1182 (123) & 2.7$\pm0.7$ (122) & N & \nodata \\
{\bf V382 Nor} & 8.9 (124) & 2453447.5 (124) & 12 (40) & 1850 (23) & \nodata & 1.7e+22 & \nodata & \nodata & \nodata & \nodata \\
V382 Vel & 2.85 (125) & 2451320.5 (125) & 4.5 (126) & 2400 (126) & 0.05: (126) & 3.4e+21  & 0.146126 (127) & 1.68$\pm0.3$ (126) & N & \nodata \\
{\bf V407 Cyg} & 6.8 (128) & 2455266.314 (128) & 5.9 (129) & 2760 (129) & 0.5$\pm0.05$ (130) & 8.8e+21 & 15595 (131) & 2.7 (131) & \nodata & Y \\
{\bf V458 Vul} & 8.24 (132) & 2454322.39 (132) & 7 (133) & 1750 (134) & 0.6 (135) & 3.6e+21 & 0.06812255 (136) & 8.5$\pm1.8$ (133) & N (135) & \nodata \\
{\bf V459 Vul} & 7.57 (137) & 2454461.5 (137) & 18 (138) & 910 (139) & 1.0 (140) & 5.5e+21  & \nodata & 3.65$\pm1.35$ (138) & Y (140) & \nodata \\
V4633 Sgr & 7.8 (141) & 2450895.5 (141) & 19$\pm3$ (142) & 1700 (143) & 0.21 (142) & 1.4e+21  & 0.125576 (144) & 8.9$\pm2.5$ (142) & N & \nodata \\
{\bf V4643 Sgr} & 8.07 (145) & 2451965.867 (145) & 4.8 (146) & 4700 (147) & 1.67 (148) & 1.4e+22 & \nodata & 3 (148) & N & \nodata \\
{\bf V4743 Sgr} & 5.0 (149) & 2452537.5 (149) & 9 (150) & 2400 (149) & 0.25 (151) & 1.2e+21 & 0.281 (152) & 3.9$\pm0.3$ (151) & N & \nodata \\
{\bf V4745 Sgr} & 7.41 (153) & 2452747.5 (153) & 8.6 (154) & 1600 (155) & 0.1 (154) & 9.0e+20  & 0.20782 (156) & 14$\pm5$ (154) & \nodata & \nodata \\
{\bf V476 Sct} & 10.3 (157) & 2453643.5 (157) & 15 (158) & \nodata & 1.9 (158) & 1.2e+22  & \nodata & 4$\pm1$ (158) & M (159) & \nodata \\
{\bf V477 Sct} & 9.8 (160) & 2453655.5 (160) & 3 (160) & 2900 (161) & 1.2: (162) & 4e+21  & \nodata & \nodata & M (163) & \nodata \\
{\bf V5114 Sgr} & 8.38 (164) & 2453081.5 (164) & 11 (165) & 2000 (23) & \nodata & 1.5e+21  & \nodata & 7.7$\pm0.7$ (165) & N (166) & \nodata \\
{\bf V5115 Sgr} & 7.7 (167) & 2453459.5 (167) & 7 (40) & 1300 (168) & 0.53 (169) & 2.3e+21  & \nodata & \nodata & N (169) & \nodata \\
{\bf V5116 Sgr} & 8.15 (170) & 2453556.91 (170) & 6.5 (171) & 970 (172) & 0.25 (173) & 1.5e+21 & 0.1238 (171) & 11$\pm3$ (173) & N (174) & \nodata \\
{\bf V5558 Sgr} & 6.53 (175) & 2454291.5 (175) & 125 (176) & 1000 (177) & 0.80 (178) & 1.6e+22  & \nodata & 1.3$\pm0.3$ (176) & N (179) & \nodata \\
{\bf V5579 Sgr} & 5.56 (180) & 2454579.62 (180) & 7: & 1500 (23) & 1.2 (181) & 3.3e+21 & \nodata & \nodata & Y (181) & \nodata \\
{\bf V5583 Sgr} & 7.43 (182) & 2455051.07 (182) & 5: & 2300 (182) & 0.39 (30) & 2.0e+21 & \nodata & 10.5 & \nodata & \nodata \\
{\bf V574 Pup} & 6.93 (183) & 2453332.22 (183) & 13 (184) & 2800 (184) & 0.5$\pm0.1$  & 6.2e+21 & \nodata & 6.5$\pm1$  & M (185) & \nodata \\
{\bf V597 Pup} & 7.0 (186) & 2454418.75 (186) & 3: & 1800 (187) & 0.3 (188) & 5.0e+21  & 0.11119 (189) & \nodata & N (188) & \nodata \\
{\bf V598 Pup} & 3.46 (14) & 2454257.79 (14) & 9$\pm1$ (190) & \nodata & 0.16 (190) & 1.4e+21 & \nodata & 2.95$\pm0.8$ (190) & \nodata & \nodata \\
{\bf V679 Car} & 7.55 (191) & 2454797.77 (191) & 20: & \nodata & \nodata & 1.3e+22  & \nodata & \nodata & \nodata & \nodata \\
{\bf V723 Cas} & 7.1 (192) & 2450069.0 (192) & 263 (2) & 600 (193) & 0.5 (194) & 2.35e+21  & 0.69 (195) & 3.86$\pm0.23$ (196) & N & \nodata \\
V838 Her & 5 (197) & 2448340.5 (197) & 2 (198) & \nodata & 0.5$\pm0.1$ (198) & 2.6e+21  & 0.2975 (199) & 3$\pm1$ (198) & Y (200) & \nodata \\
{\bf XMMSL1 J06} & 12 (201) & 2453643.5 (202) & 8$\pm2$ (202) & \nodata & 0.15 (203) & 8.7e+20 & \nodata & 50 & \nodata & \nodata \\
\enddata
\end{deluxetable*}
\end{longrotatetable}

A handy "cheat sheat" that provides the necessary LaTeX to produce 17 
different types of tables is available at \url{http://journals.aas.org/authors/aastex/aasguide.html#table_cheat_sheet}.

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% \aastex provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\begin{thebibliography}{}

\bibitem[Astropy Collaboration et al.(2013)]{2013A&A...558A..33A} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33 
\bibitem[Bertin \& Arnouts(1996)]{1996A&AS..117..393B} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
\bibitem[Corrales(2015)]{2015ApJ...805...23C} Corrales, L.\ 2015, \apj, 805, 23
\bibitem[Ferland et al.(2013)]{2013RMxAA..49..137F} Ferland, G.~J., Porter, R.~L., van Hoof, P.~A.~M., et al.\ 2013, \rmxaa, 49, 137
\bibitem[Hanisch \& Biemesderfer(1989)]{1989BAAS...21..780H} Hanisch, R.~J., \& Biemesderfer, C.~D.\ 1989, \baas, 21, 780 
\bibitem[Lamport(1994)]{lamport94} Lamport, L. 1994, LaTeX: A Document Preparation System, 2nd Edition (Boston, Addison-Wesley Professional)
\bibitem[Schwarz et al.(2011)]{2011ApJS..197...31S} Schwarz, G.~J., Ness, J.-U., Osborne, J.~P., et al.\ 2011, \apjs, 197, 31  
\bibitem[Vogt et al.(2014)]{2014ApJ...793..127V} Vogt, F.~P.~A., Dopita, M.~A., Kewley, L.~J., et al.\ 2014, \apj, 793, 127

\end{thebibliography}

%% This command is needed to show the entire author+affilation list when
%% the collaboration and author truncation commands are used.  It has to
%% go at the end of the manuscript.
%\allauthors

%% Include this line if you are using the \added, \replaced, \deleted
%% commands to see a summary list of all changes at the end of the article.
%\listofchanges

\end{document}

% End of file `sample62.tex'.

### 2019-05-31 rnaas.tex
Add AAS Template

%% rnaastex.cls is the classfile used for Research Notes. It is derived
%% from aastex61.cls with a few tweaks to allow for the unique format required.
%% (10/15/17)
%%\documentclass{rnaastex}

%% Better is to use the "RNAAS" style option in AASTeX v6.2
%% (01/08/18)
\documentclass[RNAAS]{aastex62}

%% Define new commands here
\newcommand\latex{La\TeX}

%% Tells LaTeX to search for image files in the
%% current directory as well as in the figures/ folder.
\graphicspath{{./}{figures/}}

\begin{document}

\title{An example of a Research Note of the American Astronomical Society (RNAAS)}

%% Note that the corresponding author command and emails has to come
%% before everything else. Also place all the emails in the \email
%% command instead of using multiple \email calls.
\correspondingauthor{August Muench}
\email{greg.schwarz@aas.org, august.muench@aas.org}

\author{Ethan Vishniac}
\altaffiliation{Editor-in-Chief}
\affiliation{Johns Hopkins University}

\author{Chris Lintott}
\altaffiliation{RNAAS Editor}
\affiliation{Oxford University}

%% The \author command can take an optional ORCID.
\author[0000-0002-0786-7307]{Greg J. Schwarz}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}

\author{August Muench}
\affiliation{American Astronomical Society \\
2000 Florida Ave., NW, Suite 300 \\
Washington, DC 20009-1231, USA}

%% Note that RNAAS manuscripts DO NOT have abstracts.
%% See the online documentation for the full list of available subject
%% keywords and the rules for their use.
\keywords{editorials, notices ---
miscellaneous --- catalogs --- surveys}

%% Start the main body of the article. If no sections in the
%% research note leave the \section call blank to make the title.
\section{}

\textit{Research Notes of the \href{https://aas.org}{American Astronomical Society}}
(\href{http://rnaas.aas.org}{RNAAS}) is a publication in the AAS portfolio
(alongside ApJ, AJ, ApJ Supplements, and ApJ Letters) through which authors can
promptly and briefly share materials of interest with the astronomical community
in a form that will be searchable via ADS and permanently archived.

The astronomical community has long faced a challenge in disseminating
information that may not meet the criteria for a traditional journal article.
There have generally been few options available for sharing works in progress,
comments and clarifications, null results, and timely reports of observations
(such as the spectrum of a supernova), as well as results that wouldn’t
traditionally merit a full paper (such as the discovery of a single exoplanet
or contributions to the monitoring of variable sources).

Launched in 2017, RNAAS was developed as a supported and long-term
communication channel for results such as these that would otherwise be
difficult to broadly disseminate to the professional community and persistently
archive for future reference.

Submissions to RNAAS should be brief communications - 1,000 words or fewer
\footnote{An easy way to count the number of words in a Research Note is to use
the \texttt{texcount} utility installed with most \latex\ installations. The
call  \texttt{texcount -incbib -v3 rnaas.tex}) gives 57 words in the front
matter and 493 words in the text/references/captions of this template. Another
option is by copying the words into MS/Word, and using ``Word Count'' under the
Tool tab.}, and no more than a single figure (e.g. Figure \ref{fig:1}) or table
(but not both) - and should be written in a style similar to that of a
traditional journal article, including references, where appropriate, but not
including an abstract.

Unlike the other journals in the AAS portfolio, RNAAS publications are not
peer reviewed; they are, however, reviewed by an editor for appropriateness
and format before publication. If accepted, RNAAS submissions are typically
published within 72 hours of manuscript receipt. Each RNAAS article is
issued a DOI and indexed by ADS \citep{2000A&AS..143...41K} to create a
long-term, citable record of work.

Articles can be submitted in \latex\ (preferably with the new "RNAAS"
style option in AASTeX v6.2), MS/Word, or via the direct submission in the
\href{http://www.authorea.com}{Authorea} or
\href{http://www.overleaf.com}{Overleaf} online collaborative editors.

Authors are expected to follow the AAS's ethics \citep{2006ApJ...652..847K},
including guidance on plagiarism \citep{2012AAS...21920404V}.

%% An example figure call using \includegraphics
\begin{figure}[h!]
\begin{center}
\includegraphics[scale=0.85,angle=0]{aas.pdf}
\caption{Top page of the AAS Journals' website, \url{http://journals.aas.org},
on October 15, 2017.  Each RNAAS manuscript is only allowed one figure or
table (but not both). Including the
\href{http://journals.aas.org//authors/data.html\#DbF}{data behind the figure}
in a Note is encouraged, and the data will be provided as a link in the
published Note.\label{fig:1}}
\end{center}
\end{figure}

%% An example table using AASTeX's deluxetable. Note that since
%% only one figure OR one table is allowed this is commented out.
%\begin{deluxetable}{ccl}
%\tablecaption{Example table some English and Greek letters\label{tab:1}}
%\tablehead{
%\colhead{Index number} & \colhead{English} & \colhead{Greek}
%}
%\startdata
%1 & a & alpha ($\alpha$) \\
%2 & b & beta ($\beta$) \\
%3 & c & gamma ($\gamma$) \\
%4 & d & delta ($\delta$) \\
%5 & e & epsilon ($\epsilon$) \\
%\enddata
%\tablecomments{Long tables should only show a short example with the full
%version as a machine readable table with the article.}
%\end{deluxetable}

\acknowledgments

Acknowledge people, facilities, and software here but remember that this counts
against your 1000 word limit.

\begin{thebibliography}{}

\bibitem[Kennicutt et al.(2006)]{2006ApJ...652..847K} Kennicutt, R.~C., Jr., Vishniac, E., \& Sneden, C.\ 2006, \apj, 652, 847

\bibitem[Kurtz et al.(2000)]{2000A&AS..143...41K} Kurtz, M.~J., Eichhorn, G., Accomazzi, A., et al.\ 2000, \aaps, 143, 41

\bibitem[Vishniac(2012)]{2012AAS...21920404V} Vishniac, E.~T.\ 2012, American Astronomical Society Meeting Abstracts \#219, 219, 204.04

\end{thebibliography}

\end{document}

### 2019-07-10 paper.tex
Add all the core authors
abstract and introduction added

@@
 %% this information may be modified by the editorial offices.
-\shorttitle{Sample article}
-\shortauthors{Schwarz et al.}
 %%
@@
 
-\correspondingauthor{Shreyas Bapat}
-\email{shreyas@einsteinpy.org, bapat.shreyas@gmail.com}
-
 \author[0000-0002-0870-4665]{Shreyas Bapat}
@@
 
-\author{August Muench}
-\affiliation{American Astronomical Society \\
-2000 Florida Ave., NW, Suite 300 \\
-Washington, DC 20009-1231, USA}
-\collaboration{(AAS Journals Data Scientists collaboration)}
-
-\author{Butler Burton}
-\affiliation{National Radio Astronomy Observatory}
-\affiliation{AAS Journals Associate Editor-in-Chief}
-\nocollaboration
-
-\author{Amy Hendrickson}
-\altaffiliation{Creator of AASTeX v6.2}
-\affiliation{TeXnology Inc.}
-\collaboration{(LaTeX collaboration)}
-
-\author{Julie Steffen}
-\affiliation{AAS Director of Publishing}
-\affiliation{American Astronomical Society \\
-2000 Florida Ave., NW, Suite 300 \\
-Washington, DC 20009-1231, USA}
-
-\author{Jeff Lewandowski}
-\affiliation{IOP Senior Publisher for the AAS Journals}
-\affiliation{IOP Publishing, Washington, DC 20005}
+\author{Bhavya Bhatt}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+
+\author{Ritwik Saha}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+
+\author{Priyanshu Khandelwal}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+\collaboration{(EinsteinPy Core Development)}
 
@@
 
-This example manuscript is intended to serve as a tutorial and template for
-authors to use when writing their own AAS Journal articles. The manuscript
-includes a history of \aastex\ and documents the new features in the
-previous versions as well as the new features in version 6.2. This
-manuscript includes many figure and table examples to illustrate these new
-features.  Information on features not explicitly mentioned in the article
-can be viewed in the manuscript comments or more extensive online
-documentation. Authors are welcome replace the text, tables, figures, and
-bibliography with their own and submit the resulting manuscript to the AAS
-Journals peer review system.  The first lesson in the tutorial is to remind
-authors that the AAS Journals, the Astrophysical Journal (ApJ), the
-Astrophysical Journal Letters (ApJL), and Astronomical Journal (AJ), all
-have a 250 word limit for the abstract\footnote{Note that manuscripts 
-submitted to the new Research Notes of the American Astronomical Society 
-(RNAAS) do \textbf{not} have abstracts.}.  If you exceed this length the
-Editorial office will ask you to shorten it.
+This paper presents EinsteinPy (version 0.2), a community-developed Python
+package for gravitational and relativistic astrophysics.
+Python is a free, easy to use high level programming language which have seen a huge expansion in the number of its users and developers in recent years.
+Many great frameworks came as Python packages which provides a very high level of abstraction glancing over the dirty nitty gitties of the algorithms and provide an easy to use coding interface.
+One example is Keras - Framework for deep learning which has made field like deep learning to become a easy to code task for its users.
+This example really demonstrates the power of abstraction which is achievable in Python.
+The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with a little or no background in computer programming and trying to enter the field of numerical relativity or trying to use simulations in his research.
+Currently EinsteinPy supports simulation of time-like and null geodesics and calculate trajectories in different background geometries some of which are Schwarzschild, Kerr and KerrNewmann along with coordinate inter-conversion pipeline.
+It has a partially developed pipeline for plotting and visualization with dependencies on libraries like plotly, matplotlib etc.
+One of the unique feature of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilites which is a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky.
+Currently EinsteinPy also provide few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.
+The current version of the library is in a state that can be used by any serious student of general relativity trying to get essence of this beautiful subject but is somewhere lost in the heavy mathematical formalism of the subject.
+EinsteinPy provides such students to really see through the equations and visualize whats really happening.
 
@@
 %% keywords and the rules for their use.
-\keywords{editorials, notices --- 
-miscellaneous --- catalogs --- surveys}
+\keywords{gravitational physics, astrophysics --- 
+simulations --- black holes --- gravitational waves}
 
@@
 \section{Introduction} \label{sec:intro}
-
-\latex\ \footnote{\url{http://www.latex-project.org/}} is a document markup
-language that is particularly well suited for the publication of
-mathematical and scientific articles \citep{lamport94}. \latex\ was written
-in 1985 by Leslie Lamport who based it on the \TeX\ typesetting language
-which itself was created by Donald E. Knuth in 1978.  In 1988 a suite of
-\latex\ macros were developed to investigate electronic submission and
-publication of AAS Journal articles \citep{1989BAAS...21..780H}.  Shortly
-afterwards, Chris Biemesdefer merged these macros and more into a \latex\
-2.08 style file called \aastex.  These early \aastex\ versions introduced
-many common commands and practices that authors take for granted today.
-Substantial revisions
-were made by Lee Brotzman and Pierre Landau when the package was updated to
-v4.0.  AASTeX v5.0, written in 1995 by Arthur Ogawa, upgraded to \latex\ 2e
-which uses the document class in lieu of a style file.  Other improvements
-to version 5 included hypertext support, landscape deluxetables and
-improved figure support to facilitate electronic submission.  
-\aastex\ v5.2 was released in 2005 and introduced additional graphics
-support plus new mark up to identifier astronomical objects, datasets and
-facilities.
-
-In 1996 Maxim Markevitch modified the AAS preprint style file, aaspp4.sty,
-to closely emulate the very tight, two column style of a typeset
-Astrophysical Journal article.  The result was emulateapj.sty.  A year
-later Alexey Vikhlinin took over development and maintenance.  In 2001 he
-converted emulateapj into a class file in \latex\ 2e and in 2003 Vikhlinin
-completely rewrote emulateapj based on the APS Journal's RevTEX class.
-
-During this time emulateapj gained growing acceptance in the astronomical
-community as it filled an author need to obtain an approximate number of
-manuscript pages prior to submission for cost and length estimates. The
-tighter typeset also had the added advantage of saving paper when printing
-out hard copies.
-
-Even though author publication charges are no longer based on print pages
-\footnote{see Section \ref{sec:pubcharge} in the Appendix for more details
-about how current article costs are calculated.} the emulateapj class file
-has proven to be extremely popular with AAS Journal authors.  An informal
-analysis of submitted \latex\ manuscripts in 2015 revealed that $\sim$65\%
-either called emulateapj or have a commented emulateapj classfile call
-indicating it was used at some stage of the manuscript construction.
-Clearly authors want to have access to a tightly typeset version of the
-article when corresponding with co-authors and for preprint submissions.
-
-When planning the next \aastex\ release the popularity of emulateapj played
-an important roll in the decision to drop the old base code and adopt and
-modify emulateapj for \aastex\ v6.+ instead.  The change brings \aastex\
-inline with what the majority of authors are already using while still
-delivering new and improved features.  \aastex\ v6.0 through v6.2 were written
-by Amy Hendrickson and released in January 2016 (v6.0), October 2016 (v6.1),
-and January 2018 (v6.2), respectively.  Some of the new features in v6.0 
-included:
-
-\begin{enumerate}
-\item improved citations for third party data repositories and software,
-\item easier construction of matrix figures consisting of multiple 
-encapsulated postscript (EPS) or portable document format (PDF) files,
-\item figure set mark up for large collections of similar figures,
-\item color mark up to easily enable/disable revised text highlighting,
-\item improved url support, and
-\item numerous table options such as the ability to hide columns, column 
-decimal alignment, automatic column math mode and numbering, plus splitting of
-wide tables.
-\end{enumerate}
-
-The features in v6.1 were:
-
-\begin{enumerate}
-\item ORCID support for preprints,
-\item improved author, affiliation and collaboration mark up,
-\item reintroduced the old AASTeX v5.2 {\tt\string\received}, 
-      {\tt\string\revised}, {\tt\string\accepted}, and
-      {\tt\string\published} commands plus
-      added the new {\tt\string\submitjournal} command to document
-      which AAS Journal the manuscript was submitted to, plus
-\item new typeset style options.
-\end{enumerate}
-
-The new features in v6.2 are:
-
-\begin{enumerate}
-\item A new RNAAS style option for Research Note manuscripts,
-\item Titles no longer put in all caps,
-\item No page skip between the title page and article body,
-\item re-introduce RevTeX's widetext environment for long lines in
-      two column style formats, and
-\item upgrade to the {\tt\string\doi} command.
-\end{enumerate}
-
-The rest of this article provides information and examples on how to create
-your own AAS Journal manuscript with v6.2.  Special emphasis is placed on
-how to use the full potential of \aastex\ v6+.  The next section describes
-the different manuscript styles available and how they differ from past
-releases.  Section \ref{sec:floats} describes how tables and figures are
-placed in a \latex\ document. Specific examples of tables, Section
-\ref{subsec:tables}, and figures, Section \ref{subsec:figures}, are also
-provided.  Section \ref{sec:displaymath} discusses how to display math and
-incorporate equations in a manuscript while Section \ref{sec:highlight}
-discuss how to use the new revision mark up.  The last section,
-\ref{sec:cite}, shows how recognize software and external data as first
-class references in the manuscript bibliography.  An appendix is included
-to show how to construct one and provide some information on how article
-charges are calculated.  Additional information is available both embedded
-in the comments of this \latex\ file and in the online documentation at
-\url{http://journals.aas.org/authors/aastex.html}.
-
+It was the time of 1915 when Einstein published his paper on general theory of relativity which proposed a elegant and rigorous framework for a relativistic theory of gravity and was generalized version of gravity free theory - special relativity which he published earlier in 1905 and since then the whole physics community was against the bold ideas of the young genius and resisted in the beginning because all people were worried that if these hypothesis true would then completely change our notion of how we percieve space and time.
+But sooner they started to realize the true depth in the formalism of general relativity and its ability to explain the fundamental laws of nature.
+After so many years its well established now that general theory of relativity is the "theory of gravity" in classical regime and all the attempts to formulate quantum theory of gravity one way or the other borrow ideas from GR.
+The central problem then and now remains to be the solutions of the Einstein's field equation.
+Many times we can study the behaviour of solutions under high degree of symmetry considerations and could even be solved analytically for highly unrealistic systems but for solving it for problems relevant to astrophysical and gravitational physics research it still remains a big question on how to get around the problem of solving these field equations.
+This question is so profound that it has a separate research field which goes with the name of numerical relativity which attempts to use computer programmes to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics is happening (as we can not solve for a infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
+The interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining.
+After so many years the field of numerical relativity has grown up to be a mature research area with vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones).
+Currently there exist some very robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.
+Now on the other end of the research community are the theoretical physicists many of which have little or no programming experience and is really challenged by the fact that the usage of these frameworks demands heavy use of high level programming
+in languages like C and C++.
+As described above Python provides a vast room for abstractions and no library existed at that time that do numerical relativity in Python and hence the team was hooked by this very fact of need for a python library on general relativity.
+Since then EinsteinPy has seen a lot of contributions from people all over the world and many "good to go" functionalities are already provided in this and previous versions.
+Like any other numerical relativity library EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to dive deep into the nitty gitties of the subject along with few very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity in general\footnote{More details on this are given in further coming sections}.
+In further coming section we will discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming version.
+Also we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
 \section{Manuscript styles} \label{sec:style}
@@
 %% and to override the normal way of calculating a float position
-\begin{figure}[ht!]
-\plotone{cost-eps-converted-to.pdf}
-\caption{The subscription and author publication costs from 1991 to 2013.
-The data comes from Table \ref{tab:table}.\label{fig:general}}
-\end{figure}
 
@@
 \begin{figure}
-\plottwo{RS_Oph-eps-converted-to.pdf}{U_Sco-eps-converted-to.pdf}
+
 \caption{Swift/XRT X-ray light curves of RS Oph and U Sco which represent
@@
 
-\begin{figure*}
-\gridline{\fig{V2491_Cyg-eps-converted-to.pdf}{0.3\textwidth}{(a)}
-          \fig{CSS081007-eps-converted-to.pdf}{0.3\textwidth}{(b)}
-          \fig{LMC_2009-eps-converted-to.pdf}{0.3\textwidth}{(c)}
-          }
-\gridline{\fig{RS_Oph-eps-converted-to.pdf}{0.3\textwidth}{(d)}
-          \fig{U_Sco-eps-converted-to.pdf}{0.3\textwidth}{(e)}
-          }
-\gridline{\fig{KT_Eri-eps-converted-to.pdf}{0.3\textwidth}{(f)}}
-\caption{Inverted pyramid figure of six individual files. The nova are
-(a) V2491 Cyg, (b) HV Cet, (c) LMC 2009, (d) RS Oph, (e) U Sco, and
-(f) KT Eri.\label{fig:pyramid}}
-\end{figure*}
-
 \subsection{Figure sets}
@@
 \begin{figure}
-\plotone{KT_Eri-eps-converted-to.pdf}
 \caption{The Swift/XRT X-ray light curve for the first year after
@@
 \begin{figure}
-\plotone{video3-eps-converted-to.pdf}
 \caption{Example image from the animation which is available in the electronic

### 2019-07-10 paper.tex
some changes

@@
 %% manuscript itself with \begin{document}.
-
 \begin{document}
@@
 The central problem then and now remains to be the solutions of the Einstein's field equation.
-Many times we can study the behaviour of solutions under high degree of symmetry considerations and could even be solved analytically for highly unrealistic systems but for solving it for problems relevant to astrophysical and gravitational physics research it still remains a big question on how to get around the problem of solving these field equations.
+Many times we can study the behaviour of solutions under high degree of symmetry considerations and could even solve analytically for highly unrealistic systems but solving it for problems relevant to astrophysical and gravitational physics research it still remains a big question on how to get around the problem of solving these field equations.
 This question is so profound that it has a separate research field which goes with the name of numerical relativity which attempts to use computer programmes to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics is happening (as we can not solve for a infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
@@
 After so many years the field of numerical relativity has grown up to be a mature research area with vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones).
-Currently there exist some very robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.
-Now on the other end of the research community are the theoretical physicists many of which have little or no programming experience and is really challenged by the fact that the usage of these frameworks demands heavy use of high level programming
-in languages like C and C++.
+Currently there exist some very robust and involved frameworks that provide a complete programming ecosystem and have proved to an be essential tools for any numerical relativity researcher.
+Now on the other end of the research community are the theoretical physicists many of which have little or no programming experience and is really challenged by the fact that the usage of these frameworks demand heavy use of high level programming languages like C and C++.
 As described above Python provides a vast room for abstractions and no library existed at that time that do numerical relativity in Python and hence the team was hooked by this very fact of need for a python library on general relativity.
@@
 Like any other numerical relativity library EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to dive deep into the nitty gitties of the subject along with few very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity in general\footnote{More details on this are given in further coming sections}.
-In further coming section we will discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming version.
+In further coming section we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.
 Also we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
-\section{Manuscript styles} \label{sec:style}
+\section{Data Types} \label{sec:style}
+The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with varieties of gravitational physics problems.
+The most important and central quantity in all of the general relativity is the metric tensor which defines the background geometry of spacetime on which all the dynamics happen.
+EinsteinPy provides class metric
+\subsection{metric}
+\subsection{plotting}
+\subsection{symbolic}
+\subsection{coordinates}
+\subsection{hypersurface}
 

### 2019-07-10 paper.tex
Add authors till now

@@
 
+\author[0000-0002-2268-9772]{Sofía Ortín Vela}
+\affil{Department of Theoretical Physics, University of Zaragoza \\
+Zaragoza, Spain}
+
+\author[0000-0001-8530-7252]{Jialin Ma}
+\affil{Georgia Institute of Technology, GA 30332, USA}
+
+\author[0000-0001-8530-7252]{Jialin Ma}
+\affil{Georgia Institute of Technology, GA 30332, USA}
+
+\author[0000-0001-7234-6148]{Varun Singh}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+
+\author[0000-0002-1900-3338]{Shilpi Jain}
+\affiliation{Department of Earth Sciences, Indian Institute of Technology Roorkee, India}
+
+\author[0000-0002-7179-3795]{Alpesh Jamgade}
+\affiliation{Department of Mathematics, Bharath Institute of Higher Education and Research, Chennai, India}
+
+\author[0000-0002-5198-9010]{Manvi Gupta}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+
+\author{Tushar Tyagi}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+
+\author[0000-0003-1838-8368]{Tanmay Rustagi}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+
+\author[0000-0002-0757-2883]{Abhijeet Manhas}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
+Mandi, Himachal Pradesh, 175005, India}
+
+\author[0000-0001-5558-9447]{Raphael Reyna}
+\affiliation{California State Polytechnic University, Pomona}
+
+\author[0000-0001-8302-1584]{Sashank Mishra}
+\affiliation{Department of Information Technology, Indian Institute of Information Technology Allahabad}
+\collaboration{(EinsteinPy Package Contributors)}
 %% Note that the \and command from previous versions of AASTeX is now

### 2019-07-10 paper.tex
contributors added

@@
 The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with varieties of gravitational physics problems.
-The most important and central quantity in all of the general relativity is the metric tensor which defines the background geometry of spacetime on which all the dynamics happen.
-EinsteinPy provides class metric
+The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen.
+Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satifies the following Einstein's field equation
+\[
+R_{\mu\nu} - \frac{1}{2}Rg_{\mu\nu} + \Lambda g_{\mu\nu} = \frac{8\pi G}{c^4}T_{\mu\nu}
+\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar $\Lambda$ is cosmological constant.
+All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation is terms involving $g_{\mu\nu}$ and on the right hand side is the matter field terms which only characterize the distribution of matter because of which the spacetime geometry is curved.\\
+EinsteinPy provides a core module: metric which has core data types of various metric tensors some which includes Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are exact solution of field equation for very specific matter distributions).
+The immediate functionalities which comes along with this module is solution of geodesic equations.
+The module has coupled integration with coordinates module which deals with different coordinate systems transformations\footnote{more on this in the 'coordinates' section}.
+Another core data types is in the plotting module which handles all the plotting, rendering, animation and simulation related methods and provides a user friendly interfacing of plots.
+One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremly important in the formalism of general relativity and many begineers find it
 \subsection{metric}

### 2019-07-10 paper.tex
Fix half of the abstract!

@@
 
-\title{EinsteinPy: Python for General Relativity\footnote{Released on January, 8th, 2018}}
+\title{EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}}
 
@@
 \author[0000-0002-0870-4665]{Shreyas Bapat}
-\affil{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
 \author{Bhavya Bhatt}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
 \author{Ritwik Saha}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
-
-\author{Priyanshu Khandelwal}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
-\collaboration{(EinsteinPy Core Development)}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+
+\author[0000-0003-1021-3336]{Priyanshu Khandelwal}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\collaboration{(EinsteinPy Core Development Committee)}
 
 \author[0000-0002-2268-9772]{Sofía Ortín Vela}
-\affil{Department of Theoretical Physics, University of Zaragoza \\
-Zaragoza, Spain}
+\affil{Department of Theoretical Physics, University of Zaragoza, Spain}
 
 \author[0000-0001-8530-7252]{Jialin Ma}
-\affil{Georgia Institute of Technology, GA 30332, USA}
-
-\author[0000-0001-8530-7252]{Jialin Ma}
-\affil{Georgia Institute of Technology, GA 30332, USA}
+\affil{Georgia Institute of Technology, USA}
 
 \author[0000-0001-7234-6148]{Varun Singh}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
@@
 \author[0000-0002-5198-9010]{Manvi Gupta}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
 \author{Tushar Tyagi}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
 \author[0000-0003-1838-8368]{Tanmay Rustagi}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
 \author[0000-0002-0757-2883]{Abhijeet Manhas}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi \\
-Mandi, Himachal Pradesh, 175005, India}
+\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
@@
 package for gravitational and relativistic astrophysics.
-Python is a free, easy to use high level programming language which have seen a huge expansion in the number of its users and developers in recent years.
-Many great frameworks came as Python packages which provides a very high level of abstraction glancing over the dirty nitty gitties of the algorithms and provide an easy to use coding interface.
-One example is Keras - Framework for deep learning which has made field like deep learning to become a easy to code task for its users.
+Python is a free, easy to use high level programming language which has seen a huge expansion in the number of its users and developers in recent years.
+Specifically, a lot of recent studies show that the use of Python in Astrophysics and in general physics has increased exponentially.
+Many great frameworks came as Python packages which provide a very high level of abstraction over the dirty nitty-gritty of complex algorithms and provide an easy to use interfaceand pleasing user experience.
+One such example is Keras - framework for deep learning which has made deep learning so easy that a person with zero programming knowledge can also train a neural network classifier.
 This example really demonstrates the power of abstraction which is achievable in Python.
-The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with a little or no background in computer programming and trying to enter the field of numerical relativity or trying to use simulations in his research.
+The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with a little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.
 Currently EinsteinPy supports simulation of time-like and null geodesics and calculate trajectories in different background geometries some of which are Schwarzschild, Kerr and KerrNewmann along with coordinate inter-conversion pipeline.

### 2019-07-10 paper.tex
New Changes

@@
 %% manuscript itself with \begin{document}.
+\usepackage{listings}
+\usepackage{minted}
 \begin{document}
@@
 \]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar $\Lambda$ is cosmological constant.
-All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation is terms involving $g_{\mu\nu}$ and on the right hand side is the matter field terms which only characterize the distribution of matter because of which the spacetime geometry is curved.\\
+All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation are terms involving $g_{\mu\nu}$ and on the right hand side are the matter field terms which only characterize the distribution of matter because of which the spacetime geometry is curved.\\
 EinsteinPy provides a core module: metric which has core data types of various metric tensors some which includes Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are exact solution of field equation for very specific matter distributions).
@@
 Another core data types is in the plotting module which handles all the plotting, rendering, animation and simulation related methods and provides a user friendly interfacing of plots.
-One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremly important in the formalism of general relativity and many begineers find it
+One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremly important in the formalism of general relativity and one of the first challenges faced by many beginners in their journey of learning the subject.
+EinsteinPy provides an excellent way to learn the math behind tensor manipulation and index gymnastics with the help of symbolic module: symbolic, on which more will be dicussed in its section ahead.\\
+Following sections will give a breif overview of every core module and some of their important functionalities. 
 \subsection{metric}
+metric module gives user the freedom to define metric object which can be further used in the computations related to spacetime geometry.
+Let's see an small example of solving geodesic equation in Schwarzschild spacetime and obtaining trajectories using EinsteinPy
+\begin{minted}[linenos]{python}
+from einsteinpy.metric import Schwarzschild
+mass = 
+metric_obj = Schwarzschild(mass)
+\end{minted}
 \subsection{plotting}

### 2019-07-11 paper.tex
some removal of unwanted sections from template

@@
 Also we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
+\section{Units Handling}
+EinsteinPy has dependencies on Astropy for handling units and user have to use appropiate Astropy units\footnote{more on astropy units can be refered from their official website documentation} while declaring the input data to various methods which are further used in computation.
 \section{Data Types} \label{sec:style}
@@
 All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation are terms involving $g_{\mu\nu}$ and on the right hand side are the matter field terms which only characterize the distribution of matter because of which the spacetime geometry is curved.\\
-EinsteinPy provides a core module: metric which has core data types of various metric tensors some which includes Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are exact solution of field equation for very specific matter distributions).
+EinsteinPy provides a core module: \texttt{metric} which has core data types of various metric tensors some which includes Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are exact solution of field equation for very specific matter distributions).
 The immediate functionalities which comes along with this module is solution of geodesic equations.
-The module has coupled integration with coordinates module which deals with different coordinate systems transformations\footnote{more on this in the 'coordinates' section}.
-Another core data types is in the plotting module which handles all the plotting, rendering, animation and simulation related methods and provides a user friendly interfacing of plots.
+The module has coupled integration with \texttt{coordinates} module which deals with different coordinate system transformations\footnote{more on this in the 'coordinates' section}.
+Another core data types is in the \texttt{plotting} module which handles all the plotting, rendering, animation and simulation related methods and provides a user friendly interfacing of plots.
 One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremly important in the formalism of general relativity and one of the first challenges faced by many beginners in their journey of learning the subject.
-EinsteinPy provides an excellent way to learn the math behind tensor manipulation and index gymnastics with the help of symbolic module: symbolic, on which more will be dicussed in its section ahead.\\
+EinsteinPy provides an excellent way to learn the math behind tensor manipulation and index gymnastics with the help of symbolic module: \texttt{symbolic}, on which more will be dicussed in its section ahead.\\
 Following sections will give a breif overview of every core module and some of their important functionalities. 
 \subsection{metric}
-metric module gives user the freedom to define metric object which can be further used in the computations related to spacetime geometry.
-Let's see an small example of solving geodesic equation in Schwarzschild spacetime and obtaining trajectories using EinsteinPy
+\texttt{metric} module give users the freedom to define metric object which can be further used in the computations related to spacetime geometry.
+Let's see an small example of solving geodesic equation in Kerr spacetime and obtaining trajectories using EinsteinPy
+\subsection{coordinates}
 \begin{minted}[linenos]{python}
-from einsteinpy.metric import Schwarzschild
-mass = 
-metric_obj = Schwarzschild(mass)
+# importing modules
+from astropy import units as u
+import numpy as np
+from einsteinpy.metric import Kerr
+from einsteinpy.coordinates import BoyerLindquistDifferential
+
+# initializing parameters and coordinate system
+M = 1.989e30 * u.kg
+a = 0.3 * u.m
+BL_obj = BoyerLindquistDifferential(50e5 * u.km, np.pi / 2 * u.rad, np.pi * u.rad,
+                                    0 * u.km / u.s, 0 * u.rad / u.s, 0 * u.rad / u.s,
+                                    a)
+end_lambda = ((1 * u.year).to(u.s)).value / 930
+
+# Choosing stepsize for ODE solver to be 0.02 minutes
+stepsize = ((0.02 * u.min).to(u.s)).value
+
+# defining Kerr spacetime metric object
+obj = Kerr.from_coords(BL_obj, M)
+
+# calculates the trajectory
+ans = obj.calculate_trajectory(
+    end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
+)
 \end{minted}
@@
 \subsection{symbolic}
-\subsection{coordinates}
 \subsection{hypersurface}
-
-The default style in \aastex\ v6.2 is a tight single column style, e.g.  10
-point font, single spaced.  The single column style is very useful for
-article with wide equations. It is also the easiest to style to work with
-since figures and tables, see Section \ref{sec:floats}, will span the
-entire page, reducing the need for address float sizing.
-
-To invoke a two column style similar to the what is produced in
-the published PDF copy use \\
-
-\noindent {\tt\string\documentclass[twocolumn]\{aastex62\}}. \\
-
-\noindent Note that in the two column style figures and tables will only
-span one column unless specifically ordered across both with the ``*'' flag,
-e.g. \\
-
-\noindent{\tt\string\begin\{figure*\}} ... {\tt\string\end\{figure*\}}, \\
-\noindent{\tt\string\begin\{table*\}} ... {\tt\string\end\{table*\}}, and \\
-\noindent{\tt\string\begin\{deluxetable*\}} ... {\tt\string\end\{deluxetable*\}}. \\
-
-\noindent This option is ignored in the onecolumn style.
-
-Some other style options are outlined in the commented sections of this 
-article.  Any combination of style options can be used.
-
-Two style options that are needed to fully use the new revision tracking
-feature, see Section \ref{sec:highlight}, are {\tt\string linenumbers} which 
-uses the lineno style file to number each article line in the left margin and 
-{\tt\string trackchanges} which controls the revision and commenting highlight
-output.
-
-There is also a new {\tt\string modern} option that uses a Daniel
-Foreman-Mackey and David Hogg design to produce stylish, single column
-output that has wider left and right margins. It is designed to have fewer
-words per line to improve reader retention. It also looks better on devices
-with smaller displays such as smart phones.
-
-For a Research Note use the {\tt\string RNAAS} option which will produce a
-manuscript with no abstract and in the {\tt\string modern} style.
-
-\section{Floats} \label{sec:floats}
-
-Floats are non-text items that generally can not be split over a page.
-They also have captions and can be numbered for reference.  Primarily these
-are figures and tables but authors can define their own. \latex\ tries to
-place a float where indicated in the manuscript but will move it later if
-there is not enough room at that location, hence the term ``float''.
-
-Authors are encouraged to embed their tables and figures within the text as
-they are mentioned.  Please do not place the figures and text at the end of
-the article as was the old practice.  Editors and the vast majority of
-referees find it much easier to read a manuscript with embedded figures and
-tables.
-
-Depending on the number of floats and the particular amount of text and
-equations present in a manuscript the ultimate location of any specific
-float can be hard to predict prior to compilation. It is recommended that
-authors textbf{not} spend significant time trying to get float placement
-perfect for peer review.  The AAS Journal's publisher has sophisticated
-typesetting software that will produce the optimal layout during
-production.
-
-Note that authors of Research Notes are only allowed one float, either one
-table or one figure.
-
-\startlongtable
-\begin{deluxetable}{c|cc}
-\tablecaption{ApJ costs from 1991 to 2013\tablenotemark{a} \label{tab:table}}
-\tablehead{
-\colhead{Year} & \colhead{Subscription} & \colhead{Publication} \\
-\colhead{} & \colhead{cost} & \colhead{charges\tablenotemark{b}}\\
-\colhead{} & \colhead{(\$)} & \colhead{(\$/page)}
-}
-\colnumbers
-\startdata
-1991 & 600 & 100 \\
-1992 & 650 & 105 \\
-1993 & 550 & 103 \\
-1994 & 450 & 110 \\
-1995 & 410 & 112 \\
-1996 & 400 & 114 \\
-1997 & 525 & 115 \\
-1998 & 590 & 116 \\
-1999 & 575 & 115 \\
-2000 & 450 & 103 \\
-2001 & 490 &  90 \\
-2002 & 500 &  88 \\
-2003 & 450 &  90 \\
-2004 & 460 &  88 \\
-2005 & 440 &  79 \\
-2006 & 350 &  77 \\
-2007 & 325 &  70 \\
-2008 & 320 &  65 \\
-2009 & 190 &  68 \\
-2010 & 280 &  70 \\
-2011 & 275 &  68 \\
-2012 & 150 &  56 \\
-2013 & 140 &  55 \\
-\enddata
-\tablenotetext{a}{Adjusted for inflation}
-\tablenotetext{b}{Accounts for the change from page charges to digital quanta in April, 2011}
-\tablecomments{Note that {\tt \string \colnumbers} does not work with the 
-vertical line alignment token. If you want vertical lines in the headers you
-can not use this command at this time.}
-\end{deluxetable}
-
-For authors that do want to take the time to optimize the locations of
-their floats there are some techniques that can be used.  The simplest
-solution is to placing a float earlier in the text to get the position
-right but this option will break down if the manuscript is altered, see
-Table \ref{tab:table}.  A better method is to force \latex\ to place a
-float in a general area with the use of the optional {\tt\string [placement
-specifier]} parameter for figures and tables. This parameter goes after
-{\tt\string \begin\{figure\}}, {\tt\string \begin\{table\}}, and
-{\tt\string \begin\{deluxetable\}}.  The main arguments the specifier takes
-are ``h'', ``t'', ``b'', and ``!''.  These tell \latex\ to place the float
-\underline{h}ere (or as close as possible to this location as possible), at
-the \underline{t}op of the page, and at the \underline{b}ottom of the page.
-The last argument, ``!'', tells \latex\ to override its internal method of
-calculating the float position.  A sequence of rules can be created by
-using multiple arguments.  For example, {\tt\string \begin\{figure\}[htb!]}
-tells \latex\ to try the current location first, then the top of the page
-and finally the bottom of the page without regard to what it thinks the
-proper position should be.  Many of the tables and figures in this article
-use a placement specifier to set their positions.
-
-Note that the \latex\ {\tt\string tabular} environment is not a float.  Only
-when a {\tt\string tabular} is surrounded by {\tt\string\begin\{table\}} ...
-{\tt\string\end\{table\}} is it a true float and the rules and suggestions
-above apply.
-
-In AASTeX v6.2 all deluxetables are float tables and thus if they are
-longer than a page will spill off the bottom. Long deluxetables should
-begin with the {\tt\string\startlongtable} command. This initiates a
-longtable environment.  Authors might have to use {\tt\string\clearpage} to
-isolate a long table or optimally place it within the surrounding text.
-
-\begin{deluxetable*}{ccCrlc}[b!]
-\tablecaption{Column math mode in an observation log \label{tab:mathmode}}
-\tablecolumns{6}
-\tablenum{2}
-\tablewidth{0pt}
-\tablehead{
-\colhead{UT start time\tablenotemark{a}} &
-\colhead{MJD start time\tablenotemark{a}} &
-\colhead{Seeing} & \colhead{Filter} & \colhead{Inst.} \\
-\colhead{(YYYY-mm-dd)} & \colhead{(d)} &
-\colhead{(arcsec)} & \colhead{} & \colhead{}
-}
-\startdata
-2012-03-26 & 56012.997 & \sim 0.\arcsec5 & H$\alpha$ & NOT \\
-2012-03-27 & 56013.944 & 1.\arcsec5 & grism & SMARTS \\
-2012-03-28 & 56014.984 & \nodata & F814M & HST \\
-2012-03-30 & 56016.978 & 1.\arcsec5\pm0.25 & B\&C & Bok \\
-\enddata
-\tablenotetext{a}{At exposure start.}
-\tablecomments{The ``C'' command column identifier in the 3 column turns on
-math mode for that specific column. One could do the same for the next
-column so that dollar signs would not be needed for H$\alpha$
-but then all the other text would also be in math mode and thus typeset
-in Latin Modern math and you will need to put it back to Roman by hand.
-Note that if you do change this column to math mode the dollar signs already
-present will not cause a problem. Table \ref{tab:mathmode} is published 
-in its entirety in the machine readable format.  A portion is
-shown here for guidance regarding its form and content.}
-\end{deluxetable*}
-
-\subsection{Tables} \label{subsec:tables}
-
-Tables can be constructed with \latex's standard table environment or the
-\aastex's deluxetable environment. The deluxetable construct handles long
-tables better but has a larger overhead due to the greater amount of
-defined mark up used set up and manipulate the table structure.  The choice
-of which to use is up to the author.  Examples of both environments are
-used in this manuscript. Table \ref{tab:table} is a simple deluxetable
-example that gives the approximate changes in the subscription costs and
-author publication charges from 1991 to 2013.
-
-Tables longer than 200 data lines and complex tables should only have a
-short example table with the full data set available in the machine
-readable format.  The machine readable table will be available in the HTML
-version of the article with just a short example in the PDF. Authors are
-required to indicate to the reader where the data can be obtained in the
-table comments.  Suggested text is given in the comments of Table
-\ref{tab:mathmode}.  Authors are encouraged to create their own machine
-readable tables using the online tool at
-\url{http://authortools.aas.org/MRT/upload.html}.
-
-\aastex\ v6 introduces five new table features that are designed to make
-table construction easier and the resulting display better for AAS Journal
-authors.  The items are:
-
-\begin{enumerate}
-\item Declaring math mode in specific columns,
-\item Column decimal alignment, 
-\item Automatic column header numbering,
-\item Hiding columns, and
-\item Splitting wide tables into two or three parts.
-\end{enumerate}
-
-Each of these new features are illustrated in following Table examples.
-All five features work with the regular \latex\ tabular environment and in
-\aastex's deluxetable environment.  The examples in this manuscript also
-show where the two process differ.
-
-\subsubsection{Column math mode}
-
-Both the \latex\ tabular and \aastex\ deluxetable require an argument to
-define the alignment and number of columns.  The most common values are
-``c'', ``l'' and ``r'' for \underline{c}enter, \underline{l}eft, and
-\underline{r}ight justification.  If these values are capitalized, e.g.
-``C'', ``L'', or ``R'', then that specific column will automatically be in math
-mode meaning that \$s are not required.  Note that having embedded dollar
-signs in the table does not affect the output.  The third and forth columns
-of Table \ref{tab:mathmode} shows how this math mode works.
-
-\subsubsection{Decimal alignment}
-
-Aligning a column by the decimal point can be difficult with only center,
-left, and right justification options.  It is possible to use phantom calls
-in the data, e.g. {\tt\string\phn}, to align columns by hand but this can
-be tedious in long or complex tables.  To address this \aastex\ introduces
-the {\tt\string\decimals} command and a new column justification option,
-``D'', to align data in that column on the decimal.  In deluxetable the
-{\tt\string\decimals} command is invoked before the {\tt\string\startdata}
-call but can be anywhere in \latex's tabular environment.
-
-Two other important thing to note when using decimal alignment is that each
-decimal column \textit{must end with a space before the ampersand}, e.g.
-``\&\&'' is not allowed.  Empty decimal columns are indicated with a decimal,
-e.g. ``.''.  Do not use deluxetable's {\tt\string\nodata} command.
-
-The ``D'' alignment token works by splitting the column into two parts on the
-decimal.  While this is invisible to the user one must be aware of how it
-works so that the headers are accounted for correctly.  All decimal column
-headers need to span two columns to get the alignment correct. This can be
-done with a multicolumn call, e.g {\tt\string\multicolumn2c\{\}} or
-{\tt\string\multicolumn\{2\}\{c\}\{\}}, or use the new
-{\tt\string\twocolhead\{\}} command in deluxetable.  Since \latex\ is
-splitting these columns into two it is important to get the table width
-right so that they appear joined on the page.  You may have to run the
-\latex\ compiler twice to get it right.  Table \ref{tab:decimal}
-illustrates how decimal alignment works in the tabular environment with a
-$\pm$ symbol embedded between the last two columns.
-
-%% Note that the \setcounter and \renewcommand are needed here because
-%% this example is using a mix of deluxetable and tabular.  Here the
-%% deluxetable counters are set with \tablenum but the situation is a bit
-%% more complex for tabular.  Use the first command to set the Table number
-%% to ONE LESS than it should be.  The next command will auto increment it
-%% to the desired number.
-\setcounter{table}{2}
-\begin{table}[h!]
-\renewcommand{\thetable}{\arabic{table}}
-\centering
-\caption{Decimal alignment made easy} \label{tab:decimal}
-\begin{tabular}{cD@{$\pm$}D}
-\tablewidth{0pt}
-\hline
-\hline
-Column & \multicolumn2c{Value} & \multicolumn2c{Uncertainty}\\
-\hline
-\decimals
-A & 1234     & 100.0     \\
-B &  123.4   &  10.1     \\
-C &  12.34   &   1.01    \\
-D &   1.234  &   0.101   \\
-E &    .1234 &   0.01001 \\
-F &   1.0    &    .      \\
-\hline
-\multicolumn{5}{c}{NOTE. - Two decimal aligned columns}
-\end{tabular}
-\end{table}
-
-\subsubsection{Automatic column header numbering} \label{subsubsec:autonumber}
-
-The command {\tt\string\colnumbers} can be included to automatically number
-each column as the last row in the header. Per the AAS Journal table format
-standards, each column index numbers will be surrounded by parentheses. In
-a \latex\ tabular environment the {\tt\string\colnumbers} should be invoked
-at the location where the author wants the numbers to appear, e.g. after
-the last line of specified table header rows. In deluxetable this command
-has to come before {\tt\string\startdata}.  {\tt\string\colnumbers} will
-not increment for columns hidden by the ``h'' command, see Section
-\ref{subsubsec:hide}.  Table \ref{tab:table} uses this command to
-automatically generate column index numbers.
-
-Note that when using decimal alignment in a table the command 
-{\tt\string\decimalcolnumbers} must be used instead of 
-{\tt\string\colnumbers} and {\tt\string\decimals}. Table \ref{tab:messier}
-illustrates this specific functionality.
-
-\subsubsection{Hiding columns} \label{subsubsec:hide}
-
-Entire columns can be \underline{h}idden from display simply by changing
-the specified column identifier to ``h''.  In the \latex\ tabular environment
-this column identifier conceals the entire column including the header
-columns.   In \aastex's deluxetables the header row is specifically
-declared with the {\tt\string\tablehead} call and each header column is
-marked with {\tt\string\colhead} call.  In order to make a specific header
-disappear with the ``h'' column identifier in deluxetable use 
-{\tt\string\nocolhead} instead to suppress that particular column header.
-
-Authors can use this option in many different ways.  Since column data can
-be easily suppressed authors can include extra information and hid it
-based on the comments of co-authors or referees.  For wide tables that will
-have a machine readable version, authors could put all the information in
-the \latex\ table but use this option to hid as many columns as needed until
-it fits on a page. This concealed column table would serve as the
-example table for the full machine readable version.  Regardless of how
-columns are obscured, authors are responsible for removing any unneeded
-column data or alerting the editorial office about how to treat these
-columns during production for the final typeset article.
-
-Table \ref{tab:messier} provides some basic information about the first ten
-Messier Objects and illustrates how many of these new features can be used
-together.  It has automatic column numbering, decimal alignment of the
-distances, and one concealed column.  The Common name column
-is the third in the \latex\ deluxetable but does not appear when the article
-is compiled. This hidden column can be shown simply by changing the ``h'' in
-the column identifier preamble to another valid value.  This table also
-uses {\tt\string\tablenum} to renumber the table because a \latex\ tabular
-table was inserted before it.
-
-\begin{deluxetable*}{cchlDlc}
-\tablenum{4}
-\tablecaption{Fun facts about the first 10 messier objects\label{tab:messier}}
-\tablewidth{0pt}
-\tablehead{
-\colhead{Messier} & \colhead{NGC/IC} & \nocolhead{Common} & \colhead{Object} &
-\multicolumn2c{Distance} & \colhead{} & \colhead{V} \\
-\colhead{Number} & \colhead{Number} & \nocolhead{Name} & \colhead{Type} &
-\multicolumn2c{(kpc)} & \colhead{Constellation} & \colhead{(mag)}
-}
-\decimalcolnumbers
-\startdata
-M1 & NGC 1952 & Crab Nebula & Supernova remnant & 2 & Taurus & 8.4 \\
-M2 & NGC 7089 & Messier 2 & Cluster, globular & 11.5 & Aquarius & 6.3 \\
-M3 & NGC 5272 & Messier 3 & Cluster, globular & 10.4 & Canes Venatici &  6.2 \\
-M4 & NGC 6121 & Messier 4 & Cluster, globular & 2.2 & Scorpius & 5.9 \\
-M5 & NGC 5904 & Messier 5 & Cluster, globular & 24.5 & Serpens & 5.9 \\
-M6 & NGC 6405 & Butterfly Cluster & Cluster, open & 0.31 & Scorpius & 4.2 \\
-M7 & NGC 6475 & Ptolemy Cluster & Cluster, open & 0.3 & Scorpius & 3.3 \\
-M8 & NGC 6523 & Lagoon Nebula & Nebula with cluster & 1.25 & Sagittarius & 6.0 \\
-M9 & NGC 6333 & Messier 9 & Cluster, globular & 7.91 & Ophiuchus & 8.4 \\
-M10 & NGC 6254 & Messier 10 & Cluster, globular & 4.42 & Ophiuchus & 6.4 \\
-\enddata
-\tablecomments{This table ``hides'' the third column in the \latex\ when compiled.
-The Distance is also centered on the decimals.  Note that when using decimal
-alignment you need to include the {\tt\string\decimals} command before
-{\tt\string\startdata} and all of the values in that column have to have a
-space before the next ampersand.}
-\end{deluxetable*}
-
-\subsubsection{Splitting a table into multiple horizontal components}
-
-Since the AAS Journals are now all electronic with no print version there is
-no reason why tables can not be as wide as authors need them to be.
-However, there are some artificial limitations based on the width of a
-print page.  The old way around this limitation was to rotate into 
-landscape mode and use the smallest available table font
-sizes, e.g. {\tt\string\tablewidth}, to get the table to fit.
-Unfortunately, this was not alway enough but now along with the hide column
-option outlined in Section \ref{subsubsec:hide} there is a new way to break
-a table into two or three components so that it flows down a page by
-invoking a new table type, splittabular or splitdeluxetable. Within these
-tables a new ``B'' column separator is introduced.  Much like the vertical
-bar option, ``$\vert$'', that produces a vertical table lines, e.g. Table
-\ref{tab:table}, the new ``B'' separator indicates where to \underline{B}reak
-a table.  Up to two ``B''s may be included.
-
-Table 5 % \ref{tab:deluxesplit} this freaks it out when it is used!
-shows how to split a wide deluxetable into three parts with
-the {\tt\string\splitdeluxetable} command.  The {\tt\string\colnumbers}
-option is on to show how the automatic column numbering carries through the
-second table component, see Section \ref{subsubsec:autonumber}.
-
-The last example, Table \ref{tab:tablesplit}, shows how to split the same
-table but with a regular \latex\ tabular call and into two parts. Decimal
-alignment is included in the third column and the ``Component'' column is
-hidden to illustrate the new features working together.
-
-\begin{splitdeluxetable*}{lccccBcccccBcccc}
-\tabletypesize{\scriptsize}
-\tablewidth{0pt} 
-\tablenum{5}
-\tablecaption{Measurements of Emission Lines: two breaks \label{tab:deluxesplit}}
-\tablehead{
-\colhead{Model} & \colhead{Component}& \colhead{Shift} & \colhead{FWHM} &
-\multicolumn{10}{c}{Flux} \\
-\colhead{} & \colhead{} & \colhead{($\rm
-km~s^{-1}$)}& \colhead{($\rm km~s^{-1}$)} & \multicolumn{10}{c}{($\rm
-10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
-\cline{5-14}
-\colhead{} & \colhead{} &
-\colhead{} & \colhead{} & \colhead{Ly$\alpha$} & \colhead{N\,{\footnotesize
-V}} & \colhead{Si\,{\footnotesize IV}} & \colhead{C\,{\footnotesize IV}} &
-\colhead{Mg\,{\footnotesize II}} & \colhead{H$\gamma$} & \colhead{H$\beta$}
-& \colhead{H$\alpha$} & \colhead{He\,{\footnotesize I}} &
-\colhead{Pa$\gamma$}
-} 
-\colnumbers
-\startdata 
-{       }& BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\
-{Model 1}& IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
-{       }& NELs& \nodata &     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
-\hline
-{       }& BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
-{Model 2}& IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
-{       }& NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$&
-     147$\pm       22$\\
-\enddata
-\tablecomments{This is an example of how to split a deluxetable. You can
-split any table with this command into two or three parts.  The location of
-the split is given by the author based on the placement of the ``B''
-indicators in the column identifier preamble.  For more information please
-look at the new \aastex\ instructions.}
-\end{splitdeluxetable*}
-
-%\clearpage
-
-\setcounter{table}{5}
-\begin{table*}[h!]
-\renewcommand{\thetable}{\arabic{table}}
-\caption{Measurements of Emission Lines: one break\label{tab:tablesplit}}
-\begin{splittabular}{lhDccccBccccccc}
-%\multicolumn{5}{c}{Table 6} \\
-%\multicolumn{5}{c}{Measurements of Emission Lines} \\
-\hline 
-\hline 
-Model & Component & \multicolumn2c{Shift} & FWHM & 
-\multicolumn{10}{c}{Flux} \\
- & & \multicolumn2c{($\rm km~s^{-1}$)} & {($\rm km~s^{-1}$)} & 
-\multicolumn{10}{c}{($\rm 10^{-17}~erg~s^{-1}~cm^{-2}$)} \\
-\cline{5-15}
- & & & & & {Ly$\alpha$} & {N\,{\footnotesize V}} & 
-{Si\,{\footnotesize IV}} & {C\,{\footnotesize IV}} &
-{Mg\,{\footnotesize II}} & {H$\gamma$} & {H$\beta$}
-& {H$\alpha$} & {He\,{\footnotesize I}} & {Pa$\gamma$} \\
-%\hline
-\decimalcolnumbers
- & BELs& -97.13 &    9117$\pm      38$&    1033$\pm      33$&$< 35$&$<     166$&     637$\pm      31$&    1951$\pm      26$&     991$\pm 30$&    3502$\pm      42$&   20285$\pm      80$&    2025$\pm     116$& 1289$\pm     107$\\
-Model 1 & IELs& -4049.123 & 1974$\pm      22$&    2495$\pm      30$&$<     42$&$<     109$&     995$\pm 186$&      83$\pm      30$&      75$\pm      23$&     130$\pm      25$& 357$\pm      94$&     194$\pm      64$& 36$\pm      23$\\
- & NELs& .
-&     641$\pm       4$&     449$\pm 23$&$<      6$&$<       9$&       --            &     275$\pm      18$& 150$\pm      11$&     313$\pm      12$&     958$\pm      43$&     318$\pm 34$& 151$\pm       17$\\
-\hline
- & BELs& -85 &    8991$\pm      41$& 988$\pm      29$&$<     24$&$<     173$&     623$\pm      28$&    1945$\pm 29$&     989$\pm      27$&    3498$\pm      37$&   20288$\pm      73$& 2047$\pm     143$& 1376$\pm     167$\\
-Model 2 & IELs& -51000 &    2025$\pm      26$& 2494$\pm      32$&$<     37$&$<     124$&    1005$\pm     190$&      72$\pm 28$&      72$\pm      21$&     113$\pm      18$&     271$\pm      85$& 205$\pm      72$& 34$\pm      21$\\
- & NELs& 52 &     637$\pm      10$&     477$\pm 17$&$<      4$&$<       8$&       --            &     278$\pm      17$& 153$\pm      10$&     317$\pm      15$&     969$\pm      40$&     325$\pm 37$& 147$\pm       22$\\
-\hline
-\end{splittabular}
-\end{table*}
-
-\subsection{Figures\label{subsec:figures}}
-
-%% The "ht!" tells LaTeX to put the figure "here" first, at the "top" next
-%% and to override the normal way of calculating a float position
-
-Authors can include a wide number of different graphics with their articles
-in  encapsulated postscript (EPS) or portable document format (PDF).  These
-range from general figures all authors are familiar with to new enhanced
-graphics that can only be fully experienced in HTML.  The later include
-animations, figure sets and interactive figures.  This portion of the
-article provides examples for setting up all these graphics in with the
-latest version of \aastex.
-
-\subsection{General figures\label{subsec:general}}
-
-\aastex\ has a {\tt\string\plotone} command to display a figure
-consisting of one EPS/PDF file.  Figure \ref{fig:general} is an example
-which uses the data from Table \ref{tab:table}. For a general figure
-consisting of two EPS/PDF files the {\tt\string\plottwo} command can be
-used to position the two image files side by side.  Figure \ref{fig:f2}
-shows the Swift/XRT X-ray light curves of two recurrent novae.  The data
-from Figures \ref{fig:f2} through \ref{fig:fig4} are taken from Table 2 of
-\citet{2011ApJS..197...31S}.
-
-\begin{figure}
-
-\caption{Swift/XRT X-ray light curves of RS Oph and U Sco which represent
-the two canonical recurrent types, a long period system with a red giant
-secondary and a short period system with a dwarf/sub-dwarf secondary,
-respectively.\label{fig:f2}}
-\end{figure}
-
-Both {\tt\string\plotone} and {\tt\string\plottwo} take a
-{\tt\string\caption} and an optional {\tt\string\figurenum} command to
-specify the figure number\footnote{It is better to not use
-{\tt\string\figurenum} and let LaTeX auto-increment all the figures. If you
-do use this command you need to mark all of them accordingly.}.  Each is
-based on the {\tt\string graphicx} package command,
-{\tt\string\includegraphics}.  Authors are welcome to use
-{\tt\string\includegraphics} along with its optional arguments that control
-the height, width, scale, and position angle of a file within the figure.
-More information on the full usage of {\tt\string\includegraphics} can be
-found at \break
-\url{https://en.wikibooks.org/wiki/LaTeX/Importing\_Graphics\#Including\_graphics}.
-
-\subsection{Grid figures}
-
-Including more than two EPS/PDF files in a single figure call can be tricky
-easily format.  To make the process easier for authors \aastex\ v6 offers
-{\tt\string\gridline} which allows any number of individual EPS/PDF file
-calls within a single figure.  Each file cited in a {\tt\string\gridline}
-will be displayed in a row.  By adding more {\tt\string\gridline} calls an
-author can easily construct a matrix X by Y individual files as a
-single general figure.
-
-For each {\tt\string\gridline} command a EPS/PDF file is called by one of
-four different commands.  These are {\tt\string\fig},
-{\tt\string\rightfig}, {\tt\string\leftfig}, and {\tt\string\boxedfig}.
-The first file call specifies no image position justification while the
-next two will right and left justify the image, respectively.  The
-{\tt\string\boxedfig} is similar to {\tt\string\fig} except that a box is
-drawn around the figure file when displayed. Each of these commands takes
-three arguments.  The first is the file name.  The second is the width that
-file should be displayed at.  While any natural \latex\ unit is allowed, it
-is recommended that author use fractional units with the
-{\tt\string\textwidth}.  The last argument is text for a subcaption.
-
-Figure \ref{fig:pyramid} shows an inverted pyramid of individual
-figure constructed with six individual EPS files using the
-{\tt\string\gridline} option.
-
-\subsection{Figure sets}
-
-A large collection of similar style figures should be grouped together as a
-figure set.  The derived PDF article will only shows an example figure
-while the enhanced content is available in the figure set in the electronic
-edition.  The advantage of a figure set gives the reader the ability to
-easily sort through the figure collection to find individual component
-figures.  All of the figure set components, along with their html framework,
-are also available for download in a .tar.gz package.
-
-Special \latex\ mark up is required to create a figure set.  Prior to
-\aastex\ v6 the underlying mark up commands had to be inserted by hand
-but is now included.  Note that when an article with figure set is compiled
-in \latex\ none of the component figures are shown and a floating Figure
-Set caption will appear in the resulting PDF.
-
-\figsetstart
-\figsetnum{4}
-\figsettitle{Swift X-ray light curves}
-
-\figsetgrpstart
-\figsetgrpnum{1.1}
-\figsetgrptitle{KT Eri}
-\figsetplot{KT_Eri-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.2}
-\figsetgrptitle{RS Oph}
-\figsetplot{RS_Oph-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.3}
-\figsetgrptitle{U Sco}
-\figsetplot{U_Sco-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.4}
-\figsetgrptitle{V2491 Cyg}
-\figsetplot{V2491_Cyg-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.5}
-\figsetgrptitle{Nova LMC 2009}
-\figsetplot{LMC_2009-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.6}
-\figsetgrptitle{HV Cet}
-\figsetplot{CSS081007-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.7}
-\figsetgrptitle{V2672 Oph}
-\figsetplot{V2672_Oph-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetgrpstart
-\figsetgrpnum{1.8}
-\figsetgrptitle{V407 Cyg}
-\figsetplot{V407_Cyg-eps-converted-to.pdf}
-\figsetgrpnote{The Swift/XRT X-ray light curve for the first year after
-outburst.}
-\figsetgrpend
-
-\figsetend
-
-\begin{figure}
-\caption{The Swift/XRT X-ray light curve for the first year after
-outburst of the suspected recurrent nova KT Eri. At a maximum count rate of 
-328 ct/s, KT Eri was the brightest nova in X-rays observed to date. All 
-the component figures are available in the Figure Set. \label{fig:fig4}}
-\end{figure}
-
-Authors are encouraged to use an online tool at
-\url{http://authortools.aas.org/FIGSETS/make-figset.html} to generate their
-own specific figure set mark up to incorporate into their \latex\ articles.
-
-\subsection{Animations}
-
-Authors may include animations in their articles.  A single still frame from 
-the animation should be included as a regular figure to serve as an example.
-The associated figure caption should indicate to the reader exactly what the
-animation shows and that the animation is available online.
-
-\begin{figure}
-\caption{Example image from the animation which is available in the electronic
-edition.}
-\end{figure}
-
-\subsection{Interactive figures}
-
-Interactive figures give the reader the ability to manipulate the
-information contained in an image which can add clarity or help further the
-author's narrative.  These figures consist of two parts, the figure file in
-a specific format and a javascript and html frame work that provides the
-interactive control.  An example of an interactive figure is a 3D model.
-The underlying figure is a X3D file while x3dom.js is the javascript driver
-that displays it. An author created interface is added via a html wrapper.
-The first 3D model published by the AAS Journals using this technique was
-\citet{2014ApJ...793..127V}.  Authors should consult the online tutorials
-for more information on how to construct their own interactive figures.
-
-As with animations authors should include a non-interactive regular figure
-to use as an example.  The example figure should also indicate to the reader
-that the enhanced figure is interactive and can be accessed online.
 

### 2019-07-14 paper.tex
hypersurface abstract added

@@
 \section{Data Types} \label{sec:style}
-The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with varieties of gravitational physics problems.
+The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with variety of gravitational physics problems.
 The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen.
@@
 R_{\mu\nu} - \frac{1}{2}Rg_{\mu\nu} + \Lambda g_{\mu\nu} = \frac{8\pi G}{c^4}T_{\mu\nu}
-\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar $\Lambda$ is cosmological constant.
-All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation are terms involving $g_{\mu\nu}$ and on the right hand side are the matter field terms which only characterize the distribution of matter because of which the spacetime geometry is curved.\\
+\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar, $\Lambda$ is cosmological constant.
+All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation are terms involving $g_{\mu\nu}$ and on the right hand side are the matter field terms which only characterize the distribution of matter.\\
 EinsteinPy provides a core module: \texttt{metric} which has core data types of various metric tensors some which includes Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are exact solution of field equation for very specific matter distributions).
@@
 Following sections will give a breif overview of every core module and some of their important functionalities.
+\subsection{tensor}
 \subsection{metric}
@@
 \subsection{hypersurface}
+This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry.
+Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities.
+The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems.
+A small code snippet for plotting the hypersurface is as follows:
+\begin{minted}[linenos]{python}
+# importing the modules
+from einsteinpy.hypersurface import SchwarzschildEmbedding
+from astropy import units as u
+
+# Declaring embedding object with specified mass of the body 
+surface_obj = SchwarzschildEmbedding(5.927e23 * u.kg)
+surface_obj.plot_hypersurface(plot_type='surface')
+
+# plotting the embedding hypersurface for Schwarzschild spacetime
+surface_obj.show()
+\end{minted}
+\includegraphics[scale=0.5]{hypersurface_surface.png}
 

### 2019-07-19 paper.tex
introduction part edited
in the format of other papers of the journal(also grammatically checked by Grammarly)

@@
 
-This paper presents EinsteinPy (version 0.2), a community-developed Python
-package for gravitational and relativistic astrophysics.
-Python is a free, easy to use high level programming language which has seen a huge expansion in the number of its users and developers in recent years.
-Specifically, a lot of recent studies show that the use of Python in Astrophysics and in general physics has increased exponentially.
-Many great frameworks came as Python packages which provide a very high level of abstraction over the dirty nitty-gritty of complex algorithms and provide an easy to use interfaceand pleasing user experience.
-One such example is Keras - framework for deep learning which has made deep learning so easy that a person with zero programming knowledge can also train a neural network classifier.
+This paper presents the release of EinsteinPy version 0.2, a community-developed Python package which pertains to gravitational and relativistic astrophysics.
+Python, a free, easy to use high-level programming language has conquered today’s regime of programming and has seen a huge expansion in recent times thereby extending its applicability in the domains of Astrophysics and in general physics.
+Many great frameworks on Python have substantiated a very high level of abstraction over the intricacies of complex algorithms and thus provide an easy to use interface and pleasing user experience.
+One such example is Keras - a framework for deep learning which has made the complex area much easier that even a neo-programmer can  train a neural network classifier.
 This example really demonstrates the power of abstraction which is achievable in Python.
-The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with a little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.
-Currently EinsteinPy supports simulation of time-like and null geodesics and calculate trajectories in different background geometries some of which are Schwarzschild, Kerr and KerrNewmann along with coordinate inter-conversion pipeline.
+EinsteinPy brings forth its essence in a similar way and was developed keeping in mind the state of a theoretical gravitational physicist with a little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.EinsteinPy aims to foster the development and functionality to the astronomical community with currently facilitating the simulation of time-like and null geodesics and calculation of trajectories in different background geometries some of which are Schwarzschild, Kerr and KerrNewmann along with coordinate inter-conversion pipeline.
 It has a partially developed pipeline for plotting and visualization with dependencies on libraries like plotly, matplotlib etc.
-One of the unique feature of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilites which is a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky.
-Currently EinsteinPy also provide few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.
-The current version of the library is in a state that can be used by any serious student of general relativity trying to get essence of this beautiful subject but is somewhere lost in the heavy mathematical formalism of the subject.
-EinsteinPy provides such students to really see through the equations and visualize whats really happening.
+One of the unique features of EinsteinPy is sufficiently developed symbolic tensor manipulation utilites which can build a strong foundation by deploying as a tool for self-learning in the area of tensor algebra.
+Currently, EinsteinPy also renders few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.
+The current version of the library aids in the path of inherent challenges of substantial mathematical formalism faced by a novice in general relativity, thereby modifying and remoulding the equations into visualisations.
 

### 2019-08-24 paper.tex
intro part added

--- 2019-07-14 paper.tex
@@
 \section{Introduction} \label{sec:intro}
-It was the time of 1915 when Einstein published his paper on general theory of relativity which proposed a elegant and rigorous framework for a relativistic theory of gravity and was generalized version of gravity free theory - special relativity which he published earlier in 1905 and since then the whole physics community was against the bold ideas of the young genius and resisted in the beginning because all people were worried that if these hypothesis true would then completely change our notion of how we percieve space and time.
-But sooner they started to realize the true depth in the formalism of general relativity and its ability to explain the fundamental laws of nature.
-After so many years its well established now that general theory of relativity is the "theory of gravity" in classical regime and all the attempts to formulate quantum theory of gravity one way or the other borrow ideas from GR.
-The central problem then and now remains to be the solutions of the Einstein's field equation.
-Many times we can study the behaviour of solutions under high degree of symmetry considerations and could even solve analytically for highly unrealistic systems but solving it for problems relevant to astrophysical and gravitational physics research it still remains a big question on how to get around the problem of solving these field equations.
-This question is so profound that it has a separate research field which goes with the name of numerical relativity which attempts to use computer programmes to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics is happening (as we can not solve for a infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
-The interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining.
-After so many years the field of numerical relativity has grown up to be a mature research area with vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones).
-Currently there exist some very robust and involved frameworks that provide a complete programming ecosystem and have proved to an be essential tools for any numerical relativity researcher.
-Now on the other end of the research community are the theoretical physicists many of which have little or no programming experience and is really challenged by the fact that the usage of these frameworks demand heavy use of high level programming languages like C and C++.
-As described above Python provides a vast room for abstractions and no library existed at that time that do numerical relativity in Python and hence the team was hooked by this very fact of need for a python library on general relativity.
-Since then EinsteinPy has seen a lot of contributions from people all over the world and many "good to go" functionalities are already provided in this and previous versions.
-Like any other numerical relativity library EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to dive deep into the nitty gitties of the subject along with few very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity in general\footnote{More details on this are given in further coming sections}.
-In further coming section we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.
-Also we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
+
+The relativistic theory of gravity paved its way to the ground in 1915, when Einstein published his paper on the general theory of relativity.
+This elegant and rigorous framework  was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905 and since then the whole physics community was against the bold ideas of the young genius and resisted the same in the beginning, as all people were worried that if the hypothesis stood true, complete notion of how they perceived space and time would get altered.
+Sooner,  they started to realize and conceive the true depth in the formalism of general relativity and its ability to explain the fundamental laws of nature.
+It took a huge span of time for the acceptability of general theory of relativity as the "theory of gravity" in the classical regime.
+All the attempts to formulate a quantum theory of gravity in some way or the other borrow its ideas from General Relativity.
+Almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein equation remain extremely difficult to find beyond those which exhibit significant symmetries.
+The central problem then and now remains to be the solutions of Einstein's field equation.
+Many times we can study the behaviour of solutions under a high degree of symmetry considerations and could even solve analytically for highly unrealistic systems but solving it for problems relevant to astrophysical and gravitational physics research.
+It still remains a big daunting question on how to get around the problem of solving these field equations.
+This question is so profound that it has a separate profound field of research which goes with the name of numerical relativity which attempts to use computation science and programming to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics are happening (as we can not solve for an infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
+Numerical methods have been used to solve the Einstein equation for many decades, but the past decade has seen tremendous advances and adding to that, the interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining.
+The field of numerical relativity is growing rampantly with the vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones) with the development of robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.
+Reflecting the other end of the research community stands the major section of theoretical physicists which counts the majority as a novice in programming.
+The head challenge is the fact that the usage of these frameworks demands heavy use of high-level programming languages like C, C++, Python etc.
+Though Python provides a vast room for abstractions no library existed that focused towards numerical relativity, eventually, the need of python library dedicated to general relativity became the propellant for the team and thus they made dauntless efforts to cover the space for this Python library.
+Since then, EinsteinPy has seen a lot of contributions from people all over the world and many "good to go" functionalities are already provided in this and previous versions.
+Like any other numerical relativity library, EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to deal with intricacies of the subject along with few, very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity
+with every minute detail .in general\footnote{More details on this are given in further coming sections}.
+In further coming section, we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.
+Also, we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
+Software development and tools form a significant part of research in astronomy and moreover, the field itself has long supported the development of software tools for astronomical tasks..
+These packages therefore typically provide some level of documentation and user support or training.
+.
+The development of the EinsteinPy core package began as a community-driven effort to standardize core functionality for software in Python which renders a  user-friendly interface for supporting numerical relativity and relativistic astrophysics research.
+The library is as an attempt to provide programming and numerical environment for numerous numerical relativity problems like geodesics plotter, gravitational lensing and ray tracing, solving and simulating relativistic hydrodynamical equations, plotting of black hole event horizons, solving Einstein’s field equations and simulating various dynamical systems like binary merger etc.
+
+At the same time, the scientific community contributing to the package has grown tremendously and an ecosystem of packages supporting or affiliated with the EinsteinPycore has developed. 
+EinsteinPy provides an open-source and open-development core package and an ecosystem of affiliated 
+packages that support numeric relativity functionality in the Python programming language.
+"Open development" describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes or other code changes, governance, or any other aspect of the development process is discussed.
+EinsteinPy core package is now a feature-rich library of sufficiently general tools and classes that support the development of more specialized code
+
+In this paper, we describe the current status of the EinsteinPy core package and discuss goals for future development.
+We start by describing the way EinsteinPy functions followed by the main software efforts developed by the EinsteinPy itself with proper detailed documentation of the current version release.We end with a short vision for the future of EinsteinPy to its contribution in the field of computational methodology in gravitational and relativistic Astrophysics.
+
 \section{Units Handling}
-EinsteinPy has dependencies on Astropy for handling units and user have to use appropiate Astropy units\footnote{more on astropy units can be refered from their official website documentation} while declaring the input data to various methods which are further used in computation.
+EinsteinPy has dependencies on Astropy for handling units and user have to use appropriate Astropy units\footnote{more on astropy units can be referred from their official website documentation} while declaring the input data to various methods which are further used in the computation.
 \section{Data Types} \label{sec:style}
-The heart of abstraction that EinsteinPy aims to provide is achieved by some set of data structures that are specifically designed to ease with variety of gravitational physics problems.
+Since its inception,  EinsteinPy has aimed to provide is achieved by some set of data structures that are specifically designed to ease with a variety of gravitational physics problems.
 The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen.
-Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satifies the following Einstein's field equation
+Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satisfies the following Einstein's field equation
 \[
@@
 \]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar, $\Lambda$ is cosmological constant.
-All the above quantities are derivatives of metric tensor\footnote{more on this can be refered from any standard general relativity text} so in simple terms, on the left hand side of the equation are terms involving $g_{\mu\nu}$ and on the right hand side are the matter field terms which only characterize the distribution of matter.\\
-EinsteinPy provides a core module: \texttt{metric} which has core data types of various metric tensors some which includes Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are exact solution of field equation for very specific matter distributions).
-The immediate functionalities which comes along with this module is solution of geodesic equations.
+All the above quantities are derivatives of metric tensor\footnote{more on this can be referred from any standard general relativity text} so in simple terms, on the left-hand side of the equation are terms involving $g_{\mu\nu}$ and on the right-hand side are the matter field terms which only characterize the distribution of matter.\\
+EinsteinPy provides a core module: \texttt{metric} which has core data types of various metric tensors some which include Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are the exact solution of field equation for very specific matter distributions).
+The immediate functionalities which come along with this module are the solutions of geodesic equations.
 The module has coupled integration with \texttt{coordinates} module which deals with different coordinate system transformations\footnote{more on this in the 'coordinates' section}.
-Another core data types is in the \texttt{plotting} module which handles all the plotting, rendering, animation and simulation related methods and provides a user friendly interfacing of plots.
-One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremly important in the formalism of general relativity and one of the first challenges faced by many beginners in their journey of learning the subject.
-EinsteinPy provides an excellent way to learn the math behind tensor manipulation and index gymnastics with the help of symbolic module: \texttt{symbolic}, on which more will be dicussed in its section ahead.\\
+Another core data types are in the \texttt{plotting} module which handles all the plotting, rendering, animation and simulation related methods and provides user-friendly interfacing of plots.
+One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremely important in the formalism of general relativity and one of the first challenges faced by many beginners in their journey of learning the subject.
+EinsteinPy provides an excellent way to learn the math behind tensor manipulation and index gymnastics with the help of symbolic module: \texttt{symbolic}, on which more will be discussed in its section ahead.\\
+
+Features of EinsteinPy and section division.
+\textbf{Paper organisation}
+
+			Organisation and Infrastructure
+EinsteinPy equations and notations:
+The purpose of this subsection is to clearly state the equations of motion that we have implemented and our conventions for completeness
+
+Evolution Equation
+
+EinsteinPy core package version 0.2
+Integrators
+
+Metric
+
+Utils
+
+Plotting
+
+Constant
+
+Coordinates
+
+Geodesic
+
+Bodies
+
+Hypersurface
+
+symbolic
+Support of EinsteinPy
+The EinsteinPy Project, as of the version 0.2release, does not receive any direct financial support for the development of EinsteinPy.
+Development of the software, all supporting materials, and community support are provided by individuals who work on EinsteinPy in their own personal time, by individuals or groups contributing to EinsteinPy as part of a research project.
+( A list of organizations that have contributed to EinsteinPy in this manner can be found in the Acknowledgments)
+
+Release Cycle and Long-term Support
+The EinsteinPy package is updated with significant changes and bug fixes in every release.
+The major releases contain new features or any significant changes, whereas the bugfix releases only contain fixes to code or documentation but no new features.
+
 Following sections will give a breif overview of every core module and some of their important functionalities.

### 2019-11-29 paper.tex
Changed files - removed mint

@@
 %% manuscript itself with \begin{document}.
+%\usepackage{minted}
 \usepackage{listings}
-\usepackage{minted}
+
 \begin{document}
@@
 \subsection{coordinates}
-\begin{minted}[linenos]{python}
-# importing modules
+%\begin{minted}[linenos]{python}
+%# importing modules
 from astropy import units as u
@@
 
-# initializing parameters and coordinate system
-M = 1.989e30 * u.kg
-a = 0.3 * u.m
-BL_obj = BoyerLindquistDifferential(50e5 * u.km, np.pi / 2 * u.rad, np.pi * u.rad,
-                                    0 * u.km / u.s, 0 * u.rad / u.s, 0 * u.rad / u.s,
-                                    a)
-end_lambda = ((1 * u.year).to(u.s)).value / 930
+%# initializing parameters and coordinate system
+%M = 1.989e30 * u.kg
+%a = 0.3 * u.m
+%BL_obj = BoyerLindquistDifferential(50e5 * u.km, np.pi / 2 * u.rad, np.pi * u.rad,
+     %                               0 * u.km / u.s, 0 * u.rad / u.s, 0 * u.rad / u.s,
+          %                          a)
+%end_lambda = ((1 * u.year).to(u.s)).value / 930
 
-# Choosing stepsize for ODE solver to be 0.02 minutes
-stepsize = ((0.02 * u.min).to(u.s)).value
+%# Choosing stepsize for ODE solver to be 0.02 minutes
+%stepsize = ((0.02 * u.min).to(u.s)).value
 
-# defining Kerr spacetime metric object
-obj = Kerr.from_coords(BL_obj, M)
+%# defining Kerr spacetime metric object
+%obj = Kerr.from_coords(BL_obj, M)
 
-# calculates the trajectory
-ans = obj.calculate_trajectory(
-    end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
-)
-\end{minted}
+%# calculates the trajectory
+%ans = obj.calculate_trajectory(
+    %end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
+%)
+%\end{minted}
 \subsection{plotting}
@@
 A small code snippet for plotting the hypersurface is as follows:
-\begin{minted}[linenos]{python}
-# importing the modules
+%\begin{minted}[linenos]{python}
+%# importing the modules
 from einsteinpy.hypersurface import SchwarzschildEmbedding
@@
 
-# Declaring embedding object with specified mass of the body 
-surface_obj = SchwarzschildEmbedding(5.927e23 * u.kg)
-surface_obj.plot_hypersurface(plot_type='surface')
+%# Declaring embedding object with specified mass of the body 
+%surface_obj = SchwarzschildEmbedding(5.927e23 * u.kg)
+%surface_obj.plot_hypersurface(plot_type='surface')
 
-# plotting the embedding hypersurface for Schwarzschild spacetime
-surface_obj.show()
-\end{minted}
+%# plotting the embedding hypersurface for Schwarzschild spacetime
+%surface_obj.show()
+%\end{minted}
 \includegraphics[scale=0.5]{hypersurface_surface.png}

### 2020-01-02 paper.tex
symbolic edits

@@
 \subsection{symbolic}
+General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of a arbitrary space-time.
+We would describe the various quantities currently supported by this module while maintaining brevity.
 \subsection{hypersurface}

### 2020-01-04 paper.tex
edits take-II

@@
 We would describe the various quantities currently supported by this module while maintaining brevity.
+Each quantity has its own class, even scalars, which are treated as 0\textsuperscript{th} order tensors.
+
+\subsubsection{BaseRelativityTensor}
+This is a base class from which other tensors are derived.
+The user can use this class to create his/her own tensor while using the various in-built functions provided by this class.
+The class also maintains the indicial configuration of the tensor(contravariant and co-variant indices), calculates the free variables used in describing the tensor other than those which depicts the axis of space-time itself (e.g.
+t,x,y,z).
+The class has a function to convert the symbolic tensorial quantities into functions where actual numerical values can be substitued.
+
+This class along with its parent class contains the following functions/properties.
+\begin{itemize}
+\item \texttt{order} (Property) : Returns the order of the tensor. 
+\item \texttt{config} (Property) : Returns the arrangement of contravariant(upper)/covariant(lower) indices of the tensor. For example, 'ulll'.
+\item \texttt{parent\_metric} (Property) : Returns the metric tensor of the space-time associated with the tensor, if present. Else returns \texttt{None}.
+\item \texttt{tensor} (Function) : Returns the tensorial quantity contained within the class instance.
+\item \texttt{subs} (Function) : Returns a new tensor upon substitution of current variables with new variables/values.
+\item \texttt{simplify} (Function) : Returns a tensor contain simplified expressions from the current tensor.
+\item \texttt{symbols} (Function) : Returns the symbols denoting each axis of the space-time.
+\item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
+\end{itemize}
+
+\subsubsection{MetricTensor}
+Metric Tensor describes the differential length elements required to measure distance in a curved(also applies to flat) space-time.
+It is a second order tensor and is fundamental to describe any space-time geometry.
+The \texttt{MetricTensor} class, being inherited from \texttt{BaseRelativityTensor}, inherits all its functions and also have some functions and constraints of its own.
+For example, metric tensor is bound to be a second order tensor.
+
+The defined class functions are :
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\item \texttt{inv} : returns inverse of the metric
+\end{itemize}
+
+\subsubsection{ChristoffelSymbols}
+Although Christoffel Symbols are belong to class of pseudo-tensors, it is inherited from \texttt{BaseRelativityTensor} to maintain homogenity within the module.
+Bein inherited from \texttt{BaseRelativityTensor}, it already supports the functions of its parent class and imposes some restrictions of its own, such as order of the tensor should be 3.
+
+Instance of the class can be made by directly passing a 3\textsuperscript{rd} order tensor or can be obtained using the following classmethods
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates christoffel symbols from a given instance of \texttt{MetricTensor} class.
+\end{itemize}
+
+The defined class function(s) are : 
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\end{itemize}
+
+\subsubsection{RiemannCurvatureTensor}
+This quantity is the most extensive measure of curvature of a sapce-time. It is inherited from \texttt{BaseRelativityTensor} and supports all the functions of its parent class.
+
+Instance of the class can be made by directly passing a 4\textsuperscript{th} order tensor or can be obtained using the following classmethods
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates Riemann Tensor from a given instance of \texttt{MetricTensor} class.
+\item \texttt{from\_christoffels} : Calculates Riemann Tensor from a given instance of \texttt{ChristoffelSymbols} class.
+\end{itemize}
+
+The defined class function(s) are : 
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\end{itemize}
+
+\subsubsection{RicciTensor}
+This tensor is used in solving Eintein's  equation and basically contraction of Riemann Curvature Tensor.
+It is inherited from \texttt{BaseRelativityTensor} and supports all the functions of its parent class.
+
+Instance of the class can be made by directly passing a 2\textsuperscript{nd} order tensor or can be obtained using the following classmethods
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates Ricci Tensor from a given instance of \texttt{MetricTensor} class.
+\item \texttt{from\_christoffels} : Calculates Ricci Tensor from a given instance of \texttt{ChristoffelSymbols} class.
+\item \texttt{from\_riemann} : Calculates Ricci Tensor from a given instance of \texttt{RiemannCurvatureTensor} class.
+\end{itemize}
+
+The defined class function(s) are : 
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\end{itemize}
+
+\subsubsection{RicciScalar}
+It is a scalar quantity obtained by contracting a given Ricci Tensor.
+It is inherited from \texttt{BaseRelativityTensor} and supports all the functions of its parent class.
+Being a scalar quantity, it does not support \texttt{change\_config} unlike other tensors as discussed above.
+
+Instance of the class can be made by directly passing a symbolic expression or can be obtained using the following classmethods
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates Ricci Scalar from a given instance of \texttt{MetricTensor} class.
+\item \texttt{from\_christoffels} : Calculates Ricci Scalar from a given instance of \texttt{ChristoffelSymbols} class.
+\item \texttt{from\_riemann} : Calculates Ricci Scalar from a given instance of \texttt{RiemannCurvatureTensor} class.
+\item \texttt{from\_riccitensor} : Calculates Ricci Scalar from a given instance of \texttt{RicciTensor} class.
+\end{itemize}
+
+The defined class properties are : 
+\begin{itemize}
+\item \texttt{expr} : returns the scalar symbolic expression contained in the class. 
+\end{itemize}
+
+\subsubsection{Other Defined Quantities}
+As the library is in heavy development, new quantities are being added as and when required.
+Some other quantities currently supported are listed below.
+The quantities are all inherited from \texttt{BaseRelativityTensor}, and a similar API (same as that of discussed above) has been implemented to maintain compatiblity and homegenity.
+The class names denote usual quantities relevant to General Relativity.
+
+\begin{itemize}
+\item \texttt{EinsteinTensor}
+\item \texttt{StressEnergyMomentumTensor}
+\item \texttt{WeylTensor}
+\item \texttt{SchoutenTensor}
+\end{itemize}
+
+Further, various constants like $c$(speed of light), $G$(Gravitational constant) are defined in their symbolic forms, for use within the symbolic module.
+
 \subsection{hypersurface}

### 2020-01-18 authors.tex
Seaparate Authors.tx

--- 2019-11-29 paper.tex
@@
-%%
-%% Beginning of file 'paper.tex'
-%%
-%% Modified 2018 January
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.2 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
+\newcommand{\sceeiitmandi}{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
 
-%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
-%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
-%% All of these external packages should already be present in the modern TeX 
-%% distributions.  If not they can also be obtained at www.ctan.org.
+% \author[0000-0000-0000-0000]{The EinsteinPy Community}
+% \noaffiliation
 
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style  which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%%
-%% using aastex version 6.2
-\documentclass{aastex62}
-
-%% The default is a single spaced, 10 point font, single spaced article.
-%% There are 5 other style options available via an optional argument. They
-%% can be envoked like this:
-%%
-%% \documentclass[argument]{aastex62}
-%% 
-%% where the layout options are:
-%%
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.  
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%% 		  wider left and right margins. This uses the Daniel
-%% 		  Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Preferred style for Research Notes which are by design 
-%%                lacking an abstract and brief. DO NOT use \begin{abstract}
-%%                and \end{abstract} with this style.
-%%
-%% Note that you can submit to the AAS Journals in any of these 6 styles.
-%%
-%% There are other optional arguments one can envoke to allow other stylistic
-%% actions. The available options are:
-%%
-%%  astrosymb    : Loads Astrosymb font and define \astrocommands. 
-%%  tighten      : Makes baselineskip slightly smaller, only works with 
-%%                 the twocolumn substyle.
-%%  times        : uses times font instead of the default
-%%  linenumbers  : turn on lineno package.
-%%  trackchanges : required to see the revision mark up and print its output
-%%  longauthor   : Do not use the more compressed footnote style (default) for 
-%%                 the author/collaboration/affiliations. Instead print all
-%%                 affiliation information after each name. Creates a much
-%%                 long author list but may be desirable for short author papers
-%%
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
-%%
-%% AASTeX v6.* now includes \hyperref support. While we have built in specific
-%% defaults into the classfile you can manually override them with the
-%% \hypersetup command. For example,
-%%
-%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
-%%
-%% will change the color of the internal links to red, the links to the
-%% bibliography to green, the file links to cyan, and the external links to
-%% magenta. Additional information on \hyperref options can be found here:
-%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
-%%
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-
-%% Tells LaTeX to search for image files in the 
-%% current directory as well as in the figures/ folder.
-\graphicspath{{./}{figures/}}
-
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{January 1, 2018}
-\revised{January 7, 2018}
-\accepted{\today}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the arguement.
-\submitjournal{ApJ}
-
-%% Mark up commands to limit the number of authors on the front page.
-%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
-%% an author in this case.
-%
-%\AuthorCollaborationLimit=3
-%
-%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
-%% collaboration" on the front page of this example manuscript.
-%%
-%% Note that all of the author will be shown in the published article.
-%% This feature is meant to be used prior to acceptance to make the
-%% front end of a long author article more manageable. Please do not use
-%% this functionality for manuscripts with less than 20 authors. Conversely,
-%% please do use this when the number of authors exceeds 40.
-%%
-%% Use \allauthors at the manuscript end to show the full author list.
-%% This command should only be used with \AuthorCollaborationLimit is used.
-
-%% The following command can be used to set the latex table counters.  It
-%% is needed in this document because it uses a mix of latex tabular and
-%% AASTeX deluxetables.  In general it should not be needed.
-%\setcounter{table}{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% The following section outlines numerous optional output that
-%% can be displayed in the front matter or as running meta-data.
-%%
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-%%
-%% You can add a light gray and diagonal water-mark to the first page 
-%% with this command:
-% \watermark{text}
-%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
-%% long you can control the water-mark size with:
-%  \setwatermarkfontsize{dimension}
-%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% This is the end of the preamble.  Indicate the beginning of the
-%% manuscript itself with \begin{document}.
-%\usepackage{minted}
-\usepackage{listings}
-
-\begin{document}
-
-\title{EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.2 you can include a footnote in the title.
-
-%% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affilations. The change was necessary to implement 
-%% autoindexing of affilations which prior was a manual process that could 
-%% easily be tedious in large author manuscripts.
-%%
-%% The \author command is the same as before except it now takes an optional
-%% arguement which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid.
-%%
-%% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
-%% When a duplicate is found its index will be the same as its previous entry.
-%%
-%% Note that \altaffilmark and \altaffiltext have been removed and thus 
-%% can not be used to document secondary affiliations. If they are used latex
-%% will issue a specific error message and quit. Please use multiple 
-%% \affiliation calls for to document more than one affiliation.
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.2 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
+% \author[orcid-id]{name}
+% \affiliation{}
+% below add contributing authors (those folks that have actually worked writing the paper).
+% board members get some symbol next to their names.
 
 \author[0000-0002-0870-4665]{Shreyas Bapat}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\altaffiliation{EinsteinPy Lead Developer, EinsteinPy Board Member}
+\affiliation{\sceeiitmandi}
+
+\author[0000-0002-1900-3338]{Shilpi Jain}
+\altaffiliation{EinsteinPy Board Member}
+\affiliation{Department of Earth Sciences, Indian Institute of Technology Roorkee, India}
+
+\author{Ritwik Saha}
+\altaffiliation{EinsteinPy Lead Developer, EinsteinPy Board Member}
+\affiliation{\sceeiitmandi}
 
 \author{Bhavya Bhatt}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\altaffiliation{EinsteinPy Deputy Lead Developer}
+\affiliation{\sceeiitmandi}
 
-\author{Ritwik Saha}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\author[0000-0003-3354-1893]{Akshita Jain}
+\affiliation{\sceeiitmandi}
+
+\collaboration{1000}{(Primary Paper Contributors)}
+
+% Below add contributors to the EinsteinPy project
 
 \author[0000-0003-1021-3336]{Priyanshu Khandelwal}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-\collaboration{(EinsteinPy Core Development Committee)}
+\altaffiliation{EinsteinPy Board Member}
+\affiliation{\sceeiitmandi}
 
 \author[0000-0002-2268-9772]{Sofía Ortín Vela}
-\affil{Department of Theoretical Physics, University of Zaragoza, Spain}
+\affil{University of Zaragoza, Spain}
 
@@
 \author[0000-0001-7234-6148]{Varun Singh}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author[0000-0002-1900-3338]{Shilpi Jain}
-\affiliation{Department of Earth Sciences, Indian Institute of Technology Roorkee, India}
+\affiliation{\sceeiitmandi}
 
@@
 \author[0000-0002-5198-9010]{Manvi Gupta}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\affiliation{\sceeiitmandi}
 
 \author{Tushar Tyagi}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\affiliation{\sceeiitmandi}
 
 \author[0000-0003-1838-8368]{Tanmay Rustagi}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\affiliation{\sceeiitmandi}
 
 \author[0000-0002-0757-2883]{Abhijeet Manhas}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
+\affiliation{\sceeiitmandi}
 
@@
 \affiliation{Department of Information Technology, Indian Institute of Information Technology Allahabad}
-\collaboration{(EinsteinPy Package Contributors)}
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
 
-%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
+\collaboration{1000}{(EinsteinPy Contributors)}
 
-%% Mark off the abstract in the ``abstract'' environment. 
-\begin{abstract}
-
-This paper presents EinsteinPy (version 0.2), a community-developed Python
-package for gravitational and relativistic astrophysics.
-Python is a free, easy to use high level programming language which has seen a huge expansion in the number of its users and developers in recent years.
-Specifically, a lot of recent studies show that the use of Python in Astrophysics and in general physics has increased exponentially.
-Many great frameworks came as Python packages which provide a very high level of abstraction over the dirty nitty-gritty of complex algorithms and provide an easy to use interfaceand pleasing user experience.
-One such example is Keras - framework for deep learning which has made deep learning so easy that a person with zero programming knowledge can also train a neural network classifier.
-This example really demonstrates the power of abstraction which is achievable in Python.
-The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with a little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.
-Currently EinsteinPy supports simulation of time-like and null geodesics and calculate trajectories in different background geometries some of which are Schwarzschild, Kerr and KerrNewmann along with coordinate inter-conversion pipeline.
-It has a partially developed pipeline for plotting and visualization with dependencies on libraries like plotly, matplotlib etc.
-One of the unique feature of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilites which is a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky.
-Currently EinsteinPy also provide few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.
-The current version of the library is in a state that can be used by any serious student of general relativity trying to get essence of this beautiful subject but is somewhere lost in the heavy mathematical formalism of the subject.
-EinsteinPy provides such students to really see through the equations and visualize whats really happening.
-
-\end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. 
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{gravitational physics, astrophysics --- 
-simulations --- black holes --- gravitational waves}
-
-%% From the front matter, we move on to the body of the paper.
-%% Sections are demarcated by \section and \subsection, respectively.
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-%%
-%% We recommend that authors also use the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below.
-
-\section{Introduction} \label{sec:intro}
-
-The relativistic theory of gravity paved its way to the ground in 1915, when Einstein published his paper on the general theory of relativity.
-This elegant and rigorous framework  was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905 and since then the whole physics community was against the bold ideas of the young genius and resisted the same in the beginning, as all people were worried that if the hypothesis stood true, complete notion of how they perceived space and time would get altered.
-Sooner,  they started to realize and conceive the true depth in the formalism of general relativity and its ability to explain the fundamental laws of nature.
-It took a huge span of time for the acceptability of general theory of relativity as the "theory of gravity" in the classical regime.
-All the attempts to formulate a quantum theory of gravity in some way or the other borrow its ideas from General Relativity.
-Almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein equation remain extremely difficult to find beyond those which exhibit significant symmetries.
-The central problem then and now remains to be the solutions of Einstein's field equation.
-Many times we can study the behaviour of solutions under a high degree of symmetry considerations and could even solve analytically for highly unrealistic systems but solving it for problems relevant to astrophysical and gravitational physics research.
-It still remains a big daunting question on how to get around the problem of solving these field equations.
-This question is so profound that it has a separate profound field of research which goes with the name of numerical relativity which attempts to use computation science and programming to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics are happening (as we can not solve for an infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
-Numerical methods have been used to solve the Einstein equation for many decades, but the past decade has seen tremendous advances and adding to that, the interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining.
-The field of numerical relativity is growing rampantly with the vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones) with the development of robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.
-Reflecting the other end of the research community stands the major section of theoretical physicists which counts the majority as a novice in programming.
-The head challenge is the fact that the usage of these frameworks demands heavy use of high-level programming languages like C, C++, Python etc.
-Though Python provides a vast room for abstractions no library existed that focused towards numerical relativity, eventually, the need of python library dedicated to general relativity became the propellant for the team and thus they made dauntless efforts to cover the space for this Python library.
-Since then, EinsteinPy has seen a lot of contributions from people all over the world and many "good to go" functionalities are already provided in this and previous versions.
-Like any other numerical relativity library, EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to deal with intricacies of the subject along with few, very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity
-with every minute detail .in general\footnote{More details on this are given in further coming sections}.
-In further coming section, we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.
-Also, we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
-Software development and tools form a significant part of research in astronomy and moreover, the field itself has long supported the development of software tools for astronomical tasks..
-These packages therefore typically provide some level of documentation and user support or training.
-.
-The development of the EinsteinPy core package began as a community-driven effort to standardize core functionality for software in Python which renders a  user-friendly interface for supporting numerical relativity and relativistic astrophysics research.
-The library is as an attempt to provide programming and numerical environment for numerous numerical relativity problems like geodesics plotter, gravitational lensing and ray tracing, solving and simulating relativistic hydrodynamical equations, plotting of black hole event horizons, solving Einstein’s field equations and simulating various dynamical systems like binary merger etc.
-
-At the same time, the scientific community contributing to the package has grown tremendously and an ecosystem of packages supporting or affiliated with the EinsteinPycore has developed. 
-EinsteinPy provides an open-source and open-development core package and an ecosystem of affiliated 
-packages that support numeric relativity functionality in the Python programming language.
-"Open development" describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes or other code changes, governance, or any other aspect of the development process is discussed.
-EinsteinPy core package is now a feature-rich library of sufficiently general tools and classes that support the development of more specialized code
-
-In this paper, we describe the current status of the EinsteinPy core package and discuss goals for future development.
-We start by describing the way EinsteinPy functions followed by the main software efforts developed by the EinsteinPy itself with proper detailed documentation of the current version release.We end with a short vision for the future of EinsteinPy to its contribution in the field of computational methodology in gravitational and relativistic Astrophysics.
-
-\section{Units Handling}
-EinsteinPy has dependencies on Astropy for handling units and user have to use appropriate Astropy units\footnote{more on astropy units can be referred from their official website documentation} while declaring the input data to various methods which are further used in the computation.
-\section{Data Types} \label{sec:style}
-Since its inception,  EinsteinPy has aimed to provide is achieved by some set of data structures that are specifically designed to ease with a variety of gravitational physics problems.
-The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen.
-Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satisfies the following Einstein's field equation
-\[
-R_{\mu\nu} - \frac{1}{2}Rg_{\mu\nu} + \Lambda g_{\mu\nu} = \frac{8\pi G}{c^4}T_{\mu\nu}
-\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar, $\Lambda$ is cosmological constant.
-All the above quantities are derivatives of metric tensor\footnote{more on this can be referred from any standard general relativity text} so in simple terms, on the left-hand side of the equation are terms involving $g_{\mu\nu}$ and on the right-hand side are the matter field terms which only characterize the distribution of matter.\\
-EinsteinPy provides a core module: \texttt{metric} which has core data types of various metric tensors some which include Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are the exact solution of field equation for very specific matter distributions).
-The immediate functionalities which come along with this module are the solutions of geodesic equations.
-The module has coupled integration with \texttt{coordinates} module which deals with different coordinate system transformations\footnote{more on this in the 'coordinates' section}.
-Another core data types are in the \texttt{plotting} module which handles all the plotting, rendering, animation and simulation related methods and provides user-friendly interfacing of plots.
-One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremely important in the formalism of general relativity and one of the first challenges faced by many beginners in their journey of learning the subject.
-EinsteinPy provides an excellent way to learn the math behind tensor manipulation and index gymnastics with the help of symbolic module: \texttt{symbolic}, on which more will be discussed in its section ahead.\\
-
-Features of EinsteinPy and section division.
-\textbf{Paper organisation}
-
-			Organisation and Infrastructure
-EinsteinPy equations and notations:
-The purpose of this subsection is to clearly state the equations of motion that we have implemented and our conventions for completeness
-
-Evolution Equation
-
-EinsteinPy core package version 0.2
-Integrators
-
-Metric
-
-Utils
-
-Plotting
-
-Constant
-
-Coordinates
-
-Geodesic
-
-Bodies
-
-Hypersurface
-
-symbolic
-Support of EinsteinPy
-The EinsteinPy Project, as of the version 0.2release, does not receive any direct financial support for the development of EinsteinPy.
-Development of the software, all supporting materials, and community support are provided by individuals who work on EinsteinPy in their own personal time, by individuals or groups contributing to EinsteinPy as part of a research project.
-( A list of organizations that have contributed to EinsteinPy in this manner can be found in the Acknowledgments)
-
-Release Cycle and Long-term Support
-The EinsteinPy package is updated with significant changes and bug fixes in every release.
-The major releases contain new features or any significant changes, whereas the bugfix releases only contain fixes to code or documentation but no new features.
-
-Following sections will give a breif overview of every core module and some of their important functionalities.
-\subsection{tensor}
-\subsection{metric}
-\texttt{metric} module give users the freedom to define metric object which can be further used in the computations related to spacetime geometry.
-Let's see an small example of solving geodesic equation in Kerr spacetime and obtaining trajectories using EinsteinPy
-\subsection{coordinates}
-%\begin{minted}[linenos]{python}
-%# importing modules
-from astropy import units as u
-import numpy as np
-from einsteinpy.metric import Kerr
-from einsteinpy.coordinates import BoyerLindquistDifferential
-
-%# initializing parameters and coordinate system
-%M = 1.989e30 * u.kg
-%a = 0.3 * u.m
-%BL_obj = BoyerLindquistDifferential(50e5 * u.km, np.pi / 2 * u.rad, np.pi * u.rad,
-     %                               0 * u.km / u.s, 0 * u.rad / u.s, 0 * u.rad / u.s,
-          %                          a)
-%end_lambda = ((1 * u.year).to(u.s)).value / 930
-
-%# Choosing stepsize for ODE solver to be 0.02 minutes
-%stepsize = ((0.02 * u.min).to(u.s)).value
-
-%# defining Kerr spacetime metric object
-%obj = Kerr.from_coords(BL_obj, M)
-
-%# calculates the trajectory
-%ans = obj.calculate_trajectory(
-    %end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
-%)
-%\end{minted}
-\subsection{plotting}
-\subsection{symbolic}
-\subsection{hypersurface}
-This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry.
-Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities.
-The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems.
-A small code snippet for plotting the hypersurface is as follows:
-%\begin{minted}[linenos]{python}
-%# importing the modules
-from einsteinpy.hypersurface import SchwarzschildEmbedding
-from astropy import units as u
-
-%# Declaring embedding object with specified mass of the body 
-%surface_obj = SchwarzschildEmbedding(5.927e23 * u.kg)
-%surface_obj.plot_hypersurface(plot_type='surface')
-
-%# plotting the embedding hypersurface for Schwarzschild spacetime
-%surface_obj.show()
-%\end{minted}
-\includegraphics[scale=0.5]{hypersurface_surface.png}
-
-\section{Displaying mathematics} \label{sec:displaymath}
-
-The most common mathematical symbols and formulas are in the amsmath
-package.  \aastex\ requires this package so there is no need to
-specifically call for it in the document preamble.  Most modern \latex\
-distributions already contain this package.  If you do not have this
-package or the other required packages, revtex4-1, latexsym, graphicx,
-amssymb, longtable, and epsf, they can be obtained from 
-\url{http://www.ctan.org}
-
-Mathematics can be displayed either within the text, e.g. $E = mc^2$, or
-separate from in an equation.  In order to be properly rendered, all inline
-math text has to be declared by surrounding the math by dollar signs (\$).
-
-A complex equation example with inline math as part of the explanation
-follows.
-
-\begin{equation}
-\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
-\hat a_nu(p_1,\sigma_1) ,
-\end{equation}
-where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
-and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
-and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
-operator $(\tau = \pm1)$.  This produces a single line formula.  \latex\ will
-auto-number this and any subsequent equations.  If no number is desired then
-the {\tt\string equation} call should be replaced with {\tt\string displaymath}.
-
-\latex\ can also handle a a multi-line equation.  Use {\tt\string eqnarray}
-for more than one line and end each line with a
-\textbackslash\textbackslash.  Each line will be numbered unless the
-\textbackslash\textbackslash\ is preceded by a {\tt\string\nonumber}
-command.  Alignment points can be added with ampersands (\&).  There should be
-two ampersands per line. In the examples they are centered on the equal
-symbol.
-
-\begin{eqnarray}
-\gamma^\mu  & = &
- \left(
-\begin{array}{cc}
-0 & \sigma^\mu_+ \\
-\sigma^\mu_- & 0
-\end{array}     \right) ,
- \gamma^5= \left(
-\begin{array}{cc}
--1 &   0\\
-0 &   1
-\end{array}     \right)  , \\
-\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , 
-\end{eqnarray}
-
-\begin{eqnarray}
-\hat a & = & \left(
-\begin{array}{cc}
-0 & (\hat a)_+\\
-(\hat a)_- & 0
-\end{array}\right), \nonumber \\
-(\hat a)_\pm & = & a_\mu\sigma^\mu_\pm 
-\end{eqnarray}
-
-%% Putting eqnarrays or equations inside the mathletters environment groups
-%% the enclosed equations by letter. For instance, the eqnarray below, instead
-%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
-%% LaTeX the paper and look at the output to see the results.
-
-\section{Revision tracking and color highlighting} \label{sec:highlight}
-
-Authors sometimes use color to highlight changes to their manuscript in
-response to editor and referee comments.  In \aastex\ new commands
-have been introduced to make this easier and formalize the process.
-
-The first method is through a new set of editing mark up commands that
-specifically identify what has been changed.  These commands are
-{\tt\string\added\{<text>\}}, {\tt\string\deleted\{<text>\}}, and
-{\tt\string\replaced\{<old text>\}\{<replaced text>\}}. To activate these
-commands the {\tt\string trackchanges} option must be used in the
-{\tt\string\documentclass} call.  When compiled this will produce the
-marked text in red.  The {\tt\string\explain\{<text>\}} can be used to add
-text to provide information to the reader describing the change.  Its
-output is purple italic font. To see how {\tt\string\added\{<important
-added info>\}}, {\tt\string\deleted\{<this can be deleted text>\}},
-{\tt\string\replaced\{<old data>\}\{<replaced data>\}}, and \break
-{\tt\string\explain\{<text explaining the change>\}} commands will produce
-\added{important added information}\deleted{, deleted text, and }
-\replaced{old data}{and replaced data,} toggle between versions compiled with
-and without the {\tt\string trackchanges} option.\explain{text explaining
-the change}
-
-A summary list of all these tracking commands can be produced at the end of
-the article by adding the {\tt\string\listofchanges} just before the
-{\tt\string\end\{document\}} call.  The page number for each change will be
-provided. If the {\tt\string linenumbers} option is also included in the
-documentcall call then not only will all the lines in the article be
-numbered for handy reference but the summary list will also include the
-line number for each change.
-
-The second method does not have the ability to highlight the specific
-nature of the changes but does allow the author to document changes over
-multiple revisions.  The commands are {\tt\string\edit1\{<text>\}},
-{\tt\string\edit2\{<text>\}} and {\tt\string\edit3\{<text>\}} and they
-produce {\tt\string<text>} that is highlighted in bold red, italic blue and
-underlined purple, respectively.  Authors should use the first command to
-\edit1{indicated which text has been changed from the first revision.}  The
-second command is to highlight \edit2{new or modified text from a second
-revision}.  If a third revision is needed then the last command should be used 
-\edit3{to show this changed text}.  Since over 90\% of all manuscripts are
-accepted after the 3rd revision these commands make it easy to identify
-what text has been added and when.  Once the article is accepted all the
-highlight color can be turned off simply by adding the
-{\tt\string\turnoffediting} command in the preamble. Likewise, the new commands
-{\tt\string\turnoffeditone}, {\tt\string\turnoffedittwo}, and
-{\tt\string\turnoffeditthree} can be used to only turn off the 
-{\tt\string\edit1\{<text>\}}, {\tt\string\edit2\{<text>\}} and 
-{\tt\string\edit3\{<text>\}}, respectively.
-
-Similar to marking editing changes with the {\tt\string\edit} options there
-are also the {\tt\string\authorcomments1\{<text>\}}, 
-{\tt\string\authorcomments2\{<text>\}} and
-{\tt\string\authorcomments3\{<text>\}} commands.  These produce the same
-bold red, italic blue and underlined purple text but when the
-{\tt\string\turnoffediting} command is present the {\tt\string<text>}
-material does not appear in the manuscript.  Authors can use these commands
-to mark up text that they are not sure should appear in the final
-manuscript or as a way to communicate comments between co-authors when
-writing the article.
-
-\section{Software and third party data repository citations} \label{sec:cite}
-
-The AAS Journals would like to encourage authors to change software and
-third party data repository references from the current standard of a
-footnote to a first class citation in the bibliography.  As a bibliographic
-citation these important references will be more easily captured and credit
-will be given to the appropriate people.
-
-The first step to making this happen is to have the data or software in
-a long term repository that has made these items available via a persistent
-identifier like a Digital Object Identifier (DOI).  A list of repositories
-that satisfy this criteria plus each one's pros and cons are given at \break
-\url{https://github.com/AASJournals/Tutorials/tree/master/Repositories}.
-
-In the bibliography the format for data or code follows this format: \\
-
-\noindent author year, title, version, publisher, prefix:identifier\\
-
-\citet{2015ApJ...805...23C} provides a example of how the citation in the
-article references the external code at
-\doi{10.5281/zenodo.15991}.  Unfortunately, bibtex does
-not have specific bibtex entries for these types of references so the
-``@misc'' type should be used.  The Repository tutorial explains how to
-code the ``@misc'' type correctly.  The most recent aasjournal.bst file,
-available with \aastex\ v6, will output bibtex ``@misc'' type properly.
-
-%% If you wish to include an acknowledgments section in your paper,
-%% separate it off from the body of the text using the \acknowledgments
-%% command.
-\acknowledgments
-
-We thank all the people that have made this AASTeX what it is today.  This
-includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
-Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
-Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
-for the new "modern" style design. Considerable help was provided via bug
-reports and hacks from numerous people including Patricio Cubillos, Alex
-Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
-Gagne.
-
-%% To help institutions obtain information on the effectiveness of their 
-%% telescopes the AAS Journals has created a group of keywords for telescope 
-%% facilities.
-%
-%% Following the acknowledgments section, use the following syntax and the
-%% \facility{} or \facilities{} macros to list the keywords of facilities used 
-%% in the research for the paper.  Each keyword is check against the master 
-%% list during copy editing.  Individual instruments can be provided in 
-%% parentheses, after the keyword, but they are not verified.
-
-\vspace{5mm}
-\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
-CTIO:1.5m,CXO}
-
-%% Similar to \facility{}, there is the optional \software command to allow 
-%% authors a place to specify which programs were used during the creation of 
-%% the manusscript. Authors should list each code and include either a
-%% citation or url to the code inside ()s when available.
-
-\software{astropy \citep{2013A&A...558A..33A},  
-          Cloudy \citep{2013RMxAA..49..137F}, 
-          SExtractor \citep{1996A&AS..117..393B}
-          }
-
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc. The
-%% Figure and Table counter will not reset.
-
-\appendix
-
-\section{Appendix information}
-
-Appendices can be broken into separate sections just like in the main text.
-The only difference is that each appendix section is indexed by a letter
-(A, B, C, etc.) instead of a number.  Likewise numbered equations have
-the section letter appended.  Here is an equation as an example.
-
-\begin{equation}
-I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-\end{equation}
-
-Appendix tables and figures should not be numbered like equations. Instead
-they should continue the sequence from the main article body.
-
-\section{Author publication charges} \label{sec:pubcharge}
-
-Finally some information about the AAS Journal's publication charges.
-In April 2011 the traditional way of calculating author charges based on 
-the number of printed pages was changed.  The reason for the change
-was due to a recognition of the growing number of article items that could not 
-be represented in print. Now author charges are determined by a number of
-digital ``quanta''.  A single quantum is 350 words, one figure, one table,
-and one enhanced digital item.  For the latter this includes machine readable
-tables, figure sets, animations, and interactive figures.  The current cost
-is \$27 per word quantum and \$30 for all other quantum type.
-
-\section{Rotating tables} \label{sec:rotate}
-
-The process of rotating tables into landscape mode is slightly different in
-\aastex v6.2. Instead of the {\tt\string\rotate} command, a new environment
-has been created to handle this task. To place a single page table in a
-landscape mode start the table portion with
-{\tt\string\begin\{rotatetable\}} and end with
-{\tt\string\end\{rotatetable\}}.
-
-Tables that exceed a print page take a slightly different environment since
-both rotation and long table printing are required. In these cases start
-with {\tt\string\begin\{longrotatetable\}} and end with
-{\tt\string\end\{longrotatetable\}}. Table \ref{chartable} is an
-example of a multi-page, rotated table.
-
-\begin{longrotatetable}
-\begin{deluxetable*}{lllrrrrrrll}
-\tablecaption{Observable Characteristics of 
-Galactic/Magellanic Cloud novae with X-ray observations\label{chartable}}
-\tablewidth{700pt}
-\tabletypesize{\scriptsize}
-\tablehead{
-\colhead{Name} & \colhead{V$_{max}$} & 
-\colhead{Date} & \colhead{t$_2$} & 
-\colhead{FWHM} & \colhead{E(B-V)} & 
-\colhead{N$_H$} & \colhead{Period} & 
-\colhead{D} & \colhead{Dust?} & \colhead{RN?} \\ 
-\colhead{} & \colhead{(mag)} & \colhead{(JD)} & \colhead{(d)} & 
-\colhead{(km s$^{-1}$)} & \colhead{(mag)} & \colhead{(cm$^{-2}$)} &
-\colhead{(d)} & \colhead{(kpc)} & \colhead{} & \colhead{}
-} 
-\startdata
-CI Aql & 8.83 (1) & 2451665.5 (1) & 32 (2) & 2300 (3) & 0.8$\pm0.2$ (4) & 1.2e+22 & 0.62 (4) & 6.25$\pm5$ (4) & N & Y \\
-{\bf CSS081007} & \nodata & 2454596.5 & \nodata & \nodata & 0.146 & 1.1e+21 & 1.77 (5) & 4.45$\pm1.95$ (6) & \nodata & \nodata \\
-GQ Mus & 7.2 (7) & 2445352.5 (7) & 18 (7) & 1000 (8) & 0.45 (9) & 3.8e+21  & 0.059375 (10) & 4.8$\pm1$ (9) & N (7) & \nodata \\
-IM Nor & 7.84 (11) & 2452289 (2) & 50 (2) & 1150 (12) & 0.8$\pm0.2$ (4) & 8e+21 & 0.102 (13) & 4.25$\pm3.4$ (4) & N & Y \\
-{\bf KT Eri} & 5.42 (14) & 2455150.17 (14) & 6.6 (14) & 3000 (15) & 0.08 (15) & 5.5e+20 & \nodata & 6.5 (15) & N & M \\
-{\bf LMC 1995} & 10.7 (16) & 2449778.5 (16) & 15$\pm2$ (17) & \nodata & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
-LMC 2000 & 11.45 (18) & 2451737.5 (18) & 9$\pm2$ (19) & 1700 (20) & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
-{\bf LMC 2005} & 11.5 (21) & 2453700.5 (21) & 63 (22) & 900 (23) & 0.15 (203) & 1e+21 & \nodata & 50  & M (24) & \nodata \\
-{\bf LMC 2009a} & 10.6 (25) & 2454867.5 (25) & 4$\pm1$  & 3900 (25) & 0.15 (203)  & 5.7e+20 & 1.19 (26) & 50 & N & Y \\
-{\bf SMC 2005} & 10.4 (27) & 2453588.5 (27) & \nodata & 3200 (28) & \nodata & 5e+20  & \nodata & 61 & \nodata & \nodata \\
-{\bf QY Mus} & 8.1 (29) & 2454739.90 (29) & 60:  & \nodata & 0.71 (30) & 4.2e+21  & \nodata & \nodata & M & \nodata \\
-{\bf RS Oph} & 4.5 (31) & 2453779.44 (14) & 7.9 (14) & 3930 (31) & 0.73 (32) & 2.25e+21 & 456 (33) & 1.6$\pm0.3$ (33) & N (34) & Y \\
-{\bf U Sco} & 8.05 (35) & 2455224.94 (35) & 1.2 (36) & 7600 (37) & 0.2$\pm0.1$ (4) & 1.2e+21 & 1.23056 (36) & 12$\pm2$ (4) & N & Y \\
-{\bf V1047 Cen} & 8.5 (38) & 2453614.5 (39) & 6 (40) & 840 (38) & \nodata & 1.4e+22  & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1065 Cen} & 8.2 (41) & 2454123.5 (41) & 11 (42) & 2700 (43) & 0.5$\pm0.1$ (42) & 3.75e+21 & \nodata & 9.05$\pm2.8$ (42) & Y (42) & \nodata \\
-V1187 Sco & 7.4 (44) & 2453220.5 (44) & 7: (45) & 3000 (44) & 1.56 (44) & 8.0e+21 & \nodata & 4.9$\pm0.5$ (44) & N & \nodata \\
-{\bf V1188 Sco} & 8.7 (46) & 2453577.5 (46) & 7 (40) & 1730 (47) & \nodata & 5.0e+21  & \nodata & 7.5 (39) & \nodata & \nodata \\
-{\bf V1213 Cen} & 8.53 (48) & 2454959.5 (48) & 11$\pm2$ (49) & 2300 (50) & 2.07 (30) & 1.0e+22 & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1280 Sco} & 3.79 (51) & 2454147.65 (14) & 21 (52) & 640 (53) & 0.36 (54) & 1.6e+21  & \nodata & 1.6$\pm0.4$ (54) & Y (54) & \nodata \\
-{\bf V1281 Sco} & 8.8 (55) & 2454152.21 (55) & 15:& 1800 (56) & 0.7 (57) & 3.2e+21 & \nodata & \nodata & N & \nodata \\
-{\bf V1309 Sco} & 7.1 (58) & 2454714.5 (58) & 23$\pm2$ (59) & 670 (60) & 1.2 (30) & 4.0e+21 & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1494 Aql} & 3.8 (61) & 2451515.5 (61) & 6.6$\pm0.5$ (61) & 1200 (62) & 0.6 (63) & 3.6e+21  & 0.13467 (64) & 1.6$\pm0.1$ (63) & N & \nodata \\
-{\bf V1663 Aql} & 10.5 (65) & 2453531.5 (65) & 17 (66) & 1900 (67) & 2: (68) & 1.6e+22  & \nodata & 8.9$\pm3.6$ (69) & N & \nodata \\
-V1974 Cyg & 4.3 (70) & 2448654.5 (70) & 17 (71) & 2000 (19) & 0.36$\pm0.04$ (71) & 2.7e+21  & 0.081263 (70) & 1.8$\pm0.1$ (72) & N & \nodata \\
-{\bf V2361 Cyg} & 9.3 (73) & 2453412.5 (73) & 6 (40) & 3200 (74) & 1.2: (75) & 7.0e+21 & \nodata & \nodata & Y (40) & \nodata \\
-{\bf V2362 Cyg} & 7.8 (76) & 2453831.5 (76) & 9 (77) & 1850 (78) & 0.575$\pm0.015$ (79) & 4.4e+21  & 0.06577 (80) & 7.75$\pm3$ (77) & Y (81) & \nodata \\
-{\bf V2467 Cyg} & 6.7 (82) & 2454176.27 (82) & 7 (83) & 950 (82) & 1.5 (84) & 1.4e+22  & 0.159 (85) & 3.1$\pm0.5$ (86) & M (87) & \nodata \\
-{\bf V2468 Cyg} & 7.4 (88) & 2454534.2 (88) & 10: & 1000 (88) & 0.77 (89) & 1.0e+22  & 0.242 (90) & \nodata & N & \nodata \\
-{\bf V2491 Cyg} & 7.54 (91) & 2454567.86 (91) & 4.6 (92) & 4860 (93) & 0.43 (94) & 4.7e+21  & 0.09580: (95) & 10.5 (96) & N & M \\
-V2487 Oph & 9.5 (97) & 2450979.5 (97) & 6.3 (98) & 10000 (98) & 0.38$\pm0.08$ (98) & 2.0e+21 & \nodata & 27.5$\pm3$ (99) & N (100) & Y (101) \\
-{\bf V2540 Oph} & 8.5 (102) & 2452295.5 (102) & \nodata & \nodata & \nodata & 2.3e+21 & 0.284781 (103) & 5.2$\pm0.8$ (103) & N & \nodata \\
-V2575 Oph & 11.1 (104) & 2453778.8 (104) & 20: & 560 (104) & 1.4 (105) & 3.3e+21 & \nodata & \nodata & N (105) & \nodata \\
-{\bf V2576 Oph} & 9.2 (106) & 2453832.5 (106) & 8: & 1470 (106) & 0.25 (107) & 2.6e+21  & \nodata & \nodata & N & \nodata \\
-{\bf V2615 Oph} & 8.52 (108) & 2454187.5 (108) & 26.5 (108) & 800 (109) & 0.9 (108) & 3.1e+21  & \nodata & 3.7$\pm0.2$ (108) & Y (110) & \nodata \\
-{\bf V2670 Oph} & 9.9 (111) & 2454613.11 (111) & 15: & 600 (112) & 1.3: (113) & 2.9e+21  & \nodata & \nodata & N (114) & \nodata \\
-{\bf V2671 Oph} & 11.1 (115) & 2454617.5 (115) & 8: & 1210 (116) & 2.0 (117) & 3.3e+21  & \nodata & \nodata & M (117) & \nodata \\
-{\bf V2672 Oph} & 10.0 (118) & 2455060.02 (118) & 2.3 (119) & 8000 (118) & 1.6$\pm0.1$ (119) & 4.0e+21  & \nodata & 19$\pm2$ (119) & \nodata & M \\
-V351 Pup & 6.5 (120) & 2448617.5 (120) & 16 (121) & \nodata & 0.72$\pm0.1$ (122) & 6.2e+21 & 0.1182 (123) & 2.7$\pm0.7$ (122) & N & \nodata \\
-{\bf V382 Nor} & 8.9 (124) & 2453447.5 (124) & 12 (40) & 1850 (23) & \nodata & 1.7e+22 & \nodata & \nodata & \nodata & \nodata \\
-V382 Vel & 2.85 (125) & 2451320.5 (125) & 4.5 (126) & 2400 (126) & 0.05: (126) & 3.4e+21  & 0.146126 (127) & 1.68$\pm0.3$ (126) & N & \nodata \\
-{\bf V407 Cyg} & 6.8 (128) & 2455266.314 (128) & 5.9 (129) & 2760 (129) & 0.5$\pm0.05$ (130) & 8.8e+21 & 15595 (131) & 2.7 (131) & \nodata & Y \\
-{\bf V458 Vul} & 8.24 (132) & 2454322.39 (132) & 7 (133) & 1750 (134) & 0.6 (135) & 3.6e+21 & 0.06812255 (136) & 8.5$\pm1.8$ (133) & N (135) & \nodata \\
-{\bf V459 Vul} & 7.57 (137) & 2454461.5 (137) & 18 (138) & 910 (139) & 1.0 (140) & 5.5e+21  & \nodata & 3.65$\pm1.35$ (138) & Y (140) & \nodata \\
-V4633 Sgr & 7.8 (141) & 2450895.5 (141) & 19$\pm3$ (142) & 1700 (143) & 0.21 (142) & 1.4e+21  & 0.125576 (144) & 8.9$\pm2.5$ (142) & N & \nodata \\
-{\bf V4643 Sgr} & 8.07 (145) & 2451965.867 (145) & 4.8 (146) & 4700 (147) & 1.67 (148) & 1.4e+22 & \nodata & 3 (148) & N & \nodata \\
-{\bf V4743 Sgr} & 5.0 (149) & 2452537.5 (149) & 9 (150) & 2400 (149) & 0.25 (151) & 1.2e+21 & 0.281 (152) & 3.9$\pm0.3$ (151) & N & \nodata \\
-{\bf V4745 Sgr} & 7.41 (153) & 2452747.5 (153) & 8.6 (154) & 1600 (155) & 0.1 (154) & 9.0e+20  & 0.20782 (156) & 14$\pm5$ (154) & \nodata & \nodata \\
-{\bf V476 Sct} & 10.3 (157) & 2453643.5 (157) & 15 (158) & \nodata & 1.9 (158) & 1.2e+22  & \nodata & 4$\pm1$ (158) & M (159) & \nodata \\
-{\bf V477 Sct} & 9.8 (160) & 2453655.5 (160) & 3 (160) & 2900 (161) & 1.2: (162) & 4e+21  & \nodata & \nodata & M (163) & \nodata \\
-{\bf V5114 Sgr} & 8.38 (164) & 2453081.5 (164) & 11 (165) & 2000 (23) & \nodata & 1.5e+21  & \nodata & 7.7$\pm0.7$ (165) & N (166) & \nodata \\
-{\bf V5115 Sgr} & 7.7 (167) & 2453459.5 (167) & 7 (40) & 1300 (168) & 0.53 (169) & 2.3e+21  & \nodata & \nodata & N (169) & \nodata \\
-{\bf V5116 Sgr} & 8.15 (170) & 2453556.91 (170) & 6.5 (171) & 970 (172) & 0.25 (173) & 1.5e+21 & 0.1238 (171) & 11$\pm3$ (173) & N (174) & \nodata \\
-{\bf V5558 Sgr} & 6.53 (175) & 2454291.5 (175) & 125 (176) & 1000 (177) & 0.80 (178) & 1.6e+22  & \nodata & 1.3$\pm0.3$ (176) & N (179) & \nodata \\
-{\bf V5579 Sgr} & 5.56 (180) & 2454579.62 (180) & 7: & 1500 (23) & 1.2 (181) & 3.3e+21 & \nodata & \nodata & Y (181) & \nodata \\
-{\bf V5583 Sgr} & 7.43 (182) & 2455051.07 (182) & 5: & 2300 (182) & 0.39 (30) & 2.0e+21 & \nodata & 10.5 & \nodata & \nodata \\
-{\bf V574 Pup} & 6.93 (183) & 2453332.22 (183) & 13 (184) & 2800 (184) & 0.5$\pm0.1$  & 6.2e+21 & \nodata & 6.5$\pm1$  & M (185) & \nodata \\
-{\bf V597 Pup} & 7.0 (186) & 2454418.75 (186) & 3: & 1800 (187) & 0.3 (188) & 5.0e+21  & 0.11119 (189) & \nodata & N (188) & \nodata \\
-{\bf V598 Pup} & 3.46 (14) & 2454257.79 (14) & 9$\pm1$ (190) & \nodata & 0.16 (190) & 1.4e+21 & \nodata & 2.95$\pm0.8$ (190) & \nodata & \nodata \\
-{\bf V679 Car} & 7.55 (191) & 2454797.77 (191) & 20: & \nodata & \nodata & 1.3e+22  & \nodata & \nodata & \nodata & \nodata \\
-{\bf V723 Cas} & 7.1 (192) & 2450069.0 (192) & 263 (2) & 600 (193) & 0.5 (194) & 2.35e+21  & 0.69 (195) & 3.86$\pm0.23$ (196) & N & \nodata \\
-V838 Her & 5 (197) & 2448340.5 (197) & 2 (198) & \nodata & 0.5$\pm0.1$ (198) & 2.6e+21  & 0.2975 (199) & 3$\pm1$ (198) & Y (200) & \nodata \\
-{\bf XMMSL1 J06} & 12 (201) & 2453643.5 (202) & 8$\pm2$ (202) & \nodata & 0.15 (203) & 8.7e+20 & \nodata & 50 & \nodata & \nodata \\
-\enddata
-\end{deluxetable*}
-\end{longrotatetable}
-
-A handy "cheat sheat" that provides the necessary LaTeX to produce 17 
-different types of tables is available at \url{http://journals.aas.org/authors/aastex/aasguide.html#table_cheat_sheet}.
-
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
-
-%% We have used macros to produce journal name abbreviations.
-%% \aastex provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
-\begin{thebibliography}{}
-
-\bibitem[Astropy Collaboration et al.(2013)]{2013A&A...558A..33A} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33 
-\bibitem[Bertin \& Arnouts(1996)]{1996A&AS..117..393B} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
-\bibitem[Corrales(2015)]{2015ApJ...805...23C} Corrales, L.\ 2015, \apj, 805, 23
-\bibitem[Ferland et al.(2013)]{2013RMxAA..49..137F} Ferland, G.~J., Porter, R.~L., van Hoof, P.~A.~M., et al.\ 2013, \rmxaa, 49, 137
-\bibitem[Hanisch \& Biemesderfer(1989)]{1989BAAS...21..780H} Hanisch, R.~J., \& Biemesderfer, C.~D.\ 1989, \baas, 21, 780 
-\bibitem[Lamport(1994)]{lamport94} Lamport, L. 1994, LaTeX: A Document Preparation System, 2nd Edition (Boston, Addison-Wesley Professional)
-\bibitem[Schwarz et al.(2011)]{2011ApJS..197...31S} Schwarz, G.~J., Ness, J.-U., Osborne, J.~P., et al.\ 2011, \apjs, 197, 31  
-\bibitem[Vogt et al.(2014)]{2014ApJ...793..127V} Vogt, F.~P.~A., Dopita, M.~A., Kewley, L.~J., et al.\ 2014, \apj, 793, 127
-
-\end{thebibliography}
-
-%% This command is needed to show the entire author+affilation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-
-\end{document}
-
-% End of file `sample62.tex'.
+\correspondingauthor{Shreyas Bapat}
+\email{shreyas@einsteinpy.org, bapat.shreyas@gmail.com}

### 2020-01-18 paper.tex
Seaparate Authors.tx

--- 2019-11-29 paper.tex
@@
+%% Beginning of file 'sample63.tex'
 %%
-%% Beginning of file 'paper.tex'
-%%
-%% Modified 2018 January
+%% Modified 2019 June
 %%
 %% This is a sample manuscript marked up using the
-%% AASTeX v6.2 LaTeX 2e macros.
+%% AASTeX v6.3 LaTeX 2e macros.
 %%
@@
 %%
-%% using aastex version 6.2
-\documentclass{aastex62}
+%% using aastex version 6.3
+\documentclass{aastex63}
 
@@
 %% There are 5 other style options available via an optional argument. They
-%% can be envoked like this:
+%% can be invoked like this:
 %%
-%% \documentclass[argument]{aastex62}
+%% \documentclass[arguments]{aastex63}
 %% 
@@
 %%
-%% There are other optional arguments one can envoke to allow other stylistic
+%% There are other optional arguments one can invoke to allow other stylistic
 %% actions. The available options are:
@@
 %%                  affiliation information after each name. Creates a much 
-%%                 long author list but may be desirable for short author papers
+%%                  longer author list but may be desirable for short 
+%%                  author papers.
+%% twocolappendix : make 2 column appendix.
+%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
+%%                  for dual anonymous review.
 %%
@@
 %%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex62}
+%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex63}
 %%
@@
 %%
-%%\hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
+%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
 %%
@@
 %% https://www.tug.org/applications/hyperref/manual.html#x1-40003
+%%
+%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
+%% to improve the accessibility of the compiled pdf file.
 %%
@@
 
-%% Tells LaTeX to search for image files in the 
-%% current directory as well as in the figures/ folder.
-\graphicspath{{./}{figures/}}
-
 %% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{January 1, 2018}
-\revised{January 7, 2018}
+\received{June 1, 2019}
+\revised{January 10, 2019}
 \accepted{\today}
 %% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the arguement.
+%% Adds "Submitted to " the argument.
 \submitjournal{ApJ}
 
-%% Mark up commands to limit the number of authors on the front page.
-%% Note that in AASTeX v6.2 a \collaboration call (see below) counts as
-%% an author in this case.
+%% For manuscript that include authors in collaborations, AASTeX v6.3
+%% builds on the \collaboration command to allow greater freedom to 
+%% keep the traditional author+affiliation information but only show
+%% subsets. The \collaboration command now must appear AFTER the group
+%% of authors in the collaboration and it takes TWO arguments. The last
+%% is still the collaboration identifier. The text given in this
+%% argument is what will be shown in the manuscript. The first argument
+%% is the number of author above the \collaboration command to show with
+%% the collaboration text. If there are authors that are not part of any
+%% collaboration the \nocollaboration command is used. This command takes
+%% one argument which is also the number of authors above to show. A
+%% dashed line is shown to indicate no collaboration. This example manuscript
+%% shows how these commands work to display specific set of authors 
+%% on the front page.
+%%
+%% For manuscript without any need to use \collaboration the 
+%% \AuthorCollaborationLimit command from v6.2 can still be used to 
+%% show a subset of authors.
 %
-%\AuthorCollaborationLimit=3
+%\AuthorCollaborationLimit=2
 %
-%% Will only show Schwarz, Muench and "the AAS Journals Data Scientist 
-%% collaboration" on the front page of this example manuscript.
+%% will only show Schwarz & Muench on the front page of the manuscript
+%% (assuming the \collaboration and \nocollaboration commands are
+%% commented out).
 %%
@@
 %% this information may be modified by the editorial offices.
+\shorttitle{EinsteinPy: Python for General Relativity}
+\shortauthors{The EinsteinPy Community}
 %%
@@
 %% with this command:
-% \watermark{text}
+%% \watermark{text}
 %% where "text", e.g. DRAFT, is the text to appear.  If the text is 
 %% long you can control the water-mark size with:
-%  \setwatermarkfontsize{dimension}
+%% \setwatermarkfontsize{dimension}
 %% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
+\graphicspath{{./}{figures/}}
 %% This is the end of the preamble.  Indicate the beginning of the
 %% manuscript itself with \begin{document}.
-%\usepackage{minted}
-\usepackage{listings}
 
@@
 %% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.2 you can include a footnote in the title.
+%% you desire. In v6.3 you can include a footnote in the title.
 
 %% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affilations. The change was necessary to implement 
-%% autoindexing of affilations which prior was a manual process that could 
+%% calling author and affiliations. The change was necessary to implement 
+%% auto-indexing of affiliations which prior was a manual process that could 
 %% easily be tedious in large author manuscripts.
@@
 %% The \author command is the same as before except it now takes an optional
-%% arguement which is the 16 digit ORCID. The syntax is:
+%% argument which is the 16 digit ORCID. The syntax is:
 %% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
@@
 %% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid.
+%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
+%% present or in the LaTeX pathway, the OrcID icon will appear next to
+%% the authors name.
 %%
 %% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.2 will automatically index these in the header.
+%% to \affiliation. AASTeX v6.3 will automatically index these in the header.
 %% When a duplicate is found its index will be the same as its previous entry.
@@
 %% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.2 to identify the
+%% \correspondingauthor command is available in V6.3 to identify the
 %% corresponding author of the manuscript. It is the author's responsibility
@@
 %% and save the corresponding author the trouble of entering it by hand.
+\input{authors.tex}
 
-\author[0000-0002-0870-4665]{Shreyas Bapat}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author{Bhavya Bhatt}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author{Ritwik Saha}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author[0000-0003-1021-3336]{Priyanshu Khandelwal}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-\collaboration{(EinsteinPy Core Development Committee)}
-
-\author[0000-0002-2268-9772]{Sofía Ortín Vela}
-\affil{Department of Theoretical Physics, University of Zaragoza, Spain}
-
-\author[0000-0001-8530-7252]{Jialin Ma}
-\affil{Georgia Institute of Technology, USA}
-
-\author[0000-0001-7234-6148]{Varun Singh}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author[0000-0002-1900-3338]{Shilpi Jain}
-\affiliation{Department of Earth Sciences, Indian Institute of Technology Roorkee, India}
-
-\author[0000-0002-7179-3795]{Alpesh Jamgade}
-\affiliation{Department of Mathematics, Bharath Institute of Higher Education and Research, Chennai, India}
-
-\author[0000-0002-5198-9010]{Manvi Gupta}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author{Tushar Tyagi}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author[0000-0003-1838-8368]{Tanmay Rustagi}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author[0000-0002-0757-2883]{Abhijeet Manhas}
-\affiliation{School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, India}
-
-\author[0000-0001-5558-9447]{Raphael Reyna}
-\affiliation{California State Polytechnic University, Pomona}
-
-\author[0000-0001-8302-1584]{Sashank Mishra}
-\affiliation{Department of Information Technology, Indian Institute of Information Technology Allahabad}
-\collaboration{(EinsteinPy Package Contributors)}
 %% Note that the \and command from previous versions of AASTeX is now
@@
 
-%% AASTeX 6.2 has the new \collaboration and \nocollaboration commands to
+%% AASTeX 6.3 has the new \collaboration and \nocollaboration commands to
 %% provide the collaboration status of a group of authors. These commands 
@@
 
-This paper presents EinsteinPy (version 0.2), a community-developed Python
+This paper presents EinsteinPy (version 0.3), a community-developed Python
 package for gravitational and relativistic astrophysics.
@@
 \section{Introduction} \label{sec:intro}
-
-The relativistic theory of gravity paved its way to the ground in 1915, when Einstein published his paper on the general theory of relativity.
-This elegant and rigorous framework  was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905 and since then the whole physics community was against the bold ideas of the young genius and resisted the same in the beginning, as all people were worried that if the hypothesis stood true, complete notion of how they perceived space and time would get altered.
-Sooner,  they started to realize and conceive the true depth in the formalism of general relativity and its ability to explain the fundamental laws of nature.
-It took a huge span of time for the acceptability of general theory of relativity as the "theory of gravity" in the classical regime.
-All the attempts to formulate a quantum theory of gravity in some way or the other borrow its ideas from General Relativity.
-Almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein equation remain extremely difficult to find beyond those which exhibit significant symmetries.
-The central problem then and now remains to be the solutions of Einstein's field equation.
-Many times we can study the behaviour of solutions under a high degree of symmetry considerations and could even solve analytically for highly unrealistic systems but solving it for problems relevant to astrophysical and gravitational physics research.
-It still remains a big daunting question on how to get around the problem of solving these field equations.
+The relativistic theory of gravity paved its way to the ground in 1915?, when Prof.
+Albert Einstein published his paper on the general theory of relativity.
+This elegant and rigorous framework was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905.
+Almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein field equations remain extremely difficult to find beyond those which exhibit significant symmetries.\\
+We can study the behavior of solutions under a high degree of symmetry considerations and could even solve analytically for highly unrealistic systems.
+In case of problems relevant to astrophysical and gravitational physics research, it still remains a big daunting question on how to get around the problem of solving these field equations.
 This question is so profound that it has a separate profound field of research which goes with the name of numerical relativity which attempts to use computation science and programming to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics are happening (as we can not solve for an infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
 Numerical methods have been used to solve the Einstein equation for many decades, but the past decade has seen tremendous advances and adding to that, the interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining.
-The field of numerical relativity is growing rampantly with the vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones) with the development of robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.
+The field of numerical relativity is growing rampantly with the vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones) with the development of robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.\\
 Reflecting the other end of the research community stands the major section of theoretical physicists which counts the majority as a novice in programming.
-The head challenge is the fact that the usage of these frameworks demands heavy use of high-level programming languages like C, C++, Python etc.
+The head challenge is the fact that the usage of these frameworks demands heavy use of high-level programming languages like C, C++, Python, etc.
 Though Python provides a vast room for abstractions no library existed that focused towards numerical relativity, eventually, the need of python library dedicated to general relativity became the propellant for the team and thus they made dauntless efforts to cover the space for this Python library.
-Since then, EinsteinPy has seen a lot of contributions from people all over the world and many "good to go" functionalities are already provided in this and previous versions.
-Like any other numerical relativity library, EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein's field equations an easy job for anyone who does not want to deal with intricacies of the subject along with few, very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity
-with every minute detail .in general\footnote{More details on this are given in further coming sections}.
-In further coming section, we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.
-Also, we describe few code snippets to explain the usage of the library on which more details can be found on the organisation website\footnote{https://einsteinpy.org/}
-Software development and tools form a significant part of research in astronomy and moreover, the field itself has long supported the development of software tools for astronomical tasks..
-These packages therefore typically provide some level of documentation and user support or training.
-.
-The development of the EinsteinPy core package began as a community-driven effort to standardize core functionality for software in Python which renders a  user-friendly interface for supporting numerical relativity and relativistic astrophysics research.
-The library is as an attempt to provide programming and numerical environment for numerous numerical relativity problems like geodesics plotter, gravitational lensing and ray tracing, solving and simulating relativistic hydrodynamical equations, plotting of black hole event horizons, solving Einstein’s field equations and simulating various dynamical systems like binary merger etc.
+Since then, EinsteinPy has seen a lot of contributions from people all over the world and many ”good to go” functionalities are already provided in this and previous versions.\\
+EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein’s field equations an easy job for anyone who does not want to deal with intricacies of the subject along with few, very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity with every minute detail.
+The library is as an attempt to provide programming and numerical environment for numerous numerical relativity problems like geodesics plotter, gravitational lensing and ray tracing, solving and simulating relativistic hydrodynamical equations, plotting of black hole event horizons, solving Einstein’s field equations and simulating various dynamical systems like binary merger etc.\\
+EinsteinPy provides an open-source and open-development core package and aims to build an ecosystem of affiliated packages that support numeric relativity functionality in the Python programming language.
+”Open development” describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes or other code changes, governance, or any other aspect of the development process is discussed.
+EinsteinPy core package is now a feature-rich library of sufficiently general tools and classes that support the development of more specialized code\\
+In the further coming section, we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.Also, we describe a few code snippets to explain the usage of the library on which more details can be found on the organization website.
+The development of the EinsteinPy core package began as a community-driven effort to standardize core functionality for software in Python which renders a user-friendly interface for supporting numerical relativity and relativistic astrophysics research.\\
+We start this paper by describing the way EinsteinPy functions followed by the main software efforts developed by the EinsteinPy itself with proper detailed documentation of the current version release.
+We end with a short vision for the future of EinsteinPy to its contribution in the field of computational methodology in gravitational and relativistic Astrophysics.
 
-At the same time, the scientific community contributing to the package has grown tremendously and an ecosystem of packages supporting or affiliated with the EinsteinPycore has developed. 
-EinsteinPy provides an open-source and open-development core package and an ecosystem of affiliated 
-packages that support numeric relativity functionality in the Python programming language.
-"Open development" describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes or other code changes, governance, or any other aspect of the development process is discussed.
-EinsteinPy core package is now a feature-rich library of sufficiently general tools and classes that support the development of more specialized code
+\section{Data Types} \label{sec:datatypes}
 
-In this paper, we describe the current status of the EinsteinPy core package and discuss goals for future development.
-We start by describing the way EinsteinPy functions followed by the main software efforts developed by the EinsteinPy itself with proper detailed documentation of the current version release.We end with a short vision for the future of EinsteinPy to its contribution in the field of computational methodology in gravitational and relativistic Astrophysics.
+The EinsteinPy package provides some core data types for calculating, operating on, visualizing geodesics and black holes.
+There are some data types created for symbolic manipulations and calculations of relativistic tensors.
+The most important data types for EinsteinPy are \texttt{Body}, \texttt{Geodesic} and \texttt{BaseRelativityTensor} objects that support defining and creating new bodies, storing and calculating geodesic for bodies, and handling respectively.
+The main purpose of these core classes is to standardize the way calculations and visualizations are done for various kinds of heavy cosmic bodies and black holes.
+The classes always maintain the consistency in units of measurement wherever applicable, and create a consistent and clean API for any non-programmer to understand.
+The classes are designed such that it resembles the flow of physics and are  as intuitional as possible.
+These core classes also include a rigid architecture for data manipulation and visualizations wherever applicable.
+Following sections provide deep insight into the above mentioned three code data types of EinsteinPy:
 
-\section{Units Handling}
-EinsteinPy has dependencies on Astropy for handling units and user have to use appropriate Astropy units\footnote{more on astropy units can be referred from their official website documentation} while declaring the input data to various methods which are further used in the computation.
-\section{Data Types} \label{sec:style}
-Since its inception,  EinsteinPy has aimed to provide is achieved by some set of data structures that are specifically designed to ease with a variety of gravitational physics problems.
-The most important and central quantity in all of the general relativity is the metric tensor $g_{\mu\nu}$ which defines the background geometry of spacetime on which all the dynamics happen.
-Informally the problem that packages of numerical relativity tend to solve is that we have a system (or matter field) defined by energy-momentum tensor $T_{\mu\nu}$ and we want to solve for the $g_{\mu\nu}$ such that it satisfies the following Einstein's field equation
-\[
-R_{\mu\nu} - \frac{1}{2}Rg_{\mu\nu} + \Lambda g_{\mu\nu} = \frac{8\pi G}{c^4}T_{\mu\nu}
-\]where $R_{\mu\nu}$ is contracted Riemannian tensor or Ricci tensor, $R$ is Ricci scalar, $\Lambda$ is cosmological constant.
-All the above quantities are derivatives of metric tensor\footnote{more on this can be referred from any standard general relativity text} so in simple terms, on the left-hand side of the equation are terms involving $g_{\mu\nu}$ and on the right-hand side are the matter field terms which only characterize the distribution of matter.\\
-EinsteinPy provides a core module: \texttt{metric} which has core data types of various metric tensors some which include Schwarzschild, Kerr, Kerr-Newman spacetime geometries(which are the exact solution of field equation for very specific matter distributions).
-The immediate functionalities which come along with this module are the solutions of geodesic equations.
-The module has coupled integration with \texttt{coordinates} module which deals with different coordinate system transformations\footnote{more on this in the 'coordinates' section}.
-Another core data types are in the \texttt{plotting} module which handles all the plotting, rendering, animation and simulation related methods and provides user-friendly interfacing of plots.
-One interesting feature of EinsteinPy is the support for symbolic tensor algebra which is extremely important in the formalism of general relativity and one of the first challenges faced by many beginners in their journey of learning the subject.
-EinsteinPy provides an excellent way to learn the math behind tensor manipulation and index gymnastics with the help of symbolic module: \texttt{symbolic}, on which more will be discussed in its section ahead.\\
+\subsection{Body} \label{subsec:Body}
+The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
 
-Features of EinsteinPy and section division.
-\textbf{Paper organisation}
+\begin{itemize}
+\item \texttt{name}: Body Name,
+\item \texttt{mass}: Mass of the body with attached astropy units 
+\item \texttt{R}: Radius of the body with attached astropy units
+\item \texttt{differential}: Complete position and velocity vector of the body in form of a Cartesian / Spherical / BoyerLindquist data class object from einsteinpy coordinates (optional)
+\item \texttt{a}: Spin factor (a) of the body for Kerr Solutions with attached astropy units (optional)
+\item \texttt{q}: Charge of the body with attached astropy units (optional)
+\item \texttt{is\_attractor}: A boolean variable concerned with if the body is to be supposed as a central attractor. (optional)
+\item \texttt{parent}: Parent body for the body, object of the same data class (optional)
+\end{itemize}
 
-			Organisation and Infrastructure
-EinsteinPy equations and notations:
-The purpose of this subsection is to clearly state the equations of motion that we have implemented and our conventions for completeness
+\subsection{Geodesic} \label{subsec:Geodesic}
+The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
 
-Evolution Equation
+\subsection{BaseRelativityTensor} \label{subsec:BaseRelativityTensor}
+The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
+\begin{itemize}
+\item \texttt{order} (Property) : Returns the order of the tensor. 
+\item \texttt{config} (Property) : Returns the arrangement of contravariant(upper)/covariant(lower) indices of the tensor. For example, 'ulll'.
+\item \texttt{parent\_metric} (Property) : Returns the metric tensor of the space-time associated with the tensor, if present. Else returns \texttt{None}.
+\item \texttt{tensor} (Function) : Returns the tensorial quantity contained within the class instance.
+\item \texttt{subs} (Function) : Returns a new tensor upon substitution of current variables with new variables/values.
+\item \texttt{simplify} (Function) : Returns a tensor contain simplified expressions from the current tensor.
+\item \texttt{symbols} (Function) : Returns the symbols denoting each axis of the space-time.
+\item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
+\end{itemize}
 
-EinsteinPy core package version 0.2
-Integrators
+\section{UNIT HANDLING} \label{sec:unithandle}
+All user-facing functionality provided by einsteinpy make use of astropy.units. 
+All functions and objects must have their input constrained to the appropriate type of unit (e.g., length, mass or energy).
+Inputs can then be provided with any units that match the required type (e.g., millimeters and inches are both valid units for length) and conversions occur automatically without user intervention.
+The einsteinpy.constant subpackage contains a few standard constants.
 
-Metric
+\section{Development Model} \label{sec:devmodels}
+The EinsteinPy Project follows an open development model, which is widely used in the scientific Python community and other computational astrophysics packages.
+The project is hosted on GitHub as a public repository with restricted write access to some key people.
+Anyone, however is welcome and encouraged to make code contributions and suggest changes using pull requests.
+Since the repository containing the codebase is licenced under an open and permissive MIT licence,  the project allows commercial use, modification, sublicensing, distribution and private use as long as the copyright notice and licence is redistributed.
+The project uses git for distributed version control and relies on CircleCI, Codefactor, GitHub Actions etc.
+for running the unit tests and other CI checks for every pull request.
+The code quality is maintained at the highest standards with strong control on the cyclomatic complexity, code linting, imports ordering and a proper docstring wherever necessary.
+Every contribution is reviewed and it must meet the following requirements:
 
-Utils
+\begin{itemize}
+\item \texttt The code must strictly adhere to the PEP8 Standards, on the top of it, the code must be linted with black to save the reviewer’s time identifying the changes made and reduce the diff generated because of the patch.
+\item \texttt The imports in the code must be sorted using tools such as isort. 
+\item \texttt The documentation follows numpy like docstrings, and a proper reStructured Text syntax is followed for writing the documentation.
+\item \texttt The changelog is populated at release-time by the lead developer and the releasing developer
+\end{itemize}
+EinsteinPy further follows a trunk-based development model, which ensures a new branch for every minor release and new patch release made using the minor release branch.
+All the latest changes are kept on the master branch on GitHub and the relevant issues are closed as soon as the pull request solving it merges onto the master.
+A release having the changes is made at a later date.
+EinsteinPy only supports the latest bleeding-edge Python, Numpy and Astropy versions.
+All the stable Python versions after Python 3.5 are supported.
+All the code snippets written follow the guidelines of numba in order to accelerate the Python code and make the simulations faster.
 
-Plotting
+\section{INFRASTRUCTURE} \label{sec:INFRASTRUCTURE}
+\subsection{ Testing} \label{subsec: Testing}
+The EinsteinPy Project maintains a very high bar in accepting changes and introducing new features.
+Every patch of code that is accepted in the codebase through any pull request has to be well tested using some unit tests unless given an exception after discussion with both the lead developers.
+Currently the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94% and we hope to improve it in the future.
+The 100% code coverage for this software at this level is not possible because of lack of accurate data to test the code against.
+We deliberately leave some parts of the codebase out of the testing loop because testing those modules is not possible with the current knowledge level and expertise.
+However, 94% code coverage is good enough when we consider other packages in scientific Python community who face the similar problem.
 
-Constant
+The test suite can be run manually as well as it runs in an automated fashion on every commit as well as pull request to maintain the code standards, and make it easier for contributors to understand the implications and impact of their changes.
+The EinsteinPy Project uses many continuous-integration services which provide services to create automated pipelines for code inspection, unit testing, coverage publishing etc.
+All the contributions trigger these free services (Codecov, CircleCI, Appveyor, GitHub Actions, Codefactor, Codeclimate, Hound, WIP) which are integrated with GitHub repository.
+All the pull requests are checked for code linting by a pep8speaks bot, which suggests the lines of code which violate the PEP8 standard to the contributor in a human readable way.
+All these services run on three types of operating systems (Windows, MacOS and Linux).
+The unit tests run on various versions of Python.
+They test the documentation builds, test coverage, check whether the pull request author has indicated that it is a work in progress (WIP).They also run several code linting checks which further triggers the unit test build.
 
-Coordinates
+\subsection{ Documentation and gallery} \label{subsec:  Documentation and gallery}
 
-Geodesic
+\section{COMMUNITY} \label{sec:COMMUNITY}
+EinsteinPy is being developed as an open source community inside the wide and diverse general scientific python community.
+Our code is freely available, and we have seen a lot of people contributing and joining us since over the past year.
+We touched the landmark of 30 members recently.
+EinsteinPy is dedicated to problems arising in General Relativity and gravitational physics as well as encouraging open source development.
+EinsteinPy has benefited greatly from summer of code schemes.
+Last year EinsteinPy participated in the ESA Summer of Code In Space (SOCIS).
+This program is inspired by Google Summer Of Code (GSOC) and aims to raise the awareness of open source projects related to space, promote the European Space Agency.
+The symbolic module in EinsteinPy project was developed during this program.
 
-Bodies
+\section{FUTURE} \label{sec:FUTURE}
+We intend to add more functionalities to our project, some of which are, 
+\begin{itemize}
+\item \texttt Support for null-geodesics in different geometries, . 
+\item \texttt Relativistic hydrodynamics
+\item \texttt Adaptive Mesh Refinement 
+\item \texttt Providing numerical solutions to Einstein’s equations for arbitrarily complex matter distribution.
+\end{itemize}
 
-Hypersurface
+We have an open community where suggestions from people to add functionalities are welcome. We wish to be as helpful as possible to people using EinsteinPy in.
 
-symbolic
-Support of EinsteinPy
-The EinsteinPy Project, as of the version 0.2release, does not receive any direct financial support for the development of EinsteinPy.
-Development of the software, all supporting materials, and community support are provided by individuals who work on EinsteinPy in their own personal time, by individuals or groups contributing to EinsteinPy as part of a research project.
-( A list of organizations that have contributed to EinsteinPy in this manner can be found in the Acknowledgments)
-
-Release Cycle and Long-term Support
-The EinsteinPy package is updated with significant changes and bug fixes in every release.
-The major releases contain new features or any significant changes, whereas the bugfix releases only contain fixes to code or documentation but no new features.
-
-Following sections will give a breif overview of every core module and some of their important functionalities.
-\subsection{tensor}
-\subsection{metric}
-\texttt{metric} module give users the freedom to define metric object which can be further used in the computations related to spacetime geometry.
-Let's see an small example of solving geodesic equation in Kerr spacetime and obtaining trajectories using EinsteinPy
-\subsection{coordinates}
-%\begin{minted}[linenos]{python}
-%# importing modules
-from astropy import units as u
-import numpy as np
-from einsteinpy.metric import Kerr
-from einsteinpy.coordinates import BoyerLindquistDifferential
-
-%# initializing parameters and coordinate system
-%M = 1.989e30 * u.kg
-%a = 0.3 * u.m
-%BL_obj = BoyerLindquistDifferential(50e5 * u.km, np.pi / 2 * u.rad, np.pi * u.rad,
-     %                               0 * u.km / u.s, 0 * u.rad / u.s, 0 * u.rad / u.s,
-          %                          a)
-%end_lambda = ((1 * u.year).to(u.s)).value / 930
-
-%# Choosing stepsize for ODE solver to be 0.02 minutes
-%stepsize = ((0.02 * u.min).to(u.s)).value
-
-%# defining Kerr spacetime metric object
-%obj = Kerr.from_coords(BL_obj, M)
-
-%# calculates the trajectory
-%ans = obj.calculate_trajectory(
-    %end_lambda=end_lambda, OdeMethodKwargs={"stepsize": stepsize}, return_cartesian=True
-%)
-%\end{minted}
-\subsection{plotting}
-\subsection{symbolic}
-\subsection{hypersurface}
-This module provides with basic computational functions which are essential for modelling the space-like hypersurface for any spacetime geometry.
-Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities.
-The whole module is expected to extend for providing a superclass for implementations related to gravitationl lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems.
-A small code snippet for plotting the hypersurface is as follows:
-%\begin{minted}[linenos]{python}
-%# importing the modules
-from einsteinpy.hypersurface import SchwarzschildEmbedding
-from astropy import units as u
-
-%# Declaring embedding object with specified mass of the body 
-%surface_obj = SchwarzschildEmbedding(5.927e23 * u.kg)
-%surface_obj.plot_hypersurface(plot_type='surface')
-
-%# plotting the embedding hypersurface for Schwarzschild spacetime
-%surface_obj.show()
-%\end{minted}
-\includegraphics[scale=0.5]{hypersurface_surface.png}
-
-\section{Displaying mathematics} \label{sec:displaymath}
-
-The most common mathematical symbols and formulas are in the amsmath
-package.  \aastex\ requires this package so there is no need to
-specifically call for it in the document preamble.  Most modern \latex\
-distributions already contain this package.  If you do not have this
-package or the other required packages, revtex4-1, latexsym, graphicx,
-amssymb, longtable, and epsf, they can be obtained from 
-\url{http://www.ctan.org}
-
-Mathematics can be displayed either within the text, e.g. $E = mc^2$, or
-separate from in an equation.  In order to be properly rendered, all inline
-math text has to be declared by surrounding the math by dollar signs (\$).
-
-A complex equation example with inline math as part of the explanation
-follows.
-
-\begin{equation}
-\bar v(p_2,\sigma_2)P_{-\tau}\hat a_1\hat a_2\cdots
-\hat a_nu(p_1,\sigma_1) ,
-\end{equation}
-where $p$ and $\sigma$ label the initial $e^{\pm}$ four-momenta
-and helicities $(\sigma = \pm 1)$, $\hat a_i=a^\mu_i\gamma_\nu$
-and $P_\tau=\frac{1}{2}(1+\tau\gamma_5)$ is a chirality projection
-operator $(\tau = \pm1)$.  This produces a single line formula.  \latex\ will
-auto-number this and any subsequent equations.  If no number is desired then
-the {\tt\string equation} call should be replaced with {\tt\string displaymath}.
-
-\latex\ can also handle a a multi-line equation.  Use {\tt\string eqnarray}
-for more than one line and end each line with a
-\textbackslash\textbackslash.  Each line will be numbered unless the
-\textbackslash\textbackslash\ is preceded by a {\tt\string\nonumber}
-command.  Alignment points can be added with ampersands (\&).  There should be
-two ampersands per line. In the examples they are centered on the equal
-symbol.
-
-\begin{eqnarray}
-\gamma^\mu  & = &
- \left(
-\begin{array}{cc}
-0 & \sigma^\mu_+ \\
-\sigma^\mu_- & 0
-\end{array}     \right) ,
- \gamma^5= \left(
-\begin{array}{cc}
--1 &   0\\
-0 &   1
-\end{array}     \right)  , \\
-\sigma^\mu_{\pm}  & = &   ({\bf 1} ,\pm \sigma) , 
-\end{eqnarray}
-
-\begin{eqnarray}
-\hat a & = & \left(
-\begin{array}{cc}
-0 & (\hat a)_+\\
-(\hat a)_- & 0
-\end{array}\right), \nonumber \\
-(\hat a)_\pm & = & a_\mu\sigma^\mu_\pm 
-\end{eqnarray}
-
-%% Putting eqnarrays or equations inside the mathletters environment groups
-%% the enclosed equations by letter. For instance, the eqnarray below, instead
-%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
-%% LaTeX the paper and look at the output to see the results.
-
-\section{Revision tracking and color highlighting} \label{sec:highlight}
-
-Authors sometimes use color to highlight changes to their manuscript in
-response to editor and referee comments.  In \aastex\ new commands
-have been introduced to make this easier and formalize the process.
-
-The first method is through a new set of editing mark up commands that
-specifically identify what has been changed.  These commands are
-{\tt\string\added\{<text>\}}, {\tt\string\deleted\{<text>\}}, and
-{\tt\string\replaced\{<old text>\}\{<replaced text>\}}. To activate these
-commands the {\tt\string trackchanges} option must be used in the
-{\tt\string\documentclass} call.  When compiled this will produce the
-marked text in red.  The {\tt\string\explain\{<text>\}} can be used to add
-text to provide information to the reader describing the change.  Its
-output is purple italic font. To see how {\tt\string\added\{<important
-added info>\}}, {\tt\string\deleted\{<this can be deleted text>\}},
-{\tt\string\replaced\{<old data>\}\{<replaced data>\}}, and \break
-{\tt\string\explain\{<text explaining the change>\}} commands will produce
-\added{important added information}\deleted{, deleted text, and }
-\replaced{old data}{and replaced data,} toggle between versions compiled with
-and without the {\tt\string trackchanges} option.\explain{text explaining
-the change}
-
-A summary list of all these tracking commands can be produced at the end of
-the article by adding the {\tt\string\listofchanges} just before the
-{\tt\string\end\{document\}} call.  The page number for each change will be
-provided. If the {\tt\string linenumbers} option is also included in the
-documentcall call then not only will all the lines in the article be
-numbered for handy reference but the summary list will also include the
-line number for each change.
-
-The second method does not have the ability to highlight the specific
-nature of the changes but does allow the author to document changes over
-multiple revisions.  The commands are {\tt\string\edit1\{<text>\}},
-{\tt\string\edit2\{<text>\}} and {\tt\string\edit3\{<text>\}} and they
-produce {\tt\string<text>} that is highlighted in bold red, italic blue and
-underlined purple, respectively.  Authors should use the first command to
-\edit1{indicated which text has been changed from the first revision.}  The
-second command is to highlight \edit2{new or modified text from a second
-revision}.  If a third revision is needed then the last command should be used 
-\edit3{to show this changed text}.  Since over 90\% of all manuscripts are
-accepted after the 3rd revision these commands make it easy to identify
-what text has been added and when.  Once the article is accepted all the
-highlight color can be turned off simply by adding the
-{\tt\string\turnoffediting} command in the preamble. Likewise, the new commands
-{\tt\string\turnoffeditone}, {\tt\string\turnoffedittwo}, and
-{\tt\string\turnoffeditthree} can be used to only turn off the 
-{\tt\string\edit1\{<text>\}}, {\tt\string\edit2\{<text>\}} and 
-{\tt\string\edit3\{<text>\}}, respectively.
-
-Similar to marking editing changes with the {\tt\string\edit} options there
-are also the {\tt\string\authorcomments1\{<text>\}}, 
-{\tt\string\authorcomments2\{<text>\}} and
-{\tt\string\authorcomments3\{<text>\}} commands.  These produce the same
-bold red, italic blue and underlined purple text but when the
-{\tt\string\turnoffediting} command is present the {\tt\string<text>}
-material does not appear in the manuscript.  Authors can use these commands
-to mark up text that they are not sure should appear in the final
-manuscript or as a way to communicate comments between co-authors when
-writing the article.
-
-\section{Software and third party data repository citations} \label{sec:cite}
-
-The AAS Journals would like to encourage authors to change software and
-third party data repository references from the current standard of a
-footnote to a first class citation in the bibliography.  As a bibliographic
-citation these important references will be more easily captured and credit
-will be given to the appropriate people.
-
-The first step to making this happen is to have the data or software in
-a long term repository that has made these items available via a persistent
-identifier like a Digital Object Identifier (DOI).  A list of repositories
-that satisfy this criteria plus each one's pros and cons are given at \break
-\url{https://github.com/AASJournals/Tutorials/tree/master/Repositories}.
-
-In the bibliography the format for data or code follows this format: \\
-
-\noindent author year, title, version, publisher, prefix:identifier\\
-
-\citet{2015ApJ...805...23C} provides a example of how the citation in the
-article references the external code at
-\doi{10.5281/zenodo.15991}.  Unfortunately, bibtex does
-not have specific bibtex entries for these types of references so the
-``@misc'' type should be used.  The Repository tutorial explains how to
-code the ``@misc'' type correctly.  The most recent aasjournal.bst file,
-available with \aastex\ v6, will output bibtex ``@misc'' type properly.
-
-%% If you wish to include an acknowledgments section in your paper,
-%% separate it off from the body of the text using the \acknowledgments
-%% command.
 \acknowledgments
@@
 %% authors a place to specify which programs were used during the creation of 
-%% the manusscript. Authors should list each code and include either a
+%% the manuscript. Authors should list each code and include either a
 %% citation or url to the code inside ()s when available.
@@
 
-\section{Author publication charges} \label{sec:pubcharge}
+%% For this sample we use BibTeX plus aasjournals.bst to generate the
+%% the bibliography. The sample63.bib file was populated from ADS. To
+%% get the citations to show in the compiled file do the following:
+%%
+%% pdflatex sample63.tex
+%% bibtext sample63
+%% pdflatex sample63.tex
+%% pdflatex sample63.tex
 
-Finally some information about the AAS Journal's publication charges.
-In April 2011 the traditional way of calculating author charges based on 
-the number of printed pages was changed.  The reason for the change
-was due to a recognition of the growing number of article items that could not 
-be represented in print. Now author charges are determined by a number of
-digital ``quanta''.  A single quantum is 350 words, one figure, one table,
-and one enhanced digital item.  For the latter this includes machine readable
-tables, figure sets, animations, and interactive figures.  The current cost
-is \$27 per word quantum and \$30 for all other quantum type.
+\bibliography{sample63}{}
+\bibliographystyle{aasjournal}
 
-\section{Rotating tables} \label{sec:rotate}
-
-The process of rotating tables into landscape mode is slightly different in
-\aastex v6.2. Instead of the {\tt\string\rotate} command, a new environment
-has been created to handle this task. To place a single page table in a
-landscape mode start the table portion with
-{\tt\string\begin\{rotatetable\}} and end with
-{\tt\string\end\{rotatetable\}}.
-
-Tables that exceed a print page take a slightly different environment since
-both rotation and long table printing are required. In these cases start
-with {\tt\string\begin\{longrotatetable\}} and end with
-{\tt\string\end\{longrotatetable\}}. Table \ref{chartable} is an
-example of a multi-page, rotated table.
-
-\begin{longrotatetable}
-\begin{deluxetable*}{lllrrrrrrll}
-\tablecaption{Observable Characteristics of 
-Galactic/Magellanic Cloud novae with X-ray observations\label{chartable}}
-\tablewidth{700pt}
-\tabletypesize{\scriptsize}
-\tablehead{
-\colhead{Name} & \colhead{V$_{max}$} & 
-\colhead{Date} & \colhead{t$_2$} & 
-\colhead{FWHM} & \colhead{E(B-V)} & 
-\colhead{N$_H$} & \colhead{Period} & 
-\colhead{D} & \colhead{Dust?} & \colhead{RN?} \\ 
-\colhead{} & \colhead{(mag)} & \colhead{(JD)} & \colhead{(d)} & 
-\colhead{(km s$^{-1}$)} & \colhead{(mag)} & \colhead{(cm$^{-2}$)} &
-\colhead{(d)} & \colhead{(kpc)} & \colhead{} & \colhead{}
-} 
-\startdata
-CI Aql & 8.83 (1) & 2451665.5 (1) & 32 (2) & 2300 (3) & 0.8$\pm0.2$ (4) & 1.2e+22 & 0.62 (4) & 6.25$\pm5$ (4) & N & Y \\
-{\bf CSS081007} & \nodata & 2454596.5 & \nodata & \nodata & 0.146 & 1.1e+21 & 1.77 (5) & 4.45$\pm1.95$ (6) & \nodata & \nodata \\
-GQ Mus & 7.2 (7) & 2445352.5 (7) & 18 (7) & 1000 (8) & 0.45 (9) & 3.8e+21  & 0.059375 (10) & 4.8$\pm1$ (9) & N (7) & \nodata \\
-IM Nor & 7.84 (11) & 2452289 (2) & 50 (2) & 1150 (12) & 0.8$\pm0.2$ (4) & 8e+21 & 0.102 (13) & 4.25$\pm3.4$ (4) & N & Y \\
-{\bf KT Eri} & 5.42 (14) & 2455150.17 (14) & 6.6 (14) & 3000 (15) & 0.08 (15) & 5.5e+20 & \nodata & 6.5 (15) & N & M \\
-{\bf LMC 1995} & 10.7 (16) & 2449778.5 (16) & 15$\pm2$ (17) & \nodata & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
-LMC 2000 & 11.45 (18) & 2451737.5 (18) & 9$\pm2$ (19) & 1700 (20) & 0.15 (203) & 7.8e+20  & \nodata & 50 & \nodata & \nodata \\
-{\bf LMC 2005} & 11.5 (21) & 2453700.5 (21) & 63 (22) & 900 (23) & 0.15 (203) & 1e+21 & \nodata & 50  & M (24) & \nodata \\
-{\bf LMC 2009a} & 10.6 (25) & 2454867.5 (25) & 4$\pm1$  & 3900 (25) & 0.15 (203)  & 5.7e+20 & 1.19 (26) & 50 & N & Y \\
-{\bf SMC 2005} & 10.4 (27) & 2453588.5 (27) & \nodata & 3200 (28) & \nodata & 5e+20  & \nodata & 61 & \nodata & \nodata \\
-{\bf QY Mus} & 8.1 (29) & 2454739.90 (29) & 60:  & \nodata & 0.71 (30) & 4.2e+21  & \nodata & \nodata & M & \nodata \\
-{\bf RS Oph} & 4.5 (31) & 2453779.44 (14) & 7.9 (14) & 3930 (31) & 0.73 (32) & 2.25e+21 & 456 (33) & 1.6$\pm0.3$ (33) & N (34) & Y \\
-{\bf U Sco} & 8.05 (35) & 2455224.94 (35) & 1.2 (36) & 7600 (37) & 0.2$\pm0.1$ (4) & 1.2e+21 & 1.23056 (36) & 12$\pm2$ (4) & N & Y \\
-{\bf V1047 Cen} & 8.5 (38) & 2453614.5 (39) & 6 (40) & 840 (38) & \nodata & 1.4e+22  & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1065 Cen} & 8.2 (41) & 2454123.5 (41) & 11 (42) & 2700 (43) & 0.5$\pm0.1$ (42) & 3.75e+21 & \nodata & 9.05$\pm2.8$ (42) & Y (42) & \nodata \\
-V1187 Sco & 7.4 (44) & 2453220.5 (44) & 7: (45) & 3000 (44) & 1.56 (44) & 8.0e+21 & \nodata & 4.9$\pm0.5$ (44) & N & \nodata \\
-{\bf V1188 Sco} & 8.7 (46) & 2453577.5 (46) & 7 (40) & 1730 (47) & \nodata & 5.0e+21  & \nodata & 7.5 (39) & \nodata & \nodata \\
-{\bf V1213 Cen} & 8.53 (48) & 2454959.5 (48) & 11$\pm2$ (49) & 2300 (50) & 2.07 (30) & 1.0e+22 & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1280 Sco} & 3.79 (51) & 2454147.65 (14) & 21 (52) & 640 (53) & 0.36 (54) & 1.6e+21  & \nodata & 1.6$\pm0.4$ (54) & Y (54) & \nodata \\
-{\bf V1281 Sco} & 8.8 (55) & 2454152.21 (55) & 15:& 1800 (56) & 0.7 (57) & 3.2e+21 & \nodata & \nodata & N & \nodata \\
-{\bf V1309 Sco} & 7.1 (58) & 2454714.5 (58) & 23$\pm2$ (59) & 670 (60) & 1.2 (30) & 4.0e+21 & \nodata & \nodata & \nodata & \nodata \\
-{\bf V1494 Aql} & 3.8 (61) & 2451515.5 (61) & 6.6$\pm0.5$ (61) & 1200 (62) & 0.6 (63) & 3.6e+21  & 0.13467 (64) & 1.6$\pm0.1$ (63) & N & \nodata \\
-{\bf V1663 Aql} & 10.5 (65) & 2453531.5 (65) & 17 (66) & 1900 (67) & 2: (68) & 1.6e+22  & \nodata & 8.9$\pm3.6$ (69) & N & \nodata \\
-V1974 Cyg & 4.3 (70) & 2448654.5 (70) & 17 (71) & 2000 (19) & 0.36$\pm0.04$ (71) & 2.7e+21  & 0.081263 (70) & 1.8$\pm0.1$ (72) & N & \nodata \\
-{\bf V2361 Cyg} & 9.3 (73) & 2453412.5 (73) & 6 (40) & 3200 (74) & 1.2: (75) & 7.0e+21 & \nodata & \nodata & Y (40) & \nodata \\
-{\bf V2362 Cyg} & 7.8 (76) & 2453831.5 (76) & 9 (77) & 1850 (78) & 0.575$\pm0.015$ (79) & 4.4e+21  & 0.06577 (80) & 7.75$\pm3$ (77) & Y (81) & \nodata \\
-{\bf V2467 Cyg} & 6.7 (82) & 2454176.27 (82) & 7 (83) & 950 (82) & 1.5 (84) & 1.4e+22  & 0.159 (85) & 3.1$\pm0.5$ (86) & M (87) & \nodata \\
-{\bf V2468 Cyg} & 7.4 (88) & 2454534.2 (88) & 10: & 1000 (88) & 0.77 (89) & 1.0e+22  & 0.242 (90) & \nodata & N & \nodata \\
-{\bf V2491 Cyg} & 7.54 (91) & 2454567.86 (91) & 4.6 (92) & 4860 (93) & 0.43 (94) & 4.7e+21  & 0.09580: (95) & 10.5 (96) & N & M \\
-V2487 Oph & 9.5 (97) & 2450979.5 (97) & 6.3 (98) & 10000 (98) & 0.38$\pm0.08$ (98) & 2.0e+21 & \nodata & 27.5$\pm3$ (99) & N (100) & Y (101) \\
-{\bf V2540 Oph} & 8.5 (102) & 2452295.5 (102) & \nodata & \nodata & \nodata & 2.3e+21 & 0.284781 (103) & 5.2$\pm0.8$ (103) & N & \nodata \\
-V2575 Oph & 11.1 (104) & 2453778.8 (104) & 20: & 560 (104) & 1.4 (105) & 3.3e+21 & \nodata & \nodata & N (105) & \nodata \\
-{\bf V2576 Oph} & 9.2 (106) & 2453832.5 (106) & 8: & 1470 (106) & 0.25 (107) & 2.6e+21  & \nodata & \nodata & N & \nodata \\
-{\bf V2615 Oph} & 8.52 (108) & 2454187.5 (108) & 26.5 (108) & 800 (109) & 0.9 (108) & 3.1e+21  & \nodata & 3.7$\pm0.2$ (108) & Y (110) & \nodata \\
-{\bf V2670 Oph} & 9.9 (111) & 2454613.11 (111) & 15: & 600 (112) & 1.3: (113) & 2.9e+21  & \nodata & \nodata & N (114) & \nodata \\
-{\bf V2671 Oph} & 11.1 (115) & 2454617.5 (115) & 8: & 1210 (116) & 2.0 (117) & 3.3e+21  & \nodata & \nodata & M (117) & \nodata \\
-{\bf V2672 Oph} & 10.0 (118) & 2455060.02 (118) & 2.3 (119) & 8000 (118) & 1.6$\pm0.1$ (119) & 4.0e+21  & \nodata & 19$\pm2$ (119) & \nodata & M \\
-V351 Pup & 6.5 (120) & 2448617.5 (120) & 16 (121) & \nodata & 0.72$\pm0.1$ (122) & 6.2e+21 & 0.1182 (123) & 2.7$\pm0.7$ (122) & N & \nodata \\
-{\bf V382 Nor} & 8.9 (124) & 2453447.5 (124) & 12 (40) & 1850 (23) & \nodata & 1.7e+22 & \nodata & \nodata & \nodata & \nodata \\
-V382 Vel & 2.85 (125) & 2451320.5 (125) & 4.5 (126) & 2400 (126) & 0.05: (126) & 3.4e+21  & 0.146126 (127) & 1.68$\pm0.3$ (126) & N & \nodata \\
-{\bf V407 Cyg} & 6.8 (128) & 2455266.314 (128) & 5.9 (129) & 2760 (129) & 0.5$\pm0.05$ (130) & 8.8e+21 & 15595 (131) & 2.7 (131) & \nodata & Y \\
-{\bf V458 Vul} & 8.24 (132) & 2454322.39 (132) & 7 (133) & 1750 (134) & 0.6 (135) & 3.6e+21 & 0.06812255 (136) & 8.5$\pm1.8$ (133) & N (135) & \nodata \\
-{\bf V459 Vul} & 7.57 (137) & 2454461.5 (137) & 18 (138) & 910 (139) & 1.0 (140) & 5.5e+21  & \nodata & 3.65$\pm1.35$ (138) & Y (140) & \nodata \\
-V4633 Sgr & 7.8 (141) & 2450895.5 (141) & 19$\pm3$ (142) & 1700 (143) & 0.21 (142) & 1.4e+21  & 0.125576 (144) & 8.9$\pm2.5$ (142) & N & \nodata \\
-{\bf V4643 Sgr} & 8.07 (145) & 2451965.867 (145) & 4.8 (146) & 4700 (147) & 1.67 (148) & 1.4e+22 & \nodata & 3 (148) & N & \nodata \\
-{\bf V4743 Sgr} & 5.0 (149) & 2452537.5 (149) & 9 (150) & 2400 (149) & 0.25 (151) & 1.2e+21 & 0.281 (152) & 3.9$\pm0.3$ (151) & N & \nodata \\
-{\bf V4745 Sgr} & 7.41 (153) & 2452747.5 (153) & 8.6 (154) & 1600 (155) & 0.1 (154) & 9.0e+20  & 0.20782 (156) & 14$\pm5$ (154) & \nodata & \nodata \\
-{\bf V476 Sct} & 10.3 (157) & 2453643.5 (157) & 15 (158) & \nodata & 1.9 (158) & 1.2e+22  & \nodata & 4$\pm1$ (158) & M (159) & \nodata \\
-{\bf V477 Sct} & 9.8 (160) & 2453655.5 (160) & 3 (160) & 2900 (161) & 1.2: (162) & 4e+21  & \nodata & \nodata & M (163) & \nodata \\
-{\bf V5114 Sgr} & 8.38 (164) & 2453081.5 (164) & 11 (165) & 2000 (23) & \nodata & 1.5e+21  & \nodata & 7.7$\pm0.7$ (165) & N (166) & \nodata \\
-{\bf V5115 Sgr} & 7.7 (167) & 2453459.5 (167) & 7 (40) & 1300 (168) & 0.53 (169) & 2.3e+21  & \nodata & \nodata & N (169) & \nodata \\
-{\bf V5116 Sgr} & 8.15 (170) & 2453556.91 (170) & 6.5 (171) & 970 (172) & 0.25 (173) & 1.5e+21 & 0.1238 (171) & 11$\pm3$ (173) & N (174) & \nodata \\
-{\bf V5558 Sgr} & 6.53 (175) & 2454291.5 (175) & 125 (176) & 1000 (177) & 0.80 (178) & 1.6e+22  & \nodata & 1.3$\pm0.3$ (176) & N (179) & \nodata \\
-{\bf V5579 Sgr} & 5.56 (180) & 2454579.62 (180) & 7: & 1500 (23) & 1.2 (181) & 3.3e+21 & \nodata & \nodata & Y (181) & \nodata \\
-{\bf V5583 Sgr} & 7.43 (182) & 2455051.07 (182) & 5: & 2300 (182) & 0.39 (30) & 2.0e+21 & \nodata & 10.5 & \nodata & \nodata \\
-{\bf V574 Pup} & 6.93 (183) & 2453332.22 (183) & 13 (184) & 2800 (184) & 0.5$\pm0.1$  & 6.2e+21 & \nodata & 6.5$\pm1$  & M (185) & \nodata \\
-{\bf V597 Pup} & 7.0 (186) & 2454418.75 (186) & 3: & 1800 (187) & 0.3 (188) & 5.0e+21  & 0.11119 (189) & \nodata & N (188) & \nodata \\
-{\bf V598 Pup} & 3.46 (14) & 2454257.79 (14) & 9$\pm1$ (190) & \nodata & 0.16 (190) & 1.4e+21 & \nodata & 2.95$\pm0.8$ (190) & \nodata & \nodata \\
-{\bf V679 Car} & 7.55 (191) & 2454797.77 (191) & 20: & \nodata & \nodata & 1.3e+22  & \nodata & \nodata & \nodata & \nodata \\
-{\bf V723 Cas} & 7.1 (192) & 2450069.0 (192) & 263 (2) & 600 (193) & 0.5 (194) & 2.35e+21  & 0.69 (195) & 3.86$\pm0.23$ (196) & N & \nodata \\
-V838 Her & 5 (197) & 2448340.5 (197) & 2 (198) & \nodata & 0.5$\pm0.1$ (198) & 2.6e+21  & 0.2975 (199) & 3$\pm1$ (198) & Y (200) & \nodata \\
-{\bf XMMSL1 J06} & 12 (201) & 2453643.5 (202) & 8$\pm2$ (202) & \nodata & 0.15 (203) & 8.7e+20 & \nodata & 50 & \nodata & \nodata \\
-\enddata
-\end{deluxetable*}
-\end{longrotatetable}
-
-A handy "cheat sheat" that provides the necessary LaTeX to produce 17 
-different types of tables is available at \url{http://journals.aas.org/authors/aastex/aasguide.html#table_cheat_sheet}.
-
-%% The reference list follows the main body and any appendices.
-%% Use LaTeX's thebibliography environment to mark up your reference list.
-%% Note \begin{thebibliography} is followed by an empty set of
-%% curly braces.  If you forget this, LaTeX will generate the error
-%% "Perhaps a missing \item?".
-%%
-%% thebibliography produces citations in the text using \bibitem-\cite
-%% cross-referencing. Each reference is preceded by a
-%% \bibitem command that defines in curly braces the KEY that corresponds
-%% to the KEY in the \cite commands (see the first section above).
-%% Make sure that you provide a unique KEY for every \bibitem or else the
-%% paper will not LaTeX. The square brackets should contain
-%% the citation text that LaTeX will insert in
-%% place of the \cite commands.
-
-%% We have used macros to produce journal name abbreviations.
-%% \aastex provides a number of these for the more frequently-cited journals.
-%% See the Author Guide for a list of them.
-
-%% Note that the style of the \bibitem labels (in []) is slightly
-%% different from previous examples.  The natbib system solves a host
-%% of citation expression problems, but it is necessary to clearly
-%% delimit the year from the author name used in the citation.
-%% See the natbib documentation for more details and options.
-
-\begin{thebibliography}{}
-
-\bibitem[Astropy Collaboration et al.(2013)]{2013A&A...558A..33A} Astropy Collaboration, Robitaille, T.~P., Tollerud, E.~J., et al.\ 2013, \aap, 558, A33 
-\bibitem[Bertin \& Arnouts(1996)]{1996A&AS..117..393B} Bertin, E., \& Arnouts, S.\ 1996, \aaps, 117, 393 
-\bibitem[Corrales(2015)]{2015ApJ...805...23C} Corrales, L.\ 2015, \apj, 805, 23
-\bibitem[Ferland et al.(2013)]{2013RMxAA..49..137F} Ferland, G.~J., Porter, R.~L., van Hoof, P.~A.~M., et al.\ 2013, \rmxaa, 49, 137
-\bibitem[Hanisch \& Biemesderfer(1989)]{1989BAAS...21..780H} Hanisch, R.~J., \& Biemesderfer, C.~D.\ 1989, \baas, 21, 780 
-\bibitem[Lamport(1994)]{lamport94} Lamport, L. 1994, LaTeX: A Document Preparation System, 2nd Edition (Boston, Addison-Wesley Professional)
-\bibitem[Schwarz et al.(2011)]{2011ApJS..197...31S} Schwarz, G.~J., Ness, J.-U., Osborne, J.~P., et al.\ 2011, \apjs, 197, 31  
-\bibitem[Vogt et al.(2014)]{2014ApJ...793..127V} Vogt, F.~P.~A., Dopita, M.~A., Kewley, L.~J., et al.\ 2014, \apj, 793, 127
-
-\end{thebibliography}
-
-%% This command is needed to show the entire author+affilation list when
+%% This command is needed to show the entire author+affiliation list when
 %% the collaboration and author truncation commands are used.  It has to
@@
 %\listofchanges
-
 \end{document}
-
-% End of file `sample62.tex'.

### 2020-01-19 sections/abstract.tex
Add Abstract as a section

--- 2020-01-18 paper.tex
@@
-%% Beginning of file 'sample63.tex'
-%%
-%% Modified 2019 June
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.3 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
-
-%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
-%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
-%% All of these external packages should already be present in the modern TeX 
-%% distributions.  If not they can also be obtained at www.ctan.org.
-
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%%
-%% using aastex version 6.3
-\documentclass{aastex63}
-
-%% The default is a single spaced, 10 point font, single spaced article.
-%% There are 5 other style options available via an optional argument. They
-%% can be invoked like this:
-%%
-%% \documentclass[arguments]{aastex63}
-%% 
-%% where the layout options are:
-%%
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.  
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%% 		  wider left and right margins. This uses the Daniel
-%% 		  Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Preferred style for Research Notes which are by design 
-%%                lacking an abstract and brief. DO NOT use \begin{abstract}
-%%                and \end{abstract} with this style.
-%%
-%% Note that you can submit to the AAS Journals in any of these 6 styles.
-%%
-%% There are other optional arguments one can invoke to allow other stylistic
-%% actions. The available options are:
-%%
-%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
-%%   tighten      : Makes baselineskip slightly smaller, only works with 
-%%                  the twocolumn substyle.
-%%   times        : uses times font instead of the default
-%%   linenumbers  : turn on lineno package.
-%%   trackchanges : required to see the revision mark up and print its output
-%%   longauthor   : Do not use the more compressed footnote style (default) for 
-%%                  the author/collaboration/affiliations. Instead print all
-%%                  affiliation information after each name. Creates a much 
-%%                  longer author list but may be desirable for short 
-%%                  author papers.
-%% twocolappendix : make 2 column appendix.
-%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
-%%                  for dual anonymous review.
-%%
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex63}
-%%
-%% AASTeX v6.* now includes \hyperref support. While we have built in specific
-%% defaults into the classfile you can manually override them with the
-%% \hypersetup command. For example,
-%%
-%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
-%%
-%% will change the color of the internal links to red, the links to the
-%% bibliography to green, the file links to cyan, and the external links to
-%% magenta. Additional information on \hyperref options can be found here:
-%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
-%%
-%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
-%% to improve the accessibility of the compiled pdf file.
-%%
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{June 1, 2019}
-\revised{January 10, 2019}
-\accepted{\today}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the argument.
-\submitjournal{ApJ}
-
-%% For manuscript that include authors in collaborations, AASTeX v6.3
-%% builds on the \collaboration command to allow greater freedom to 
-%% keep the traditional author+affiliation information but only show
-%% subsets. The \collaboration command now must appear AFTER the group
-%% of authors in the collaboration and it takes TWO arguments. The last
-%% is still the collaboration identifier. The text given in this
-%% argument is what will be shown in the manuscript. The first argument
-%% is the number of author above the \collaboration command to show with
-%% the collaboration text. If there are authors that are not part of any
-%% collaboration the \nocollaboration command is used. This command takes
-%% one argument which is also the number of authors above to show. A
-%% dashed line is shown to indicate no collaboration. This example manuscript
-%% shows how these commands work to display specific set of authors 
-%% on the front page.
-%%
-%% For manuscript without any need to use \collaboration the 
-%% \AuthorCollaborationLimit command from v6.2 can still be used to 
-%% show a subset of authors.
-%
-%\AuthorCollaborationLimit=2
-%
-%% will only show Schwarz & Muench on the front page of the manuscript
-%% (assuming the \collaboration and \nocollaboration commands are
-%% commented out).
-%%
-%% Note that all of the author will be shown in the published article.
-%% This feature is meant to be used prior to acceptance to make the
-%% front end of a long author article more manageable. Please do not use
-%% this functionality for manuscripts with less than 20 authors. Conversely,
-%% please do use this when the number of authors exceeds 40.
-%%
-%% Use \allauthors at the manuscript end to show the full author list.
-%% This command should only be used with \AuthorCollaborationLimit is used.
-
-%% The following command can be used to set the latex table counters.  It
-%% is needed in this document because it uses a mix of latex tabular and
-%% AASTeX deluxetables.  In general it should not be needed.
-%\setcounter{table}{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% The following section outlines numerous optional output that
-%% can be displayed in the front matter or as running meta-data.
-%%
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-\shorttitle{EinsteinPy: Python for General Relativity}
-\shortauthors{The EinsteinPy Community}
-%%
-%% You can add a light gray and diagonal water-mark to the first page 
-%% with this command:
-%% \watermark{text}
-%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
-%% long you can control the water-mark size with:
-%% \setwatermarkfontsize{dimension}
-%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{{./}{figures/}}
-%% This is the end of the preamble.  Indicate the beginning of the
-%% manuscript itself with \begin{document}.
-
-\begin{document}
-
-\title{EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}}
-
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.3 you can include a footnote in the title.
-
-%% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affiliations. The change was necessary to implement 
-%% auto-indexing of affiliations which prior was a manual process that could 
-%% easily be tedious in large author manuscripts.
-%%
-%% The \author command is the same as before except it now takes an optional
-%% argument which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
-%% present or in the LaTeX pathway, the OrcID icon will appear next to
-%% the authors name.
-%%
-%% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.3 will automatically index these in the header.
-%% When a duplicate is found its index will be the same as its previous entry.
-%%
-%% Note that \altaffilmark and \altaffiltext have been removed and thus 
-%% can not be used to document secondary affiliations. If they are used latex
-%% will issue a specific error message and quit. Please use multiple 
-%% \affiliation calls for to document more than one affiliation.
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.3 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
-\input{authors.tex}
-
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
-
-%% AASTeX 6.3 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
-
-%% Mark off the abstract in the ``abstract'' environment. 
 \begin{abstract}
-
 This paper presents EinsteinPy (version 0.3), a community-developed Python
@@
 EinsteinPy provides such students to really see through the equations and visualize whats really happening.
-
 \end{abstract}
-
-%% Keywords should appear after the \end{abstract} command. 
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{gravitational physics, astrophysics --- 
-simulations --- black holes --- gravitational waves}
-
-%% From the front matter, we move on to the body of the paper.
-%% Sections are demarcated by \section and \subsection, respectively.
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-%%
-%% We recommend that authors also use the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below.
-
-\section{Introduction} \label{sec:intro}
-The relativistic theory of gravity paved its way to the ground in 1915?, when Prof.
-Albert Einstein published his paper on the general theory of relativity.
-This elegant and rigorous framework was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905.
-Almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein field equations remain extremely difficult to find beyond those which exhibit significant symmetries.\\
-We can study the behavior of solutions under a high degree of symmetry considerations and could even solve analytically for highly unrealistic systems.
-In case of problems relevant to astrophysical and gravitational physics research, it still remains a big daunting question on how to get around the problem of solving these field equations.
-This question is so profound that it has a separate profound field of research which goes with the name of numerical relativity which attempts to use computation science and programming to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics are happening (as we can not solve for an infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
-Numerical methods have been used to solve the Einstein equation for many decades, but the past decade has seen tremendous advances and adding to that, the interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining.
-The field of numerical relativity is growing rampantly with the vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones) with the development of robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.\\
-Reflecting the other end of the research community stands the major section of theoretical physicists which counts the majority as a novice in programming.
-The head challenge is the fact that the usage of these frameworks demands heavy use of high-level programming languages like C, C++, Python, etc.
-Though Python provides a vast room for abstractions no library existed that focused towards numerical relativity, eventually, the need of python library dedicated to general relativity became the propellant for the team and thus they made dauntless efforts to cover the space for this Python library.
-Since then, EinsteinPy has seen a lot of contributions from people all over the world and many ”good to go” functionalities are already provided in this and previous versions.\\
-EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein’s field equations an easy job for anyone who does not want to deal with intricacies of the subject along with few, very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity with every minute detail.
-The library is as an attempt to provide programming and numerical environment for numerous numerical relativity problems like geodesics plotter, gravitational lensing and ray tracing, solving and simulating relativistic hydrodynamical equations, plotting of black hole event horizons, solving Einstein’s field equations and simulating various dynamical systems like binary merger etc.\\
-EinsteinPy provides an open-source and open-development core package and aims to build an ecosystem of affiliated packages that support numeric relativity functionality in the Python programming language.
-”Open development” describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes or other code changes, governance, or any other aspect of the development process is discussed.
-EinsteinPy core package is now a feature-rich library of sufficiently general tools and classes that support the development of more specialized code\\
-In the further coming section, we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.Also, we describe a few code snippets to explain the usage of the library on which more details can be found on the organization website.
-The development of the EinsteinPy core package began as a community-driven effort to standardize core functionality for software in Python which renders a user-friendly interface for supporting numerical relativity and relativistic astrophysics research.\\
-We start this paper by describing the way EinsteinPy functions followed by the main software efforts developed by the EinsteinPy itself with proper detailed documentation of the current version release.
-We end with a short vision for the future of EinsteinPy to its contribution in the field of computational methodology in gravitational and relativistic Astrophysics.
-
-\section{Data Types} \label{sec:datatypes}
-
-The EinsteinPy package provides some core data types for calculating, operating on, visualizing geodesics and black holes.
-There are some data types created for symbolic manipulations and calculations of relativistic tensors.
-The most important data types for EinsteinPy are \texttt{Body}, \texttt{Geodesic} and \texttt{BaseRelativityTensor} objects that support defining and creating new bodies, storing and calculating geodesic for bodies, and handling respectively.
-The main purpose of these core classes is to standardize the way calculations and visualizations are done for various kinds of heavy cosmic bodies and black holes.
-The classes always maintain the consistency in units of measurement wherever applicable, and create a consistent and clean API for any non-programmer to understand.
-The classes are designed such that it resembles the flow of physics and are  as intuitional as possible.
-These core classes also include a rigid architecture for data manipulation and visualizations wherever applicable.
-Following sections provide deep insight into the above mentioned three code data types of EinsteinPy:
-
-\subsection{Body} \label{subsec:Body}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
-
-\begin{itemize}
-\item \texttt{name}: Body Name,
-\item \texttt{mass}: Mass of the body with attached astropy units 
-\item \texttt{R}: Radius of the body with attached astropy units
-\item \texttt{differential}: Complete position and velocity vector of the body in form of a Cartesian / Spherical / BoyerLindquist data class object from einsteinpy coordinates (optional)
-\item \texttt{a}: Spin factor (a) of the body for Kerr Solutions with attached astropy units (optional)
-\item \texttt{q}: Charge of the body with attached astropy units (optional)
-\item \texttt{is\_attractor}: A boolean variable concerned with if the body is to be supposed as a central attractor. (optional)
-\item \texttt{parent}: Parent body for the body, object of the same data class (optional)
-\end{itemize}
-
-\subsection{Geodesic} \label{subsec:Geodesic}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
-
-\subsection{BaseRelativityTensor} \label{subsec:BaseRelativityTensor}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
-\begin{itemize}
-\item \texttt{order} (Property) : Returns the order of the tensor. 
-\item \texttt{config} (Property) : Returns the arrangement of contravariant(upper)/covariant(lower) indices of the tensor. For example, 'ulll'.
-\item \texttt{parent\_metric} (Property) : Returns the metric tensor of the space-time associated with the tensor, if present. Else returns \texttt{None}.
-\item \texttt{tensor} (Function) : Returns the tensorial quantity contained within the class instance.
-\item \texttt{subs} (Function) : Returns a new tensor upon substitution of current variables with new variables/values.
-\item \texttt{simplify} (Function) : Returns a tensor contain simplified expressions from the current tensor.
-\item \texttt{symbols} (Function) : Returns the symbols denoting each axis of the space-time.
-\item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
-\end{itemize}
-
-\section{UNIT HANDLING} \label{sec:unithandle}
-All user-facing functionality provided by einsteinpy make use of astropy.units. 
-All functions and objects must have their input constrained to the appropriate type of unit (e.g., length, mass or energy).
-Inputs can then be provided with any units that match the required type (e.g., millimeters and inches are both valid units for length) and conversions occur automatically without user intervention.
-The einsteinpy.constant subpackage contains a few standard constants.
-
-\section{Development Model} \label{sec:devmodels}
-The EinsteinPy Project follows an open development model, which is widely used in the scientific Python community and other computational astrophysics packages.
-The project is hosted on GitHub as a public repository with restricted write access to some key people.
-Anyone, however is welcome and encouraged to make code contributions and suggest changes using pull requests.
-Since the repository containing the codebase is licenced under an open and permissive MIT licence,  the project allows commercial use, modification, sublicensing, distribution and private use as long as the copyright notice and licence is redistributed.
-The project uses git for distributed version control and relies on CircleCI, Codefactor, GitHub Actions etc.
-for running the unit tests and other CI checks for every pull request.
-The code quality is maintained at the highest standards with strong control on the cyclomatic complexity, code linting, imports ordering and a proper docstring wherever necessary.
-Every contribution is reviewed and it must meet the following requirements:
-
-\begin{itemize}
-\item \texttt The code must strictly adhere to the PEP8 Standards, on the top of it, the code must be linted with black to save the reviewer’s time identifying the changes made and reduce the diff generated because of the patch.
-\item \texttt The imports in the code must be sorted using tools such as isort. 
-\item \texttt The documentation follows numpy like docstrings, and a proper reStructured Text syntax is followed for writing the documentation.
-\item \texttt The changelog is populated at release-time by the lead developer and the releasing developer
-\end{itemize}
-EinsteinPy further follows a trunk-based development model, which ensures a new branch for every minor release and new patch release made using the minor release branch.
-All the latest changes are kept on the master branch on GitHub and the relevant issues are closed as soon as the pull request solving it merges onto the master.
-A release having the changes is made at a later date.
-EinsteinPy only supports the latest bleeding-edge Python, Numpy and Astropy versions.
-All the stable Python versions after Python 3.5 are supported.
-All the code snippets written follow the guidelines of numba in order to accelerate the Python code and make the simulations faster.
-
-\section{INFRASTRUCTURE} \label{sec:INFRASTRUCTURE}
-\subsection{ Testing} \label{subsec: Testing}
-The EinsteinPy Project maintains a very high bar in accepting changes and introducing new features.
-Every patch of code that is accepted in the codebase through any pull request has to be well tested using some unit tests unless given an exception after discussion with both the lead developers.
-Currently the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94% and we hope to improve it in the future.
-The 100% code coverage for this software at this level is not possible because of lack of accurate data to test the code against.
-We deliberately leave some parts of the codebase out of the testing loop because testing those modules is not possible with the current knowledge level and expertise.
-However, 94% code coverage is good enough when we consider other packages in scientific Python community who face the similar problem.
-
-The test suite can be run manually as well as it runs in an automated fashion on every commit as well as pull request to maintain the code standards, and make it easier for contributors to understand the implications and impact of their changes.
-The EinsteinPy Project uses many continuous-integration services which provide services to create automated pipelines for code inspection, unit testing, coverage publishing etc.
-All the contributions trigger these free services (Codecov, CircleCI, Appveyor, GitHub Actions, Codefactor, Codeclimate, Hound, WIP) which are integrated with GitHub repository.
-All the pull requests are checked for code linting by a pep8speaks bot, which suggests the lines of code which violate the PEP8 standard to the contributor in a human readable way.
-All these services run on three types of operating systems (Windows, MacOS and Linux).
-The unit tests run on various versions of Python.
-They test the documentation builds, test coverage, check whether the pull request author has indicated that it is a work in progress (WIP).They also run several code linting checks which further triggers the unit test build.
-
-\subsection{ Documentation and gallery} \label{subsec:  Documentation and gallery}
-
-\section{COMMUNITY} \label{sec:COMMUNITY}
-EinsteinPy is being developed as an open source community inside the wide and diverse general scientific python community.
-Our code is freely available, and we have seen a lot of people contributing and joining us since over the past year.
-We touched the landmark of 30 members recently.
-EinsteinPy is dedicated to problems arising in General Relativity and gravitational physics as well as encouraging open source development.
-EinsteinPy has benefited greatly from summer of code schemes.
-Last year EinsteinPy participated in the ESA Summer of Code In Space (SOCIS).
-This program is inspired by Google Summer Of Code (GSOC) and aims to raise the awareness of open source projects related to space, promote the European Space Agency.
-The symbolic module in EinsteinPy project was developed during this program.
-
-\section{FUTURE} \label{sec:FUTURE}
-We intend to add more functionalities to our project, some of which are, 
-\begin{itemize}
-\item \texttt Support for null-geodesics in different geometries, . 
-\item \texttt Relativistic hydrodynamics
-\item \texttt Adaptive Mesh Refinement 
-\item \texttt Providing numerical solutions to Einstein’s equations for arbitrarily complex matter distribution.
-\end{itemize}
-
-We have an open community where suggestions from people to add functionalities are welcome. We wish to be as helpful as possible to people using EinsteinPy in.
-
-\acknowledgments
-
-We thank all the people that have made this AASTeX what it is today.  This
-includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
-Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
-Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
-for the new "modern" style design. Considerable help was provided via bug
-reports and hacks from numerous people including Patricio Cubillos, Alex
-Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
-Gagne.
-
-%% To help institutions obtain information on the effectiveness of their 
-%% telescopes the AAS Journals has created a group of keywords for telescope 
-%% facilities.
-%
-%% Following the acknowledgments section, use the following syntax and the
-%% \facility{} or \facilities{} macros to list the keywords of facilities used 
-%% in the research for the paper.  Each keyword is check against the master 
-%% list during copy editing.  Individual instruments can be provided in 
-%% parentheses, after the keyword, but they are not verified.
-
-\vspace{5mm}
-\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
-CTIO:1.5m,CXO}
-
-%% Similar to \facility{}, there is the optional \software command to allow 
-%% authors a place to specify which programs were used during the creation of 
-%% the manuscript. Authors should list each code and include either a
-%% citation or url to the code inside ()s when available.
-
-\software{astropy \citep{2013A&A...558A..33A},  
-          Cloudy \citep{2013RMxAA..49..137F}, 
-          SExtractor \citep{1996A&AS..117..393B}
-          }
-
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc. The
-%% Figure and Table counter will not reset.
-
-\appendix
-
-\section{Appendix information}
-
-Appendices can be broken into separate sections just like in the main text.
-The only difference is that each appendix section is indexed by a letter
-(A, B, C, etc.) instead of a number.  Likewise numbered equations have
-the section letter appended.  Here is an equation as an example.
-
-\begin{equation}
-I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-\end{equation}
-
-Appendix tables and figures should not be numbered like equations. Instead
-they should continue the sequence from the main article body.
-
-%% For this sample we use BibTeX plus aasjournals.bst to generate the
-%% the bibliography. The sample63.bib file was populated from ADS. To
-%% get the citations to show in the compiled file do the following:
-%%
-%% pdflatex sample63.tex
-%% bibtext sample63
-%% pdflatex sample63.tex
-%% pdflatex sample63.tex
-
-\bibliography{sample63}{}
-\bibliographystyle{aasjournal}
-
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
-\end{document}

### 2020-01-20 paper.tex

@@
 \documentclass{aastex63}
+\usepackage{amsmath}
+\usepackage[utf8]{inputenc}
 
@@
 
+\section{The EinsteinPy Core Package}
+This section explains in detail, the modules available within EinsteinPy core pacakge, their API and the purpose they serve.
+\subsection{METRIC}
+This module captures all the geometric and causal structure of specific spacetimes, and being able to calculate trajectories in a given space-time. 
+The module derives its name from Metric Tensor, a tensorial quantity used to describe differential lengths, especially in a curved space-time. 
+However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of newtonian physics fail.
+\subsubsection{Schwarzschild Metric}
+Karl Schwarzchild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body.
+The metric equation corrosponding to a space-time centred around a body in the above described conditions is given by,
+
+\begin{align}
+& ds^2 = -d\tau ^2 = - (1 - \frac{r_s}{r})c^2 dt^2  + \frac{1}{(1 - \frac{r_s}{r})}dr^2 + r^2 d\theta ^2 + r^2 sin^2 \theta d\phi ^2
+\end{align}
+
+The same equation can be written in a tensorial form as follows,
+
+\begin{gather}
+g_{\mu \nu} = \begin{bmatrix} - (1 - \frac{r_s}{r})c^2 & 0 & 0 & 0 \\ 0 & \frac{1}{(1 - \frac{r_s}{r})} & 0 & 0 \\ 0 & 0 & r^2 & 0 \\ 0 & 0 & 0 &  r^2 sin^2 \theta \end{bmatrix} \\ 
+\nonumber \\
+ds^2 = g_{\mu \nu} dx^\mu dx^\nu
+\end{gather}
+
+where $r_s$ is the schwarzschild radius of a given heavy body and is given by the equation,
+
+\begin{gather}
+r_s = \frac{2GM}{c^2}
+\end{gather}
+
+$G$, $M$, and $c$ are gravitational constant, mass of the body and speed of light in vacuum respectively.
+
+\subsubsection{Kerr Metric}
+\subsubsection{Kerr-Newman Metric}
+
+\subsection{COORDINATES}
+\subsection{SYMBOLIC}
+\subsection{HYPERSURFACE}
+\subsection{PLOTTING}
+
 \section{INFRASTRUCTURE} \label{sec:INFRASTRUCTURE}
@@
 Every patch of code that is accepted in the codebase through any pull request has to be well tested using some unit tests unless given an exception after discussion with both the lead developers.
-Currently the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94% and we hope to improve it in the future.
-The 100% code coverage for this software at this level is not possible because of lack of accurate data to test the code against.
+Currently the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94\% and we hope to improve it in the future.
+The 100\% code coverage for this software at this level is not possible because of lack of accurate data to test the code against.
 We deliberately leave some parts of the codebase out of the testing loop because testing those modules is not possible with the current knowledge level and expertise.
-However, 94% code coverage is good enough when we consider other packages in scientific Python community who face the similar problem.
+However, 94\% code coverage is good enough when we consider other packages in scientific Python community who face the similar problem.
 

### 2020-01-20 paper.tex
completed schwarzschild

@@
 \usepackage[utf8]{inputenc}
+\usepackage{listings}  % for code in latex
+\usepackage{color}
 
@@
 
-\section{The EinsteinPy Core Package}
+\section{The EinsteinPy Core Package} \label{sec:CORE}
 This section explains in detail, the modules available within EinsteinPy core pacakge, their API and the purpose they serve.
@@
 \begin{align}
-& ds^2 = -d\tau ^2 = - (1 - \frac{r_s}{r})c^2 dt^2  + \frac{1}{(1 - \frac{r_s}{r})}dr^2 + r^2 d\theta ^2 + r^2 sin^2 \theta d\phi ^2
+& ds^2 = -c^2 d\tau ^2 = - (1 - \frac{r_s}{r})c^2 dt^2  + \frac{1}{(1 - \frac{r_s}{r})}dr^2 + r^2 d\theta ^2 + r^2 sin^2 \theta d\phi ^2
 \end{align}
@@
 $G$, $M$, and $c$ are gravitational constant, mass of the body and speed of light in vacuum respectively.
+
+Schwarzschild Radius is a limit below which the degree of space-time curvature causes the partcle to undergo irreversible gravitational collapse wherein the partcle would need a speed greater than speed of light ot escape singularity.
+
+As $r \to \infty$, the metric defined above starts to approximate flat Minkowski space-time, thus showing that Schwarzschild geometry is asymptotically flat.
+
+If supplied with initial position and velocity of a particle with negligible mass(in comparision to the central body), we can obtain the geodesics of the particle for a given range of proper time $\tau$, as it boils down to a set of eight differential equations numerically solvable by a class of Runge-Kutta methods.
+
+The file \textbf{schwarzschild.py} contains the class \textit{Schwarzschild} for defining Schwarzschild geometry methods.
+
+Here is a working code describing the motion of particle revolving around a black hole of mass approximately equal to mass of the Earth.
+As the trajectory starts from a mere $130m$ from the black hole, we obtain some interesting observations.
+
+\begin{lstlisting}[language=Python, caption=Importing the required modules]
+>>> import numpy as np
+>>> import astropy.units as u
+>>> from einsteinpy.plotting import GeodesicPlotter
+>>> from einsteinpy.coordinates import SphericalDifferential
+>>> from einsteinpy.bodies import Body
+>>> from einsteinpy.geodesic import Geodesic
+>>> from einsteinpy.metric import Schwarzschild
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python, caption=Defining the attractor and the particle and calculating geodesics]
+>>> Attractor = Body(name="BH", mass=6e24 * u.kg)
+>>> init_conditions = SphericalDifferential(130*u.m, np.pi/2*u.rad, -np.pi/8*u.rad,
+...                                         0*u.m/u.s, 0*u.rad/u.s, 1900*u.rad/u.s)
+>>> Particle = Body(differential=init_conditions, parent=Attractor)
+>>> geodesic = Geodesic(body=Particle, time=0 * u.s, end_lambda=0.00205, step_size=5e-8)
+>>> goedesic.trajectory
+array([[ 0.00000000e+00,  1.20104339e+02, -4.97488462e+01, ...,
+         9.45228078e+04,  2.28198245e+05,  0.00000000e+00],
+       [ 3.99986427e-08,  1.20108103e+02, -4.97397110e+01, ...,
+         9.36472607e+04,  2.28560869e+05, -5.80280784e-14],
+       ...,
+       [ 2.04962579e-03,  1.04114904e+02,  1.08255773e+01, ...,
+        -1.23245830e+06,  1.80261847e+05, -9.67931265e-09],
+       [ 2.05002578e-03,  1.03619005e+02,  1.08973776e+01, ...,
+        -1.24706334e+06,  1.78734562e+05, -9.79337222e-09]])
+>>> geodesic.trajectory.shape
+(6567, 8)
+\end{lstlisting}
+We can see that for each timestep, we obtain eight values : $t$, $r$, $\theta$, $\phi$, $v_t$, $v_r$, $v_\theta$ and $v_\phi$ corrosponding to coordinate time, radial distance from the centre, polar angle, azimuth angle and their respective velocities w.r.t proper time $\tau$.
+
+Further, we plot the trajectory in 2D for vizualization purposes.
+\begin{lstlisting}[language=Python, caption=Plotting the trajectory]
+>>> obj = GeodesicPlotter()
+>>> obj.plot(geodesic)
+>>> obj.show()
+\end{lstlisting}
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.7]{images/perihelion_cropped.png}
+	%\centerline{\includegraphics{ftcbuild2.pdf}}
+	\caption{Plot obtained from the above code showing the phenomenon of perihelion advance}
+	\label{fig:schwarzschild}
+\end{figure}
+
+We observe the phenomenon of perihelion advance of a particle around a heavy body due to spacetime curavture.
+The orbit would have been purely eliptical if plotted in accordance with Newtonian Mechanics, however, the curvature of space-time around the heavy mass shifts the orbit with each revolution.
+In practicality, this phenomenon is not so pronounced as no particle approaches a heavy mass this closely.
+For instance, Mercury advances its perihelion at a rate of $42.98\pm 0.04$ arcsec/century.
 

### 2020-01-20 paper.tex

@@
 >>> Particle = Body(differential=init_conditions, parent=Attractor)
->>> geodesic = Geodesic(body=Particle, time=0 * u.s, end_lambda=0.00205, step_size=5e-8)
->>> goedesic.trajectory
+>>> geodesic = Geodesic(body=Particle, time=0 * u.s, end_lambda=0.00205, step_size=5e-8,
+...                     metric=Schwarzschild)
+>>> geodesic.trajectory
 array([[ 0.00000000e+00,  1.20104339e+02, -4.97488462e+01, ...,
@@
 \subsubsection{Kerr Metric}
+Kerr metric is a further generalization of Schwarzschild metric and a specific case of Kerr-Newman geometry.
+A spacetime is defined as a "Kerr" spacetime as and when the massive central body posseses an angular momentum.
+The corresponding metric equation which defines the space-time is,
+
+\begin{gather}
+g_{\mu \nu} = \begin{bmatrix} - (1 - \frac{r_s r}{\Sigma})c^2 & 0 & 0 & -\frac{r_s r a sin^2 \theta}{\Sigma}c \\ 0 & \frac{\Sigma}{\Delta} & 0 & 0 \\ 0 & 0 & \Sigma & 0 \\ -\frac{r_s r a sin^2 \theta}{\Sigma}c & 0 & 0 &  (r^2 + a^2 + \frac{r_s r a^2}{\Sigma}sin^2 \theta) sin^2 \theta \end{bmatrix} \\
+\nonumber \\
+ds^2 = g_{\mu \nu} dx^\mu dx^\nu
+\end{gather}
+
+where,
+\begin{gather}
+a = \frac{J}{Mc} \\
+\Sigma = r^2 + a^2 cos^2 \theta \\
+\Delta  = r^2 - r_s r + a^2
+\end{gather}
+
+$J$ is the angular momentum of the body and all the other symbols hold their usual meanings as discussed in Schwarzschild Metric.
+The coordinate system used to describe the metric is Boyer-Lindquist coordinate system.
+
+The file \textbf{kerr.py} contains the class \textit{Kerr} for defining Schwarzschild geometry methods.
+
+APIs for \textit{Schwarzschild}, \textit{Kerr} and \textit{KerrNewman} are consistent and code structure remains same for the sake for clarity and intuitiveness. For example,
+
+\begin{lstlisting}[language=Python, caption=Defining the Kerr Body and the particle and calculating geodesics]
+>>> a = 0.3 * u.m
+>>> Attractor = Body(name="BH", mass=1.989e30 * u.kg, a=a)
+>>> init_conditions = BoyerLindquistDifferential(49.95e5 * u.km, np.pi / 2 * u.rad, 
+...                                              np.pi * u.rad, 0 * u.km / u.s, 
+...                                              0 * u.rad / u.s, 0 * u.rad / u.s,
+...                                              a)
+>>> Particle = Body(differential=init_conditions, parent=Attractor)
+>>> geodesic = Geodesic(body=Particle, time=0 * u.s, end_lambda=33932.90,
+...                     step_size=1.2, metric=Kerr)
+\end{lstlisting}
+
+As evident from the code, API across different classes are made to be as homegenous as possible.
+
+As a rotating black hole drags the space-time around it, a freely falling object acquires a angular velocity around the coordinate centre, i.e centre of the black hole.
+This effect is evident from the plot obatined from the above geodesics, in the same way as obtained one in the Schwarzschild example.
+
+\begin{figure}[h]
+	\centering
+	\includegraphics[scale=0.1]{images/blank.jpg} %replace this when the actual plot becomes available
+	%\centerline{\includegraphics{ftcbuild2.pdf}}
+	\caption{Plot obtained from the above geodesics showing the phenomenon of frame dragging}
+	\label{fig:kerr}
+\end{figure}
+
 \subsubsection{Kerr-Newman Metric}

### 2020-01-20 paper.tex
newman baba

@@
 This section explains in detail, the modules available within EinsteinPy core pacakge, their API and the purpose they serve.
-\subsection{METRIC}
+\subsection{METRIC} \label{subsec:metric}
 This module captures all the geometric and causal structure of specific spacetimes, and being able to calculate trajectories in a given space-time. 
@@
 However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of newtonian physics fail.
-\subsubsection{Schwarzschild Metric}
+\subsubsection{Schwarzschild Metric} \label{subsubsec:sch}
 Karl Schwarzchild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body.
@@
 
-\subsubsection{Kerr Metric}
+\subsubsection{Kerr Metric}\label{subsubsec:kerr}
 Kerr metric is a further generalization of Schwarzschild metric and a specific case of Kerr-Newman geometry.
@@
 \begin{gather}
-a = \frac{J}{Mc} \\
-\Sigma = r^2 + a^2 cos^2 \theta \\
-\Delta  = r^2 - r_s r + a^2
+a = \frac{J}{Mc}, \nonumber \\
+\Sigma = r^2 + a^2 cos^2, \nonumber \theta \\
+\Delta  = r^2 - r_s r + a^2 \nonumber
 \end{gather}
 
-$J$ is the angular momentum of the body and all the other symbols hold their usual meanings as discussed in Schwarzschild Metric.
+$J$ is the angular momentum of the body and all the other symbols hold their usual meanings as discussed in \ref{subsubsec:sch}.
 The coordinate system used to describe the metric is Boyer-Lindquist coordinate system.
@@
 
-\subsubsection{Kerr-Newman Metric}
+\subsubsection{Kerr-Newman Metric}\label{subsubsec:kerrnewman}
+Kerr-Newman metric presents the most general case within single-body vacuum solutions of Einstein Field Equation.
+It generalizes all the quantities used to describe a black hole, as affirmed by "no hair" theoram, i.e.
+Charge $Q$, Angular Momentum $J$ and Mass $M$.
+The metric equation is given by,
+
+\begin{gather}
+-ds^2 = c^2 d\tau^2 = -(\frac{dr^2}{\Delta}+d\theta^2)\rho^2 + (c dt - a sin^2 \theta d\phi)^2 \frac{\Delta}{\rho^2} - ((r^2 + a^2)d\phi - ac dt)^2 \frac{sin^2 \theta}{\rho^2}
+\end{gather}
+
+where,
+
+\begin{gather}
+a = \frac{J}{Mc}, \nonumber \\
+\Sigma = r^2 + a^2 cos^2 \theta , \nonumber  \\
+\Delta  = r^2 - r_s r + a^2 + r_Q ^ 2, \nonumber \\
+r_Q ^ 2 = \frac{Q^2 G}{4\pi\epsilon_0 c^4} \nonumber
+\end{gather}
+
+All the other symbols convey their usual meanings, as discussed in the previous two sections \ref{subsubsec:sch} and \ref{subsubsec:kerr}.
+For the sake of brevity, we would not go into the specifics of this class as the classes within \textit{Metric} module share very similar APIs as inferred in \ref{subsubsec:kerr}.
 

### 2020-01-21 paper.tex

@@
 \usepackage{color}
+% \usepackage{caption}
 
@@
 \subsection{BaseRelativityTensor} \label{subsec:BaseRelativityTensor}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
+This is a base class from which other tensors in \textit{symbolic} module are derived.
+The user can use this class to create his/her own tensor while using the various in-built functions provided by this class.
+The class also maintains the indicial configuration of the tensor(contravariant and covariant indices), calculates the free variables used in describing the tensor other than those which depicts the axis of space-time itself (e.g.
+$t, x, y, z$).
+The class has a function to convert the symbolic tensorial quantities into functions where actual numerical values can be substitued.
+
+This class along with its parent class \textit{Tensor} have the following functions/properties,
 \begin{itemize}
@@
 \item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
+\item \texttt{lorentz\_transform} (Function) : Returns a lorentz-transformed tensor when supplied with a transformation matrix.
+This function also considers the contravariance and covariance of tensors during transformation.
 \end{itemize}
@@
 
-\section{The EinsteinPy Core Package} \label{sec:CORE}
+\section{The EinsteinPy Core Package} \label{sec:core}
 This section explains in detail, the modules available within EinsteinPy core pacakge, their API and the purpose they serve.
@@
 \subsection{SYMBOLIC}
+General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of a arbitrary space-time.
+We would describe the various quantities currently supported by this module while maintaining brevity.
+Each quantity has its own class, even scalars, which are treated as 0\textsuperscript{th} order tensors.
+
+All the mathematical quantities build upon \textit{BaseRelativityTensor} as derived classes, which is discussed in detail in \ref{subsec:BaseRelativityTensor}.
+
+\subsubsection{MetricTensor}\label{subsubsec:metric}
+Metric Tensor describes the differential length elements required to measure distance in a curved(also applies to flat) space-time.
+It is a second order tensor and is fundamental to describe any space-time geometry.
+The \textit{MetricTensor} class, being inherited from \textit{BaseRelativityTensor} (\ref{subsec:BaseRelativityTensor}) , inherits all its functions and also have some functions and constraints of its own.
+For example, metric tensor is bound to be a second order tensor.
+
+The defined class functions are :
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\item \texttt{inv} : returns inverse of the metric
+\end{itemize}
+
+Also, the library maintains an ever expanding predefined metrics for direct use. Here's an code snippet for a better dive into the specificities of the class.
+
+\begin{lstlisting}[language=Python, caption=Importing a predefined metric]
+>>> from einsteinpy.symbolic.predefined import CMetric
+>>> metric = CMetric
+>>> metric.tensor()
+\end{lstlisting}
+
+\begin{center}
+$\displaystyle \left[\begin{matrix}- \frac{h{\left(y \right)}}{\left(x + y\right)^{2}} & 0 & 0 & 0\\0 & \frac{1}{\left(x + y\right)^{2} f{\left(x \right)}} & 0 & 0\\0 & 0 & \frac{1}{\left(x + y\right)^{2} h{\left(y \right)}} & 0\\0 & 0 & 0 & \frac{f{\left(x \right)}}{\left(x + y\right)^{2}}\end{matrix}\right]$
+\end{center}
+
+\begin{lstlisting}[language=Python, caption=Displaying the contravarint configuration of metric]
+>>> metric.change_config("uu").tensor()
+\end{lstlisting}
+
+\begin{center}
+ $\displaystyle \left[\begin{matrix}- \frac{\left(x + y\right)^{2}}{h{\left(y \right)}} & 0 & 0 & 0\\0 & \left(x + y\right)^{2} f{\left(x \right)} & 0 & 0\\0 & 0 & \left(x + y\right)^{2} h{\left(y \right)} & 0\\0 & 0 & 0 & \frac{\left(x + y\right)^{2}}{f{\left(x \right)}}\end{matrix}\right]$ \\
+\end{center}
+
+\subsubsection{ChristoffelSymbols}\label{subsubsec:chl}
+\subsubsection{RiemannCurvatureTensor}\label{subsubsec:riemann}
+\subsubsection{RicciTensor}\label{subsubsec:riccitensor}
+\subsubsection{RicciScalar}\label{subsubsec:ricciscalar}
+\subsubsection{Other Defined Quantities}\label{subsubsec:other}
+
 \subsection{HYPERSURFACE}
@@
 
-\section{INFRASTRUCTURE} \label{sec:INFRASTRUCTURE}
-\subsection{ Testing} \label{subsec: Testing}
+\section{INFRASTRUCTURE} \label{sec:infra}
+\subsection{ Testing} \label{subsec:testing}
 The EinsteinPy Project maintains a very high bar in accepting changes and introducing new features.
@@
 
-\subsection{ Documentation and gallery} \label{subsec:  Documentation and gallery}
+\subsection{ Documentation and gallery} \label{subsec:doc}
 

### 2020-01-22 paper.tex
complete symbolic, kind of!

@@
 \usepackage{color}
+\usepackage{hyperref}
 % \usepackage{caption}
@@
 \subsection{SYMBOLIC}
-General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of a arbitrary space-time.
+General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of an arbitrary space-time.
 We would describe the various quantities currently supported by this module while maintaining brevity.
@@
 
-All the mathematical quantities build upon \textit{BaseRelativityTensor} as derived classes, which is discussed in detail in \ref{subsec:BaseRelativityTensor}.
+All the mathematical quantities build upon \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} as derived classes, which is discussed in detail in \ref{subsec:BaseRelativityTensor}.
 
@@
 It is a second order tensor and is fundamental to describe any space-time geometry.
-The \textit{MetricTensor} class, being inherited from \textit{BaseRelativityTensor} (\ref{subsec:BaseRelativityTensor}) , inherits all its functions and also have some functions and constraints of its own.
+The \textit{MetricTensor} class, being inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} , inherits all its functions and also have some functions and constraints of its own.
 For example, metric tensor is bound to be a second order tensor.
@@
 \subsubsection{ChristoffelSymbols}\label{subsubsec:chl}
+
+Although Christoffel Symbols are belong to class of pseudo-tensors, it is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} to maintain homogenity within the module.
+Being inherited from  \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}}, it already supports the functions of its parent class and imposes some restrictions of its own, such as order of the tensor should be 3.
+
+Instance of the class can be made by directly passing a 3\textsuperscript{rd} order tensor or can be obtained using the following classmethods,
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates christoffel symbols from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+\end{itemize}
+
+The defined class function(s) are : 
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\end{itemize}
+
 \subsubsection{RiemannCurvatureTensor}\label{subsubsec:riemann}
+
+This quantity is the most extensive measure of curvature of a sapce-time.
+It is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} and supports all the functions of its parent class.
+
+Instance of the class can be made by directly passing a 4\textsuperscript{th} order tensor or can be obtained using the following classmethods
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates Riemann Tensor from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+\item \texttt{from\_christoffels} : Calculates Riemann Tensor from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
+\end{itemize}
+
+The defined class function(s) are : 
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\end{itemize}
+
 \subsubsection{RicciTensor}\label{subsubsec:riccitensor}
+
+This tensor is used in solving Eintein's  equation and basically contraction of Riemann Curvature Tensor.
+It is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} and supports all the functions of its parent class.
+
+Instance of the class can be made by directly passing a 2\textsuperscript{nd} order tensor or can be obtained using the following classmethods
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+\item \texttt{from\_christoffels} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
+\item \texttt{from\_riemann} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}} class.
+\end{itemize}
+
+The defined class function(s) are : 
+\begin{itemize}
+\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+\end{itemize}
+
 \subsubsection{RicciScalar}\label{subsubsec:ricciscalar}
+
+It is a scalar quantity obtained by contracting a given Ricci Tensor.
+It is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} and supports all the functions of its parent class.
+Being a scalar quantity, it does not support \texttt{change\_config} unlike other tensors as discussed above.
+
+Instance of the class can be made by directly passing a symbolic expression or can be obtained using the following classmethods
+\begin{itemize}
+\item \texttt{from\_metric} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+\item \texttt{from\_christoffels} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
+\item \texttt{from\_riemann} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}} class.
+\item \texttt{from\_riccitensor} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:riccitensor]{\textit{RicciTensor}} class.
+\end{itemize}
+
+The defined class properties are : 
+\begin{itemize}
+\item \texttt{expr} : returns the scalar symbolic expression contained in the class. 
+\end{itemize}
+
+Here is a sample code snippet, using the above discussed Classes
+
+\begin{lstlisting}[language=Python, caption=Importing Anti De-Sitter metric]
+>>> from einsteinpy.symbolic.predefined import AntiDeSitter
+>>> from einsteinpy.symbolic import RicciTensor, RicciScalar
+>>> import sympy
+\end{lstlisting}
+
+\begin{lstlisting}[language=Python, caption=Obtaining Ricci Tensor from the metric]
+>>> RT = RicciTensor.from_metric(AntiDeSitter())
+>>> RT.tensor()
+\end{lstlisting}
+
+\begin{center}
+$\displaystyle \left[\begin{matrix}3 & 0 & 0 & 0\\0 & - 3 \cos^{2}{\left(t \right)} & 0 & 0\\0 & 0 & \left(\sin^{2}{\left(t \right)} - 1\right) \sinh^{2}{\left(\chi \right)} - 2 \cos^{2}{\left(t \right)} \sinh^{2}{\left(\chi \right)} & 0\\0 & 0 & 0 & \left(\sin^{2}{\left(t \right)} - 1\right) \sin^{2}{\left(\theta \right)} \sinh^{2}{\left(\chi \right)} - 2 \sin^{2}{\left(\theta \right)} \cos^{2}{\left(t \right)} \sinh^{2}{\left(\chi \right)}\end{matrix}\right]$
+\end{center}
+
+\begin{lstlisting}[language=Python, caption=Deriving Ricci(Curvature) Scalar from Ricci Tensor]
+>>> RS = RicciScalar.from_riccitensor(RT)
+>>> sympy.simplify(RS.expr)  # simplifying the expression
+\end{lstlisting}
+
+\begin{center}
+$\displaystyle -12$
+\end{center}
+
+In congruence to theoretical results, the code outputs a constant negetive scalar curvature for Anti De-Sitter spacetime.
+All the above discussed classes are called in this snippet as \hyperref[subsubsec:riccitensor]{\textit{RicciTensor}} internally calls \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}}, which in turn calls \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}}.
+
 \subsubsection{Other Defined Quantities}\label{subsubsec:other}
+
+As the library is in heavy development, new quantities are being added as and when required.
+Some other quantities currently supported are listed below.
+The quantities are all inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}}, and a similar API (same as that of discussed above) has been implemented to maintain compatiblity and homegenity.
+The class names denote usual quantities relevant to General Relativity.
+
+\begin{itemize}
+\item \textit{EinsteinTensor}
+\item \textit{StressEnergyMomentumTensor}
+\item \textit{WeylTensor}
+\item \textit{SchoutenTensor}
+\end{itemize}
 

### 2020-01-24 authors.tex
Fix things

@@
 
-% \author[0000-0000-0000-0000]{The EinsteinPy Community}
+% \author[0000-0000-0000-0000]{The SunPy Community}
 % \noaffiliation
@@
 
-\author{Ritwik Saha}
+\author[0000-0002-2369-0628]{Ritwik Saha}
 \altaffiliation{EinsteinPy Lead Developer, EinsteinPy Board Member}
@@
 
-\author{Bhavya Bhatt}
+\author[0000-0002-2784-5666]{Bhavya Bhatt}
 \altaffiliation{EinsteinPy Deputy Lead Developer}
@@
 
-% Below add contributors to the EinsteinPy project
+% Below add contributors to the Sunpy project
+% this list is ordered alphabetically
 
 \author[0000-0003-1021-3336]{Priyanshu Khandelwal}
+\altaffiliation{EinsteinPy Board Member}
+\affiliation{\sceeiitmandi}
+
+\author[0000-0002-1928-1549]{Rishi Sharma}
 \altaffiliation{EinsteinPy Board Member}
@@
 
+\author[0000-0003-4387-8078]{Divya Gupta}
+\affiliation{\sceeiitmandi}
+
+\author{Hrishikesh Sudam Sarode}
+\affiliation{\sceeiitmandi}
+
 \author[0000-0003-1838-8368]{Tanmay Rustagi}
@@
 \author[0000-0001-5558-9447]{Raphael Reyna}
-\affiliation{California State Polytechnic University, Pomona}
+\affiliation{California State Polytechnic University, Pomona, USA}
+
+\author[0000-0002-6696-8730]{Govind Dixit}
+\affiliation{Information Technology, Indian Institute of Information Technology Lucknow, India}
+
+\author{Ratin Kumar}
+\affiliation{National Institute of Technology Kurukshetra, India}
 
 \author[0000-0001-8302-1584]{Sashank Mishra}
-\affiliation{Department of Information Technology, Indian Institute of Information Technology Allahabad}
+\affiliation{Department of Information Technology, Indian Institute of Information Technology Allahabad, India}
+
+\author[0000-0003-0973-4994]{Pratyush Kerhalkar}
+\affiliation{Department of Electronics & Communication Engineering, Manipal Institute of Technology, India}
 

### 2020-01-24 paper.tex
Fix things

@@
 
-\title{EinsteinPy: Python for General Relativity\footnote{Released on July, 15th, 2019}}
+\title{EinsteinPy: Python for General Relativity}
 
@@
 \subsection{Body} \label{subsec:Body}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
+The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. 
+% A new body can be defined by some of the very basic constraints:
 
-\begin{itemize}
-\item \texttt{name}: Body Name,
-\item \texttt{mass}: Mass of the body with attached astropy units 
-\item \texttt{R}: Radius of the body with attached astropy units
-\item \texttt{differential}: Complete position and velocity vector of the body in form of a Cartesian / Spherical / BoyerLindquist data class object from einsteinpy coordinates (optional)
-\item \texttt{a}: Spin factor (a) of the body for Kerr Solutions with attached astropy units (optional)
-\item \texttt{q}: Charge of the body with attached astropy units (optional)
-\item \texttt{is\_attractor}: A boolean variable concerned with if the body is to be supposed as a central attractor. (optional)
-\item \texttt{parent}: Parent body for the body, object of the same data class (optional)
-\end{itemize}
+% \begin{itemize}
+% \item \texttt{name}: Body Name,
+% \item \texttt{mass}: Mass of the body with attached astropy units 
+% \item \texttt{R}: Radius of the body with attached astropy units
+% \item \texttt{differential}: Complete position and velocity vector of the body in form of a Cartesian / Spherical / BoyerLindquist data class object from einsteinpy coordinates (optional)
+% \item \texttt{a}: Spin factor (a) of the body for Kerr Solutions with attached astropy units (optional)
+% \item \texttt{q}: Charge of the body with attached astropy units (optional)
+% \item \texttt{is\_attractor}: A boolean variable concerned with if the body is to be supposed as a central attractor. (optional)
+% \item \texttt{parent}: Parent body for the body, object of the same data class (optional)
+% \end{itemize}
 
 \subsection{Geodesic} \label{subsec:Geodesic}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. A new body can be defined by some of the very basic constraints:
+The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. 
+% A new body can be defined by some of the very basic constraints:
 
@@
 
-This class along with its parent class \textit{Tensor} have the following functions/properties,
-\begin{itemize}
-\item \texttt{order} (Property) : Returns the order of the tensor. 
-\item \texttt{config} (Property) : Returns the arrangement of contravariant(upper)/covariant(lower) indices of the tensor. For example, 'ulll'.
-\item \texttt{parent\_metric} (Property) : Returns the metric tensor of the space-time associated with the tensor, if present. Else returns \texttt{None}.
-\item \texttt{tensor} (Function) : Returns the tensorial quantity contained within the class instance.
-\item \texttt{subs} (Function) : Returns a new tensor upon substitution of current variables with new variables/values.
-\item \texttt{simplify} (Function) : Returns a tensor contain simplified expressions from the current tensor.
-\item \texttt{symbols} (Function) : Returns the symbols denoting each axis of the space-time.
-\item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
-\item \texttt{lorentz\_transform} (Function) : Returns a lorentz-transformed tensor when supplied with a transformation matrix.
+% This class along with its parent class \textit{Tensor} have the following functions/properties,
+% \begin{itemize}
+% \item \texttt{order} (Property) : Returns the order of the tensor. 
+% \item \texttt{config} (Property) : Returns the arrangement of contravariant(upper)/covariant(lower) indices of the tensor. For example, 'ulll'.
+% \item \texttt{parent\_metric} (Property) : Returns the metric tensor of the space-time associated with the tensor, if present. Else returns \texttt{None}.
+% \item \texttt{tensor} (Function) : Returns the tensorial quantity contained within the class instance.
+% \item \texttt{subs} (Function) : Returns a new tensor upon substitution of current variables with new variables/values.
+% \item \texttt{simplify} (Function) : Returns a tensor contain simplified expressions from the current tensor.
+% \item \texttt{symbols} (Function) : Returns the symbols denoting each axis of the space-time.
+% \item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
+% \item \texttt{lorentz\_transform} (Function) : Returns a lorentz-transformed tensor when supplied with a transformation matrix.
 This function also considers the contravariance and covariance of tensors during transformation.
-\end{itemize}
+% \end{itemize}
 
@@
 
-The same equation can be written in a tensorial form as follows,
+%The same equation can be written in a tensorial form as follows,
 
-\begin{gather}
-g_{\mu \nu} = \begin{bmatrix} - (1 - \frac{r_s}{r})c^2 & 0 & 0 & 0 \\ 0 & \frac{1}{(1 - \frac{r_s}{r})} & 0 & 0 \\ 0 & 0 & r^2 & 0 \\ 0 & 0 & 0 &  r^2 sin^2 \theta \end{bmatrix} \\ 
-\nonumber \\
-ds^2 = g_{\mu \nu} dx^\mu dx^\nu
-\end{gather}
+%\begin{gather}
+%g_{\mu \nu} = \begin{bmatrix} - (1 - \frac{r_s}{r})c^2 & 0 & 0 & 0 \\ 0 & \frac{1}{(1 - \frac{r_s}{r})} & 0 & 0 \\ 0 & 0 & r^2 & 0 \\ 0 & 0 & 0 &  r^2 sin^2 \theta \end{bmatrix} \\ 
+%\nonumber \\
+%ds^2 = g_{\mu \nu} dx^\mu dx^\nu
+%\end{gather}
 
-where $r_s$ is the schwarzschild radius of a given heavy body and is given by the equation,
+%where $r_s$ is the schwarzschild radius of a given heavy body and is given by the equation,
 
-\begin{gather}
-r_s = \frac{2GM}{c^2}
-\end{gather}
+%\begin{gather}
+%r_s = \frac{2GM}{c^2}
+%\end{gather}
 
-$G$, $M$, and $c$ are gravitational constant, mass of the body and speed of light in vacuum respectively.
+%$G$, $M$, and $c$ are gravitational constant, mass of the body and speed of light in vacuum respectively.
 
-Schwarzschild Radius is a limit below which the degree of space-time curvature causes the partcle to undergo irreversible gravitational collapse wherein the partcle would need a speed greater than speed of light ot escape singularity.
+Schwarzschild Radius is a limit below which the degree of space-time curvature causes the particle to undergo irreversible gravitational collapse wherein the particle would need a speed greater than speed of light ot escape singularity.
 
@@
 
-The file \textbf{schwarzschild.py} contains the class \textit{Schwarzschild} for defining Schwarzschild geometry methods.
-
-Here is a working code describing the motion of particle revolving around a black hole of mass approximately equal to mass of the Earth.
+%Here is a working code describing the motion of particle revolving around a black hole of mass approximately equal to mass of the Earth.
 As the trajectory starts from a mere $130m$ from the black hole, we obtain some interesting observations.
 
-\begin{lstlisting}[language=Python, caption=Importing the required modules]
->>> import numpy as np
->>> import astropy.units as u
->>> from einsteinpy.plotting import GeodesicPlotter
->>> from einsteinpy.coordinates import SphericalDifferential
->>> from einsteinpy.bodies import Body
->>> from einsteinpy.geodesic import Geodesic
->>> from einsteinpy.metric import Schwarzschild
-\end{lstlisting}
+% \begin{lstlisting}[language=Python, caption=Importing the required modules]
+% >>> import numpy as np
+% >>> import astropy.units as u
+% >>> from einsteinpy.plotting import GeodesicPlotter
+% >>> from einsteinpy.coordinates import SphericalDifferential
+% >>> from einsteinpy.bodies import Body
+% >>> from einsteinpy.geodesic import Geodesic
+% \end{lstlisting}
 
-\begin{lstlisting}[language=Python, caption=Defining the attractor and the particle and calculating geodesics]
->>> Attractor = Body(name="BH", mass=6e24 * u.kg)
->>> init_conditions = SphericalDifferential(130*u.m, np.pi/2*u.rad, -np.pi/8*u.rad,
-...                                         0*u.m/u.s, 0*u.rad/u.s, 1900*u.rad/u.s)
->>> Particle = Body(differential=init_conditions, parent=Attractor)
->>> geodesic = Geodesic(body=Particle, time=0 * u.s, end_lambda=0.00205, step_size=5e-8,
-...                     metric=Schwarzschild)
->>> geodesic.trajectory
-array([[ 0.00000000e+00,  1.20104339e+02, -4.97488462e+01, ...,
-         9.45228078e+04,  2.28198245e+05,  0.00000000e+00],
-       [ 3.99986427e-08,  1.20108103e+02, -4.97397110e+01, ...,
-         9.36472607e+04,  2.28560869e+05, -5.80280784e-14],
-       ...,
-       [ 2.04962579e-03,  1.04114904e+02,  1.08255773e+01, ...,
-        -1.23245830e+06,  1.80261847e+05, -9.67931265e-09],
-       [ 2.05002578e-03,  1.03619005e+02,  1.08973776e+01, ...,
-        -1.24706334e+06,  1.78734562e+05, -9.79337222e-09]])
->>> geodesic.trajectory.shape
-(6567, 8)
-\end{lstlisting}
-We can see that for each timestep, we obtain eight values : $t$, $r$, $\theta$, $\phi$, $v_t$, $v_r$, $v_\theta$ and $v_\phi$ corrosponding to coordinate time, radial distance from the centre, polar angle, azimuth angle and their respective velocities w.r.t proper time $\tau$.
+% \begin{lstlisting}[language=Python, caption=Defining the attractor and the particle and calculating geodesics]
+% >>> Attractor = Body(name="BH", mass=6e24 * u.kg)
+% >>> init_conditions = SphericalDifferential(130*u.m, np.pi/2*u.rad, -np.pi/8*u.rad,
+% ...                                         0*u.m/u.s, 0*u.rad/u.s, 1900*u.rad/u.s)
+% >>> Particle = Body(differential=init_conditions, parent=Attractor)
+% >>> geodesic = Geodesic(body=Particle, end_lambda=0.00205, step_size=5e-8)
 
-Further, we plot the trajectory in 2D for vizualization purposes.
-\begin{lstlisting}[language=Python, caption=Plotting the trajectory]
->>> obj = GeodesicPlotter()
->>> obj.plot(geodesic)
->>> obj.show()
-\end{lstlisting}
+% \end{lstlisting}
+% We can see that for each timestep, we obtain eight values : $t$, $r$, $\theta$, $\phi$, $v_t$, $v_r$, $v_\theta$ and $v_\phi$ corrosponding to coordinate time, radial distance from the centre, polar angle, azimuth angle and their respective velocities w.r.t proper time $\tau$.
 
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.7]{images/perihelion_cropped.png}
-	%\centerline{\includegraphics{ftcbuild2.pdf}}
-	\caption{Plot obtained from the above code showing the phenomenon of perihelion advance}
-	\label{fig:schwarzschild}
-\end{figure}
+% Further, we plot the trajectory in 2D for vizualization purposes.
+% \begin{lstlisting}[language=Python, caption=Plotting the trajectory]
+% >>> obj = GeodesicPlotter()
+% >>> obj.plot(geodesic)
+% >>> obj.show()
+% \end{lstlisting}
 
-We observe the phenomenon of perihelion advance of a particle around a heavy body due to spacetime curavture.
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[scale=0.7]{figures/perihelion_cropped.png}
+% 	%\centerline{\includegraphics{ftcbuild2.pdf}}
+% 	\caption{Plot obtained from the above code showing the phenomenon of perihelion advance}
+% 	\label{fig:schwarzschild}
+% \end{figure}
+
+% We observe the phenomenon of perihelion advance of a particle around a heavy body due to spacetime curavture.
 The orbit would have been purely eliptical if plotted in accordance with Newtonian Mechanics, however, the curvature of space-time around the heavy mass shifts the orbit with each revolution.
@@
 
-The file \textbf{kerr.py} contains the class \textit{Kerr} for defining Schwarzschild geometry methods.
-
 APIs for \textit{Schwarzschild}, \textit{Kerr} and \textit{KerrNewman} are consistent and code structure remains same for the sake for clarity and intuitiveness. For example,
 
-\begin{lstlisting}[language=Python, caption=Defining the Kerr Body and the particle and calculating geodesics]
->>> a = 0.3 * u.m
->>> Attractor = Body(name="BH", mass=1.989e30 * u.kg, a=a)
->>> init_conditions = BoyerLindquistDifferential(49.95e5 * u.km, np.pi / 2 * u.rad, 
-...                                              np.pi * u.rad, 0 * u.km / u.s, 
-...                                              0 * u.rad / u.s, 0 * u.rad / u.s,
-...                                              a)
->>> Particle = Body(differential=init_conditions, parent=Attractor)
->>> geodesic = Geodesic(body=Particle, time=0 * u.s, end_lambda=33932.90,
-...                     step_size=1.2, metric=Kerr)
-\end{lstlisting}
+% \begin{lstlisting}[language=Python, caption=Defining the Kerr Body and the particle and calculating geodesics]
+% >>> a = 0.3 * u.m
+% >>> attractor = Body(name="BH", mass=1.989e30 * u.kg, a=a)
+% >>> coordinates = BoyerLindquistDifferential(49.95e5 * u.km, np.pi / 2 * u.rad, np.pi * u.rad, a=a)
+% >>> particle = Body(differential=init_conditions, parent=attractor)
+% >>> geodesic = Geodesic(body=particle, end_lambda=33932.90, step_size=1.2, metric=Kerr)
+% \end{lstlisting}
+% As evident from the code, API across different classes are made to be as homogeneous as possible.
 
-As evident from the code, API across different classes are made to be as homegenous as possible.
+% As a rotating black hole drags the space-time around it, a freely falling object acquires a angular velocity around the coordinate centre, i.e centre of the black hole.
+This effect is evident from the plot obtained from the above geodesics, in the same way as obtained one in the Schwarzschild example.
 
-As a rotating black hole drags the space-time around it, a freely falling object acquires a angular velocity around the coordinate centre, i.e centre of the black hole.
-This effect is evident from the plot obatined from the above geodesics, in the same way as obtained one in the Schwarzschild example.
-
-\begin{figure}[h]
-	\centering
-	\includegraphics[scale=0.1]{images/blank.jpg} %replace this when the actual plot becomes available
+% \begin{figure}[h]
+% 	\centering
+% 	\includegraphics[scale=0.1]{figures/blank.jpg} %replace this when the actual plot becomes available
 	%\centerline{\includegraphics{ftcbuild2.pdf}}
-	\caption{Plot obtained from the above geodesics showing the phenomenon of frame dragging}
-	\label{fig:kerr}
-\end{figure}
+% 	\caption{Plot obtained from the above geodesics showing the phenomenon of frame dragging}
+% 	\label{fig:kerr}
+% \end{figure}
 
@@
 Kerr-Newman metric presents the most general case within single-body vacuum solutions of Einstein Field Equation.
-It generalizes all the quantities used to describe a black hole, as affirmed by "no hair" theoram, i.e.
+It generalizes all the quantities used to describe a black hole, as affirmed by "no hair" theorem, i.e.
 Charge $Q$, Angular Momentum $J$ and Mass $M$.
@@
 \subsection{COORDINATES}
+The coordinates subpackage provides support for representing and transforming coordinates. Cartesian, Spherical and BoyerLindquist coordinate system can be accessed while using einsteinpy.
+
 \subsection{SYMBOLIC}
@@
 
-The defined class functions are :
-\begin{itemize}
-\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
-\item \texttt{inv} : returns inverse of the metric
-\end{itemize}
+% The defined class functions are :
+% \begin{itemize}
+% \item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+% \item \texttt{inv} : returns inverse of the metric
+% \end{itemize}
 
-Also, the library maintains an ever expanding predefined metrics for direct use. Here's an code snippet for a better dive into the specificities of the class.
+Also, the library maintains an ever expanding predefined metrics for direct use in research purposes.
 
-\begin{lstlisting}[language=Python, caption=Importing a predefined metric]
->>> from einsteinpy.symbolic.predefined import CMetric
->>> metric = CMetric
->>> metric.tensor()
-\end{lstlisting}
+%\begin{lstlisting}[language=Python, caption=Importing a predefined metric]
+%>>> from einsteinpy.symbolic.predefined import CMetric
+%>>> metric = CMetric
+% >>> metric.tensor()
+% \end{lstlisting}
 
-\begin{center}
-$\displaystyle \left[\begin{matrix}- \frac{h{\left(y \right)}}{\left(x + y\right)^{2}} & 0 & 0 & 0\\0 & \frac{1}{\left(x + y\right)^{2} f{\left(x \right)}} & 0 & 0\\0 & 0 & \frac{1}{\left(x + y\right)^{2} h{\left(y \right)}} & 0\\0 & 0 & 0 & \frac{f{\left(x \right)}}{\left(x + y\right)^{2}}\end{matrix}\right]$
-\end{center}
+% \begin{center}
+% $\displaystyle \left[\begin{matrix}- \frac{h{\left(y \right)}}{\left(x + y\right)^{2}} & 0 & 0 & 0\\0 & \frac{1}{\left(x + y\right)^{2} f{\left(x \right)}} & 0 & 0\\0 & 0 & \frac{1}{\left(x + y\right)^{2} h{\left(y \right)}} & 0\\0 & 0 & 0 & \frac{f{\left(x \right)}}{\left(x + y\right)^{2}}\end{matrix}\right]$
+% \end{center}
 
-\begin{lstlisting}[language=Python, caption=Displaying the contravarint configuration of metric]
->>> metric.change_config("uu").tensor()
-\end{lstlisting}
+% \begin{lstlisting}[language=Python, caption=Displaying the contravarint configuration of metric]
+% >>> metric.change_config("uu").tensor()
+% \end{lstlisting}
 
-\begin{center}
- $\displaystyle \left[\begin{matrix}- \frac{\left(x + y\right)^{2}}{h{\left(y \right)}} & 0 & 0 & 0\\0 & \left(x + y\right)^{2} f{\left(x \right)} & 0 & 0\\0 & 0 & \left(x + y\right)^{2} h{\left(y \right)} & 0\\0 & 0 & 0 & \frac{\left(x + y\right)^{2}}{f{\left(x \right)}}\end{matrix}\right]$ \\
-\end{center}
+% \begin{center}
+%  $\displaystyle \left[\begin{matrix}- \frac{\left(x + y\right)^{2}}{h{\left(y \right)}} & 0 & 0 & 0\\0 & \left(x + y\right)^{2} f{\left(x \right)} & 0 & 0\\0 & 0 & \left(x + y\right)^{2} h{\left(y \right)} & 0\\0 & 0 & 0 & \frac{\left(x + y\right)^{2}}{f{\left(x \right)}}\end{matrix}\right]$ \\
+% \end{center}
 
@@
 
-Instance of the class can be made by directly passing a 3\textsuperscript{rd} order tensor or can be obtained using the following classmethods,
-\begin{itemize}
-\item \texttt{from\_metric} : Calculates christoffel symbols from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
-\end{itemize}
+% Instance of the class can be made by directly passing a 3\textsuperscript{rd} order tensor or can be obtained using the following classmethods,
+% \begin{itemize}
+% \item \texttt{from\_metric} : Calculates christoffel symbols from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+% \end{itemize}
 
-The defined class function(s) are : 
-\begin{itemize}
-\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
-\end{itemize}
+% The defined class function(s) are : 
+% \begin{itemize}
+% \item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+% \end{itemize}
 
@@
 
-Instance of the class can be made by directly passing a 4\textsuperscript{th} order tensor or can be obtained using the following classmethods
-\begin{itemize}
-\item \texttt{from\_metric} : Calculates Riemann Tensor from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
-\item \texttt{from\_christoffels} : Calculates Riemann Tensor from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
-\end{itemize}
+% Instance of the class can be made by directly passing a 4\textsuperscript{th} order tensor or can be obtained using the following classmethods
+% \begin{itemize}
+% \item \texttt{from\_metric} : Calculates Riemann Tensor from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+% \item \texttt{from\_christoffels} : Calculates Riemann Tensor from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
+% \end{itemize}
 
-The defined class function(s) are : 
-\begin{itemize}
-\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
-\end{itemize}
+% The defined class function(s) are : 
+% \begin{itemize}
+% \item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+% \end{itemize}
 
@@
 
-Instance of the class can be made by directly passing a 2\textsuperscript{nd} order tensor or can be obtained using the following classmethods
-\begin{itemize}
-\item \texttt{from\_metric} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
-\item \texttt{from\_christoffels} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
-\item \texttt{from\_riemann} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}} class.
-\end{itemize}
+% Instance of the class can be made by directly passing a 2\textsuperscript{nd} order tensor or can be obtained using the following classmethods
+% \begin{itemize}
+% \item \texttt{from\_metric} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+% \item \texttt{from\_christoffels} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
+% \item \texttt{from\_riemann} : Calculates Ricci Tensor from a given instance of \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}} class.
+% \end{itemize}
 
-The defined class function(s) are : 
-\begin{itemize}
-\item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
-\end{itemize}
+% The defined class function(s) are : 
+% \begin{itemize}
+% \item \texttt{change\_config} : returns a different instance of the same class with different index (contravariant or covariant) configuration. 
+% \end{itemize}
 
@@
 
-Instance of the class can be made by directly passing a symbolic expression or can be obtained using the following classmethods
-\begin{itemize}
-\item \texttt{from\_metric} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
-\item \texttt{from\_christoffels} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
-\item \texttt{from\_riemann} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}} class.
-\item \texttt{from\_riccitensor} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:riccitensor]{\textit{RicciTensor}} class.
-\end{itemize}
+% Instance of the class can be made by directly passing a symbolic expression or can be obtained using the following classmethods
+% \begin{itemize}
+% \item \texttt{from\_metric} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:metric]{\textit{MetricTensor}} class.
+% \item \texttt{from\_christoffels} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}} class.
+% \item \texttt{from\_riemann} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}} class.
+% \item \texttt{from\_riccitensor} : Calculates Ricci Scalar from a given instance of \hyperref[subsubsec:riccitensor]{\textit{RicciTensor}} class.
+% \end{itemize}
 
-The defined class properties are : 
-\begin{itemize}
-\item \texttt{expr} : returns the scalar symbolic expression contained in the class. 
-\end{itemize}
+% The defined class properties are : 
+% \begin{itemize}
+% \item \texttt{expr} : returns the scalar symbolic expression contained in the class. 
+% \end{itemize}
 
@@
 \subsection{HYPERSURFACE}
+This module provides basic computational functions which are essential for modelling the space-like hypersurface for any space-time geometry.
+Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities.
+The whole module is expected to extend for providing a super-class for implementations related to gravitational lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems.
+A small code snippet for plotting the hypersurface is as follows:
+\begin{lstlisting}[language=Python, caption=Schwarzschild Embedding]
+>>> surface_obj = SchwarzschildEmbedding(5.927e23 * u.kg)
+>>> surface = HypersurfacePlotter(embedding=surface_obj, plot_type='surface')
+>>> surface.plot()
+>>> surface.show()
+\end{lstlisting}
+
 \subsection{PLOTTING}
+The plotting ecosystem in EinsteinPy has two back-ends for two type of users.
+A static, matplotlib based plotter for publication quality plots and an interactive plotly based plotter for analysis and interpretation.
+\\
+The plotting module is specifically designed keeping in mind the variety of IDEs and tools people working with Python use, for example python scripts, jupyter notebooks, spyder, pycharm etc.
+As plotly plots need JavasScript to render plots, it becomes difficult for the first time user to decide which backend to use.
+\texttt{StaticGeodesicPlotter} and \texttt{InteractiveGeodesicPlotter} undergo an internal switching depending on the environment variables and the appropriate environment aware plot is shown to the user for a better user experience and interface.\\
+The plotting module throughout the applications follow a very consistent API. \begin{lstlisting}[language=Python, caption=Plotting Module API]
+>>> data = Plotter()
+>>> data.plot()
+>>> data.show()
+\end{lstlisting}
 
@@
 \subsection{ Documentation and gallery} \label{subsec:doc}
+The EinsteinPy Project strives to provide high quality, up-to-date and accurate documentation of the software.
+The documentation is highly approachable with easy and intuitive user interface.
+The documentation is self-updating with every change in the codebase, and is rendered automatically from the docstrings written for each function and classes.
+Along with the main API, new example codes for different functionalities is added to the repository frequently in the form of jupyter notebooks.
+Many sections like User Guide and Developer Guide has been written for easy on-boarding of new users and contributors.
 
@@
 
-We thank all the people that have made this AASTeX what it is today.  This
-includes but not limited to Bob Hanisch, Chris Biemesderfer, Lee Brotzman,
-Pierre Landau, Arthur Ogawa, Maxim Markevitch, Alexey Vikhlinin and Amy
-Hendrickson. Also special thanks to David Hogg and Daniel Foreman-Mackey
-for the new "modern" style design. Considerable help was provided via bug
-reports and hacks from numerous people including Patricio Cubillos, Alex
-Drlica-Wagner, Sean Lake, Michele Bannister, Peter Williams, and Jonathan
-Gagne.
+We thank all the people that have made EinsteinPy what it is today.  
+The organisations ESA, Poliastro and Indian institute of Technology, Mandi provided us with significant support and have our deepest thanks.
+We would specially like to thank Dr.Abhay Ashtekar and  Dr. Timothy A. Gonsalves for their constant motivation.
+Lastly, thanks to all our contributors who contrubuted towards building EinsteinPy.
 
@@
 %% parentheses, after the keyword, but they are not verified.
-
-\vspace{5mm}
-\facilities{HST(STIS), Swift(XRT and UVOT), AAVSO, CTIO:1.3m,
-CTIO:1.5m,CXO}
 
@@
 
-\appendix
-
-\section{Appendix information}
-
-Appendices can be broken into separate sections just like in the main text.
-The only difference is that each appendix section is indexed by a letter
-(A, B, C, etc.) instead of a number.  Likewise numbered equations have
-the section letter appended.  Here is an equation as an example.
-
-\begin{equation}
-I = \frac{1}{1 + d_{1}^{P (1 + d_{2} )}}
-\end{equation}
-
-Appendix tables and figures should not be numbered like equations. Instead
-they should continue the sequence from the main article body.
+% \appendix
+% \section{Appendix information}
 

### 2020-01-24 paper.tex
Add bibliography

@@
 \section{Introduction} \label{sec:intro}
-The relativistic theory of gravity paved its way to the ground in 1915?, when Prof.
-Albert Einstein published his paper on the general theory of relativity.
+The relativistic theory of gravity paved its way to the ground in 1916, when Prof.
+Albert Einstein published his paper on the general theory of relativity \citep{Einstein:1916vd}.
 This elegant and rigorous framework was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905.
-Almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein field equations remain extremely difficult to find beyond those which exhibit significant symmetries.\\
+Even after almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein field equations remain extremely difficult to find beyond those which exhibit significant symmetries.\\
 We can study the behavior of solutions under a high degree of symmetry considerations and could even solve analytically for highly unrealistic systems.
@@
 A release having the changes is made at a later date.
-EinsteinPy only supports the latest bleeding-edge Python, Numpy and Astropy versions.
+EinsteinPy only supports the latest bleeding-edge Python, Numpy\citep{numpy} and Astropy\citep{astropy:2018} versions.
 All the stable Python versions after Python 3.5 are supported.
-All the code snippets written follow the guidelines of numba in order to accelerate the Python code and make the simulations faster.
+All the code snippets written follow the guidelines of numba\citep{Lam2015NumbaAL} in order to accelerate the Python code and make the simulations faster.
 
 \section{The EinsteinPy Core Package} \label{sec:core}
-This section explains in detail, the modules available within EinsteinPy core pacakge, their API and the purpose they serve.
+This section explains in detail, the modules available within EinsteinPy core package, their API and the purpose they serve.
 \subsection{METRIC} \label{subsec:metric}
-This module captures all the geometric and causal structure of specific spacetimes, and being able to calculate trajectories in a given space-time. 
+This module captures all the geometric and causal structure of specific space-times, and being able to calculate trajectories in a given space-time. 
 The module derives its name from Metric Tensor, a tensorial quantity used to describe differential lengths, especially in a curved space-time. 
-However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of newtonian physics fail.
-\subsubsection{Schwarzschild Metric} \label{subsubsec:sch}
-Karl Schwarzchild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body.
-The metric equation corrosponding to a space-time centred around a body in the above described conditions is given by,
+However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of Newtonian physics fail.
+\subsubsection{Schwarzschild Metric \citep{Schwarzschild:1916uq}} \label{subsubsec:sch}
+Karl Schwarzschild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body.
+The metric equation corresponding to a space-time centred around a body in the above described conditions is given by,
 
@@
 
-%The same equation can be written in a tensorial form as follows,
+%The same equation can be written in a tonsorial form as follows,
 
@@
 We thank all the people that have made EinsteinPy what it is today.  
-The organisations ESA, Poliastro and Indian institute of Technology, Mandi provided us with significant support and have our deepest thanks.
-We would specially like to thank Dr.Abhay Ashtekar and  Dr. Timothy A. Gonsalves for their constant motivation.
-Lastly, thanks to all our contributors who contrubuted towards building EinsteinPy.
+The generous sponsorship by European Space Agency during Summer of Code in Space really helped us with the betterment of code.
+We would like to thank the awesome poliastro \citep{juan_luis_cano_rodriguez_2019_3588160} for always motivating us and for being the first sponsor for the project.
+We would also like to thank our host university, Indian institute of Technology, Mandi who provided us with significant support and have our deepest thanks.
+We would specially like to thank Prof.Abhay Ashtekar for his motivational email and  Prof. Timothy A. Gonsalves for his constant motivation and support.
+Lastly, we thank all our contributors who contributed selflessly for building this amazing software called EinsteinPy.
 
@@
 
-\software{astropy \citep{2013A&A...558A..33A},  
-          Cloudy \citep{2013RMxAA..49..137F}, 
-          SExtractor \citep{1996A&AS..117..393B}
+\software{astropy \citep{astropy:2013} \citep{astropy:2018},  
+          Numpy \citep{numpy}, 
+          scipy \citep{2019arXiv190710121V},
+          numba \citep{Lam2015NumbaAL},
+          matplotlib \citep{matplotlib}
           }
@@
 
-\bibliography{sample63}{}
+\bibliography{bibliography}{}
 \bibliographystyle{aasjournal}

### 2020-05-04 paper.tex
Paper-finalise

@@
-%% Beginning of file 'sample63.tex'
-%%
-%% Modified 2019 June
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v6.3 LaTeX 2e macros.
-%%
-%% AASTeX is now based on Alexey Vikhlinin's emulateapj.cls 
-%% (Copyright 2000-2015).  See the classfile for details.
+%                                                                 aa.dem
+% AA vers. 9.1, LaTeX class for Astronomy & Astrophysics
+% demonstration file
+%                                                       (c) EDP Sciences
+%-----------------------------------------------------------------------
+%
+%\documentclass[referee]{aa} % for a referee version
+%\documentclass[onecolumn]{aa} % for a paper on 1 column  
+%\documentclass[longauth]{aa} % for the long lists of affiliations 
+%\documentclass[letter]{aa} % for the letters 
+%\documentclass[bibyear]{aa} % if the references are not structured 
+%                              according to the author-year natbib style
 
-%% AASTeX requires revtex4-1.cls (http://publish.aps.org/revtex4/) and
-%% other external packages (latexsym, graphicx, amssymb, longtable, and epsf).
-%% All of these external packages should already be present in the modern TeX 
-%% distributions.  If not they can also be obtained at www.ctan.org.
-
-%% The first piece of markup in an AASTeX v6.x document is the \documentclass
-%% command. LaTeX will ignore any data that comes before this command. The 
-%% documentclass can take an optional argument to modify the output style.
-%% The command below calls the preprint style which will produce a tightly 
-%% typeset, one-column, single-spaced document.  It is the default and thus
-%% does not need to be explicitly stated.
-%%
-%%
-%% using aastex version 6.3
-\documentclass{aastex63}
-\usepackage{amsmath}
-\usepackage[utf8]{inputenc}
-\usepackage{listings}  % for code in latex
-\usepackage{color}
-\usepackage{hyperref}
-% \usepackage{caption}
-
-%% The default is a single spaced, 10 point font, single spaced article.
-%% There are 5 other style options available via an optional argument. They
-%% can be invoked like this:
-%%
-%% \documentclass[arguments]{aastex63}
-%% 
-%% where the layout options are:
-%%
-%%  twocolumn   : two text columns, 10 point font, single spaced article.
-%%                This is the most compact and represent the final published
-%%                derived PDF copy of the accepted manuscript from the publisher
-%%  manuscript  : one text column, 12 point font, double spaced article.
-%%  preprint    : one text column, 12 point font, single spaced article.  
-%%  preprint2   : two text columns, 12 point font, single spaced article.
-%%  modern      : a stylish, single text column, 12 point font, article with
-%% 		  wider left and right margins. This uses the Daniel
-%% 		  Foreman-Mackey and David Hogg design.
-%%  RNAAS       : Preferred style for Research Notes which are by design 
-%%                lacking an abstract and brief. DO NOT use \begin{abstract}
-%%                and \end{abstract} with this style.
-%%
-%% Note that you can submit to the AAS Journals in any of these 6 styles.
-%%
-%% There are other optional arguments one can invoke to allow other stylistic
-%% actions. The available options are:
-%%
-%%   astrosymb    : Loads Astrosymb font and define \astrocommands. 
-%%   tighten      : Makes baselineskip slightly smaller, only works with 
-%%                  the twocolumn substyle.
-%%   times        : uses times font instead of the default
-%%   linenumbers  : turn on lineno package.
-%%   trackchanges : required to see the revision mark up and print its output
-%%   longauthor   : Do not use the more compressed footnote style (default) for 
-%%                  the author/collaboration/affiliations. Instead print all
-%%                  affiliation information after each name. Creates a much 
-%%                  longer author list but may be desirable for short 
-%%                  author papers.
-%% twocolappendix : make 2 column appendix.
-%%   anonymous    : Do not show the authors, affiliations and acknowledgments 
-%%                  for dual anonymous review.
-%%
-%% these can be used in any combination, e.g.
-%%
-%% \documentclass[twocolumn,linenumbers,trackchanges]{aastex63}
-%%
-%% AASTeX v6.* now includes \hyperref support. While we have built in specific
-%% defaults into the classfile you can manually override them with the
-%% \hypersetup command. For example,
-%%
-%% \hypersetup{linkcolor=red,citecolor=green,filecolor=cyan,urlcolor=magenta}
-%%
-%% will change the color of the internal links to red, the links to the
-%% bibliography to green, the file links to cyan, and the external links to
-%% magenta. Additional information on \hyperref options can be found here:
-%% https://www.tug.org/applications/hyperref/manual.html#x1-40003
-%%
-%% Note that in v6.3 "bookmarks" has been changed to "true" in hyperref
-%% to improve the accessibility of the compiled pdf file.
-%%
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-\newcommand{\vdag}{(v)^\dagger}
-\newcommand\aastex{AAS\TeX}
-\newcommand\latex{La\TeX}
-
-%% Reintroduced the \received and \accepted commands from AASTeX v5.2
-\received{June 1, 2019}
-\revised{January 10, 2019}
-\accepted{\today}
-%% Command to document which AAS Journal the manuscript was submitted to.
-%% Adds "Submitted to " the argument.
-\submitjournal{ApJ}
-
-%% For manuscript that include authors in collaborations, AASTeX v6.3
-%% builds on the \collaboration command to allow greater freedom to 
-%% keep the traditional author+affiliation information but only show
-%% subsets. The \collaboration command now must appear AFTER the group
-%% of authors in the collaboration and it takes TWO arguments. The last
-%% is still the collaboration identifier. The text given in this
-%% argument is what will be shown in the manuscript. The first argument
-%% is the number of author above the \collaboration command to show with
-%% the collaboration text. If there are authors that are not part of any
-%% collaboration the \nocollaboration command is used. This command takes
-%% one argument which is also the number of authors above to show. A
-%% dashed line is shown to indicate no collaboration. This example manuscript
-%% shows how these commands work to display specific set of authors 
-%% on the front page.
-%%
-%% For manuscript without any need to use \collaboration the 
-%% \AuthorCollaborationLimit command from v6.2 can still be used to 
-%% show a subset of authors.
 %
-%\AuthorCollaborationLimit=2
+\documentclass[onecolumn]{aa}  
+%\documentclass[bibyear]{aa}
+%\documentclass[onecolumn]{aa}  
+\usepackage{graphicx}
+\usepackage{listings}
+\usepackage{xspace}
+\usepackage{natbib}
+\usepackage{url}
+\usepackage[xindy, toc, hyperfirst=false, nolist, nostyles, sanitize={name=false,description=false,symbol=false}]{glossaries}
+\bibpunct{(}{)}{;}{a}{}{,} % to follow the A&A style
 %
-%% will only show Schwarz & Muench on the front page of the manuscript
-%% (assuming the \collaboration and \nocollaboration commands are
-%% commented out).
-%%
-%% Note that all of the author will be shown in the published article.
-%% This feature is meant to be used prior to acceptance to make the
-%% front end of a long author article more manageable. Please do not use
-%% this functionality for manuscripts with less than 20 authors. Conversely,
-%% please do use this when the number of authors exceeds 40.
-%%
-%% Use \allauthors at the manuscript end to show the full author list.
-%% This command should only be used with \AuthorCollaborationLimit is used.
-
-%% The following command can be used to set the latex table counters.  It
-%% is needed in this document because it uses a mix of latex tabular and
-%% AASTeX deluxetables.  In general it should not be needed.
-%\setcounter{table}{1}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%
-%% The following section outlines numerous optional output that
-%% can be displayed in the front matter or as running meta-data.
-%%
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-\shorttitle{EinsteinPy: Python for General Relativity}
-\shortauthors{The EinsteinPy Community}
-%%
-%% You can add a light gray and diagonal water-mark to the first page 
-%% with this command:
-%% \watermark{text}
-%% where "text", e.g. DRAFT, is the text to appear.  If the text is 
-%% long you can control the water-mark size with:
-%% \setwatermarkfontsize{dimension}
-%% where dimension is any recognized LaTeX dimension, e.g. pt, in, etc.
-%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\graphicspath{{./}{figures/}}
-%% This is the end of the preamble.  Indicate the beginning of the
-%% manuscript itself with \begin{document}.
-
+\usepackage{graphicx}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\usepackage{txfonts}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%\usepackage[options]{hyperref}
+% To add links in your PDF file, use the package "hyperref"
+% with options according to your LaTeX or PDFLaTeX drivers.
+%
 \begin{document}
 
-\title{EinsteinPy: Python for General Relativity}
+   \title{EinsteinPy: A Community Python Package for General Relativity}
 
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire. In v6.3 you can include a footnote in the title.
+   \subtitle{}
 
-%% A significant change from earlier AASTEX versions is in the structure for 
-%% calling author and affiliations. The change was necessary to implement 
-%% auto-indexing of affiliations which prior was a manual process that could 
-%% easily be tedious in large author manuscripts.
-%%
-%% The \author command is the same as before except it now takes an optional
-%% argument which is the 16 digit ORCID. The syntax is:
-%% \author[xxxx-xxxx-xxxx-xxxx]{Author Name}
-%%
-%% This will hyperlink the author name to the author's ORCID page. Note that
-%% during compilation, LaTeX will do some limited checking of the format of
-%% the ID to make sure it is valid. If the "orcid-ID.png" image file is 
-%% present or in the LaTeX pathway, the OrcID icon will appear next to
-%% the authors name.
-%%
-%% Use \affiliation for affiliation information. The old \affil is now aliased
-%% to \affiliation. AASTeX v6.3 will automatically index these in the header.
-%% When a duplicate is found its index will be the same as its previous entry.
-%%
-%% Note that \altaffilmark and \altaffiltext have been removed and thus 
-%% can not be used to document secondary affiliations. If they are used latex
-%% will issue a specific error message and quit. Please use multiple 
-%% \affiliation calls for to document more than one affiliation.
-%%
-%% The new \altaffiliation can be used to indicate some secondary information
-%% such as fellowships. This command produces a non-numeric footnote that is
-%% set away from the numeric \affiliation footnotes.  NOTE that if an
-%% \altaffiliation command is used it must come BEFORE the \affiliation call,
-%% right after the \author command, in order to place the footnotes in
-%% the proper location.
-%%
-%% Use \email to set provide email addresses. Each \email will appear on its
-%% own line so you can put multiple email address in one \email call. A new
-%% \correspondingauthor command is available in V6.3 to identify the
-%% corresponding author of the manuscript. It is the author's responsibility
-%% to make sure this name is also in the author list.
-%%
-%% While authors can be grouped inside the same \author and \affiliation
-%% commands it is better to have a single author for each. This allows for
-%% one to exploit all the new benefits and should make book-keeping easier.
-%%
-%% If done correctly the peer review system will be able to
-%% automatically put the author and affiliation information from the manuscript
-%% and save the corresponding author the trouble of entering it by hand.
-\input{authors.tex}
+   \author{
+Shreyas Bapat\inst{\ref{inst:iitm}}  % confirmed
+  \and
+Ritwik Saha\inst{\ref{inst:iitm}}  % confirmed
+  \and
+Bhavya Bhatt\inst{\ref{inst:iitm}}  % confirmed
+\and
+Shilpi Jain\inst{\ref{inst:iitr}}
+\and
+Akshita Jain\inst{\ref{inst:iitm}}
+\and
+Sofía Ortín Vela\inst{\ref{inst:uz}}
+\and
+Priyanshu Khandelwal\inst{\ref{inst:gatech}}
+\and
+Jyotirmaya Shivottam\inst{\ref{inst:niser}}
+\and
+Jialin Ma\inst{\ref{inst:gatech}}
+}
+   \institute{
+  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India
+  \label{inst:iitm}
+    \and
+  Department of Earth Sciences, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
+  \label{inst:iitr}
+    \and
+  University of Zaragoza, Calle de Pedro Cerbuna, 12, 50009 Zaragoza, Spain
+  \label{inst:uz}
+    \and
+  Georgia Institute of Technology, USA
+  \label{inst:gatech}
+    \and
+   School of Physical Sciences, National Institute of Science Education and Research, Jatni, Khurdha, Odisha, India
+   \label{inst:niser}
+}
 
-%% Note that the \and command from previous versions of AASTeX is now
-%% depreciated in this version as it is no longer necessary. AASTeX 
-%% automatically takes care of all commas and "and"s between authors names.
+   \date{Received May 04, 2020; accepted May 04, 2020}
 
-%% AASTeX 6.3 has the new \collaboration and \nocollaboration commands to
-%% provide the collaboration status of a group of authors. These commands 
-%% can be used either before or after the list of corresponding authors. The
-%% argument for \collaboration is the collaboration identifier. Authors are
-%% encouraged to surround collaboration identifiers with ()s. The 
-%% \nocollaboration command takes no argument and exists to indicate that
-%% the nearby authors are not part of surrounding collaborations.
+  \abstract
+{This paper presents EinsteinPy (version 0.3), a community-developed Python package for gravitational and relativistic astrophysics.
+Python is a free, easy to use a high-level programming language which has seen a huge expansion in the number of its users and developers in recent years.
+Specifically, a lot of recent studies show that the use of Python in Astrophysics and general physics has increased exponentially.
+Many great frameworks came as Python packages which provide a very high level of abstraction over the dirty nitty-gritty of complex algorithms and provide an easy to use interface and pleasing user experience.
+One such example is Keras - a framework for deep learning which has made deep learning so easy that a person with zero programming knowledge can also train a neural network classifier.
+This example demonstrates the power of abstraction which is achievable in Python.
+The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.
+Currently, EinsteinPy supports simulation of time-like and null geodesics and calculates trajectories in different background geometries some of which are Schwarzschild, Kerr, and KerrNewmann along with coordinate inter-conversion pipeline.
+It has a partially developed pipeline for plotting and visualization with dependencies on libraries like Plotly, matplotlib, etc.
+One of the unique features of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilities which are a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky.
+EinsteinPy also provides few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.
+The current version of the library is in a state that can be used by any serious student of general relativity trying to get the essence of this beautiful subject but is somewhere lost in the heavy mathematical formalism of the subject.
+EinsteinPy provides such students to really see through the equations and visualize what's really happening.}
 
-%% Mark off the abstract in the ``abstract'' environment. 
-\begin{abstract}
+   \keywords{
+    gravitational physics --
+    astrophysics --
+    simulations --
+    black holes --
+    astropy
+    }
 
-This paper presents EinsteinPy (version 0.3), a community-developed Python
-package for gravitational and relativistic astrophysics.
-Python is a free, easy to use high level programming language which has seen a huge expansion in the number of its users and developers in recent years.
-Specifically, a lot of recent studies show that the use of Python in Astrophysics and in general physics has increased exponentially.
-Many great frameworks came as Python packages which provide a very high level of abstraction over the dirty nitty-gritty of complex algorithms and provide an easy to use interfaceand pleasing user experience.
-One such example is Keras - framework for deep learning which has made deep learning so easy that a person with zero programming knowledge can also train a neural network classifier.
-This example really demonstrates the power of abstraction which is achievable in Python.
-The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with a little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.
-Currently EinsteinPy supports simulation of time-like and null geodesics and calculate trajectories in different background geometries some of which are Schwarzschild, Kerr and KerrNewmann along with coordinate inter-conversion pipeline.
-It has a partially developed pipeline for plotting and visualization with dependencies on libraries like plotly, matplotlib etc.
-One of the unique feature of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilites which is a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky.
-Currently EinsteinPy also provide few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.
-The current version of the library is in a state that can be used by any serious student of general relativity trying to get essence of this beautiful subject but is somewhere lost in the heavy mathematical formalism of the subject.
-EinsteinPy provides such students to really see through the equations and visualize whats really happening.
+   \maketitle
+%
+%-------------------------------------------------------------------
 
-\end{abstract}
+\section{Introduction}
 
-%% Keywords should appear after the \end{abstract} command. 
-%% See the online documentation for the full list of available subject
-%% keywords and the rules for their use.
-\keywords{gravitational physics, astrophysics --- 
-simulations --- black holes --- gravitational waves}
+   The relativistic theory of gravity paved its way to the ground in 1916, 
+   when Prof. Albert Einstein published his paper on the general theory of 
+   relativity \citeyear{Einstein:1916vd}. This elegant and rigorous framework 
+   was a generalized version of gravity-free theory - special relativity, 
+   which he published earlier in 1905. Even after almost a hundred years 
+   after Einstein wrote down the equations of General Relativity, solutions 
+   of the Einstein field equations remain extremely difficult to find beyond 
+   those which exhibit significant symmetries.
 
-%% From the front matter, we move on to the body of the paper.
-%% Sections are demarcated by \section and \subsection, respectively.
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-%%
-%% We recommend that authors also use the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below.
+   We can study the behaviour of solutions under a high degree of symmetry 
+   considerations and could even solve analytically for highly unrealistic 
+   systems. In case of problems relevant to astrophysical and gravitational 
+   physics research, it remains a big daunting question on how to get around 
+   the problem of solving these field equations. This question is so profound 
+   that it has a separate field of research which goes with the name of numerical  
+   relativity and attempts to use computation science and programming to numerically 
+   obtain solutions of the equations (which would be the background geometry) 
+   for some turbulent region where most of the interesting dynamics are happening 
+   (as we can not solve for an infinitely large grid due to restrictions imposed 
+   on us by space and time complexity and computation power).
 
-\section{Introduction} \label{sec:intro}
-The relativistic theory of gravity paved its way to the ground in 1916, when Prof.
-Albert Einstein published his paper on the general theory of relativity \citep{Einstein:1916vd}.
-This elegant and rigorous framework was a generalized version of gravity-free theory - special relativity, which he published earlier in 1905.
-Even after almost a hundred years after Einstein wrote down the equations of General Relativity, solutions of the Einstein field equations remain extremely difficult to find beyond those which exhibit significant symmetries.\\
-We can study the behavior of solutions under a high degree of symmetry considerations and could even solve analytically for highly unrealistic systems.
-In case of problems relevant to astrophysical and gravitational physics research, it still remains a big daunting question on how to get around the problem of solving these field equations.
-This question is so profound that it has a separate profound field of research which goes with the name of numerical relativity which attempts to use computation science and programming to numerically obtain solutions of the equations (which would be the background geometry) for some turbulent region where most of the interesting dynamics are happening (as we can not solve for an infinitely large grid due to restrictions imposed on us by space and time complexity and computability).\\
-Numerical methods have been used to solve the Einstein equation for many decades, but the past decade has seen tremendous advances and adding to that, the interest of the community grew when the field found applications in areas of radio astronomy, cosmology, signal processing, data mining.
-The field of numerical relativity is growing rampantly with the vast literature on algorithms, numerical methods and theoretical formulations (from basic 3+1 decomposition formulation to more sophisticated ones) with the development of robust and involved frameworks that provide a complete programming ecosystem and have proved to be essential tools for any numerical relativity researcher.\\
-Reflecting the other end of the research community stands the major section of theoretical physicists which counts the majority as a novice in programming.
-The head challenge is the fact that the usage of these frameworks demands heavy use of high-level programming languages like C, C++, Python, etc.
-Though Python provides a vast room for abstractions no library existed that focused towards numerical relativity, eventually, the need of python library dedicated to general relativity became the propellant for the team and thus they made dauntless efforts to cover the space for this Python library.
-Since then, EinsteinPy has seen a lot of contributions from people all over the world and many ”good to go” functionalities are already provided in this and previous versions.\\
-EinsteinPy is made to provide a set of tools which can make numerical computations for solving Einstein’s field equations an easy job for anyone who does not want to deal with intricacies of the subject along with few, very basic but powerful functionalities that could be used by anyone who wants to learn the subject of general relativity with every minute detail.
-The library is as an attempt to provide programming and numerical environment for numerous numerical relativity problems like geodesics plotter, gravitational lensing and ray tracing, solving and simulating relativistic hydrodynamical equations, plotting of black hole event horizons, solving Einstein’s field equations and simulating various dynamical systems like binary merger etc.\\
-EinsteinPy provides an open-source and open-development core package and aims to build an ecosystem of affiliated packages that support numeric relativity functionality in the Python programming language.
-”Open development” describes a process where anybody with an internet connection can suggest changes to the source code and contribute their opinion when new features, bug fixes or other code changes, governance, or any other aspect of the development process is discussed.
-EinsteinPy core package is now a feature-rich library of sufficiently general tools and classes that support the development of more specialized code\\
-In the further coming section, we discuss with some of the features of the current as well previous version and the future plans which are yet to be implemented in the upcoming versions.Also, we describe a few code snippets to explain the usage of the library on which more details can be found on the organization website.
-The development of the EinsteinPy core package began as a community-driven effort to standardize core functionality for software in Python which renders a user-friendly interface for supporting numerical relativity and relativistic astrophysics research.\\
-We start this paper by describing the way EinsteinPy functions followed by the main software efforts developed by the EinsteinPy itself with proper detailed documentation of the current version release.
-We end with a short vision for the future of EinsteinPy to its contribution in the field of computational methodology in gravitational and relativistic Astrophysics.
+   The field of numerical relativity is growing rampantly with the vast literature 
+   on algorithms, numerical methods and theoretical formulations (from basic 3+1 
+   decomposition formulation to more sophisticated ones) with the development of 
+   robust and involved frameworks that provide a complete programming ecosystem 
+   and have proved to be essential tools for any numerical relativity researcher.
 
-\section{Data Types} \label{sec:datatypes}
+   Reflecting the other end of the research community stands the major section 
+   of theoretical physicists which counts the majority as a novice in programming. 
+   The head challenge is the fact that the usage of these frameworks demands 
+   heavy use of high-level programming languages like C, C++, Python, etc. 
+   Though Python provides a vast room for abstractions, no library existed that  
+   focused towards numerical relativity, eventually, the need of python library  
+   dedicated to general relativity became the propellant for the team and thus 
+   they made dauntless efforts to cover the space for this Python library. 
+   Since then, EinsteinPy has seen a lot of contributions from people all over 
+   the world and many ”good to go” functionalities are already provided in 
+   this and previous versions.
 
-The EinsteinPy package provides some core data types for calculating, operating on, visualizing geodesics and black holes.
-There are some data types created for symbolic manipulations and calculations of relativistic tensors.
-The most important data types for EinsteinPy are \texttt{Body}, \texttt{Geodesic} and \texttt{BaseRelativityTensor} objects that support defining and creating new bodies, storing and calculating geodesic for bodies, and handling respectively.
-The main purpose of these core classes is to standardize the way calculations and visualizations are done for various kinds of heavy cosmic bodies and black holes.
-The classes always maintain the consistency in units of measurement wherever applicable, and create a consistent and clean API for any non-programmer to understand.
-The classes are designed such that it resembles the flow of physics and are  as intuitional as possible.
-These core classes also include a rigid architecture for data manipulation and visualizations wherever applicable.
-Following sections provide deep insight into the above mentioned three code data types of EinsteinPy:
+   EinsteinPy is made to provide a set of tools which can make numerical 
+   computations for solving Einstein’s field equations an easy job for anyone 
+   who does not want to deal with intricacies of the subject along with few, 
+   very basic but powerful functionalities that could be used by anyone who 
+   wants to learn the subject of general relativity with every minute detail.
 
-\subsection{Body} \label{subsec:Body}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. 
-% A new body can be defined by some of the very basic constraints:
+   The library is as an attempt to provide programming and numerical environment 
+   for numerous numerical relativity problems like geodesics plotter, gravitational 
+   lensing and ray tracing, solving and simulating relativistic hydrodynamical  
+   equations, plotting of black hole event horizons, solving Einstein’s 
+   field equations and simulating various dynamical systems like binary merger etc.
 
-% \begin{itemize}
-% \item \texttt{name}: Body Name,
-% \item \texttt{mass}: Mass of the body with attached astropy units 
-% \item \texttt{R}: Radius of the body with attached astropy units
-% \item \texttt{differential}: Complete position and velocity vector of the body in form of a Cartesian / Spherical / BoyerLindquist data class object from einsteinpy coordinates (optional)
-% \item \texttt{a}: Spin factor (a) of the body for Kerr Solutions with attached astropy units (optional)
-% \item \texttt{q}: Charge of the body with attached astropy units (optional)
-% \item \texttt{is\_attractor}: A boolean variable concerned with if the body is to be supposed as a central attractor. (optional)
-% \item \texttt{parent}: Parent body for the body, object of the same data class (optional)
-% \end{itemize}
+   EinsteinPy provides an open-source and open-development core package and 
+   aims to build an ecosystem of affiliated packages that support numeric 
+   relativity functionality in the Python programming language. EinsteinPy 
+   core package is now a feature-rich library of sufficiently general tools 
+   and classes that support the development of more specialized code.
 
-\subsection{Geodesic} \label{subsec:Geodesic}
-The Body data type helps define the central black-hole or the heavy massed object and the objects revolving around it. 
-% A new body can be defined by some of the very basic constraints:
+   In the further coming section, we discuss with some of the features of the 
+   current as well previous version and the plans which are yet to be implemented 
+   in the upcoming versions. Also, we describe a few code snippets to explain 
+   the usage of the library on which more details can be found on the 
+   project website. We start this paper by describing the way EinsteinPy functions 
+   followed by the main software efforts developed by the EinsteinPy itself 
+   with proper detailed documentation of the current version release. We end 
+   with a short vision for the future of EinsteinPy to its contribution in 
+   the field of computational methodology in gravitational and 
+   relativistic Astrophysics.
 
-\subsection{BaseRelativityTensor} \label{subsec:BaseRelativityTensor}
-This is a base class from which other tensors in \textit{symbolic} module are derived.
-The user can use this class to create his/her own tensor while using the various in-built functions provided by this class.
-The class also maintains the indicial configuration of the tensor(contravariant and covariant indices), calculates the free variables used in describing the tensor other than those which depicts the axis of space-time itself (e.g.
-$t, x, y, z$).
-The class has a function to convert the symbolic tensorial quantities into functions where actual numerical values can be substitued.
+%--------------------------------------------------------------------
+\section{Data Types}
 
-% This class along with its parent class \textit{Tensor} have the following functions/properties,
-% \begin{itemize}
-% \item \texttt{order} (Property) : Returns the order of the tensor. 
-% \item \texttt{config} (Property) : Returns the arrangement of contravariant(upper)/covariant(lower) indices of the tensor. For example, 'ulll'.
-% \item \texttt{parent\_metric} (Property) : Returns the metric tensor of the space-time associated with the tensor, if present. Else returns \texttt{None}.
-% \item \texttt{tensor} (Function) : Returns the tensorial quantity contained within the class instance.
-% \item \texttt{subs} (Function) : Returns a new tensor upon substitution of current variables with new variables/values.
-% \item \texttt{simplify} (Function) : Returns a tensor contain simplified expressions from the current tensor.
-% \item \texttt{symbols} (Function) : Returns the symbols denoting each axis of the space-time.
-% \item \texttt{tensor\_lambdify} (Function) : Returns lambdified function of symbolic tensors. This means that the returned functions can accept numerical values and return numerical quantities.
-% \item \texttt{lorentz\_transform} (Function) : Returns a lorentz-transformed tensor when supplied with a transformation matrix.
-This function also considers the contravariance and covariance of tensors during transformation.
-% \end{itemize}
+%-------------------------------------- Two column figure (place early!)
+  The EinsteinPy package provides some core data types for calculating, 
+  operating, visualizing geodesics and black holes. There are some data 
+  types created for symbolic manipulations and calculations of relativistic 
+  tensors. The most important data types for EinsteinPy are \texttt{Body}, 
+  \texttt{Geodesic} and \texttt{BaseRelativityTensor} objects that support 
+  defining and creating new bodies, storing and calculating geodesic for 
+  bodies, and handling respectively. The main purpose of these core classes 
+  is to standardize the way calculations and visualizations are done for 
+  various kinds of heavy cosmic bodies and black holes. The classes always 
+  maintain the consistency in units of measurement wherever applicable, and 
+  create a consistent and clean API for any non-programmer to understand. 
+  The classes are designed such that it resembles the flow of physics and 
+  are as intuitional as possible. These core classes also include a rigid 
+  architecture for data manipulation and visualizations wherever applicable. 
+  Following sections provide deep insight into the above mentioned three 
+  core data types of EinsteinPy:
 
-\section{UNIT HANDLING} \label{sec:unithandle}
-All user-facing functionality provided by einsteinpy make use of astropy.units. 
-All functions and objects must have their input constrained to the appropriate type of unit (e.g., length, mass or energy).
-Inputs can then be provided with any units that match the required type (e.g., millimeters and inches are both valid units for length) and conversions occur automatically without user intervention.
-The einsteinpy.constant subpackage contains a few standard constants.
+  \subsection{Body}
+  The Body data type helps define an attractor i.e. the central black-hole 
+  or the heavy mass object and later the objects under its influence. 
+  The bodies can have their characteristics defined then and there thus 
+  helping the user create the system easily.
 
-\section{Development Model} \label{sec:devmodels}
+  \subsection{Geodesic}
+  A geodesic is the path that an-accelerating particle would follow. 
+  In the plane, the geodesics are straight lines. On the sphere, the 
+  geodesics are great circles. The Geodesic data type helps define the 
+  geodesic of a body in the presence of an attractor or more aptly, 
+  according to the system user created. These \texttt{Geodesic} objects 
+  can be defined for any configuration and metric.
+
+  \subsection{BaseRelativityTensor}
+  This is a base class from which other tensors in \textit{symbolic} 
+  module are derived. The user can use this class to create his/her 
+  own tensor while using the various in-built functions provided by this 
+  class. The class also maintains the indicial configuration of 
+  the tensor(contravariant and covariant indices), calculates the 
+  free variables used in describing the tensor other than those which 
+  depicts the axis of space-time itself (e.g. $t, x, y, z$). The class 
+  has a function to convert the symbolic tensorial quantities into 
+  functions where actual numerical values can be substituted.
+
+\section{Unit Handling}
+
+All user-facing functionality provided by EinsteinPy make use of Astropy \citet{astropy:2013} units. All functions and objects must have their input 
+constrained to the appropriate type of unit (e.g., length, mass or energy). 
+Inputs can then be provided with any units that match the required type 
+(e.g., millimeters and inches are both valid units for length) and conversions 
+occur automatically without user intervention. The einsteinpy.constant 
+subpackage contains a few standard constants.
+
+\section{Development Model}
 The EinsteinPy Project follows an open development model, which is widely used in the scientific Python community and other computational astrophysics packages.
 The project is hosted on GitHub as a public repository with restricted write access to some key people.
-Anyone, however is welcome and encouraged to make code contributions and suggest changes using pull requests.
-Since the repository containing the codebase is licenced under an open and permissive MIT licence,  the project allows commercial use, modification, sublicensing, distribution and private use as long as the copyright notice and licence is redistributed.
+However, anyone is welcomed and is encouraged to make code contributions and suggest changes using pull requests.
+Since the repository containing the codebase is licensed under an open and permissive MIT licence,  the project allows commercial use, modification, sub licensing, distribution and private use as long as the copyright notice and license are redistributed.
 The project uses git for distributed version control and relies on CircleCI, Codefactor, GitHub Actions etc.
 for running the unit tests and other CI checks for every pull request.
-The code quality is maintained at the highest standards with strong control on the cyclomatic complexity, code linting, imports ordering and a proper docstring wherever necessary.
-Every contribution is reviewed and it must meet the following requirements:
+The code quality is maintained at the highest standards with a strong control on the cyclomatic complexity, code linting, imports ordering and a proper docstring wherever necessary.
+Every contribution is reviewed to further see if it fulfils the following requirements:
 
 \begin{itemize}
-\item \texttt The code must strictly adhere to the PEP8 Standards, on the top of it, the code must be linted with black to save the reviewer’s time identifying the changes made and reduce the diff generated because of the patch.
+\item \texttt The code must strictly adhere to the PEP8 Standards, on the top of it, the code must be lined with black to save the reviewer’s time identifying the changes made and reduce the diff generated because of the patch.
 \item \texttt The imports in the code must be sorted using tools such as isort. 
@@
 A release having the changes is made at a later date.
-EinsteinPy only supports the latest bleeding-edge Python, Numpy\citep{numpy} and Astropy\citep{astropy:2018} versions.
+EinsteinPy only supports the latest bleeding-edge Python, Numpy\citep{numpy} and Astropy \citep{2019arXiv190710121V}{astropy:2018} versions.
 All the stable Python versions after Python 3.5 are supported.
-All the code snippets written follow the guidelines of numba\citep{Lam2015NumbaAL} in order to accelerate the Python code and make the simulations faster.
+All the code snippets written follow the guidelines of numba \citep{Lam2015NumbaAL} to accelerate the Python code and make the simulations faster.
 
-\section{The EinsteinPy Core Package} \label{sec:core}
+\section{The EinsteinPy Core Package} 
 This section explains in detail, the modules available within EinsteinPy core package, their API and the purpose they serve.
-\subsection{METRIC} \label{subsec:metric}
-This module captures all the geometric and causal structure of specific space-times, and being able to calculate trajectories in a given space-time. 
-The module derives its name from Metric Tensor, a tensorial quantity used to describe differential lengths, especially in a curved space-time. 
-However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a spacetime with high curvature, where notions of Newtonian physics fail.
-\subsubsection{Schwarzschild Metric \citep{Schwarzschild:1916uq}} \label{subsubsec:sch}
+\subsection{Metric}
+This module captures all the geometric and causal structure of specific space-times, and can calculate trajectories in a given space-time. 
+The module derives its name from Metric Tensor, a tensorial quantity used to describe differential lengths, especially in curved space-time. 
+However, this module serves more than its usual definition and ultimately leads us to obtain geodesics of particles in a space-time with high curvature, where notions of Newtonian physics fail.
+\subsubsection{Schwarzschild Metric} 
 Karl Schwarzschild pioneered the analysis of the relation between the size of black hole and its mass and this work paved the way for the first exact solution of Einstein's Field Equation under the limited case of single spherical non-rotating, non-charged body.
-The metric equation corresponding to a space-time centred around a body in the above described conditions is given by,
+The metric equation \citep{Schwarzschild:1916uq} corresponding to a space-time centred around a body in the above described conditions is given by,
 
@@
 
-%The same equation can be written in a tonsorial form as follows,
-
-%\begin{gather}
-%g_{\mu \nu} = \begin{bmatrix} - (1 - \frac{r_s}{r})c^2 & 0 & 0 & 0 \\ 0 & \frac{1}{(1 - \frac{r_s}{r})} & 0 & 0 \\ 0 & 0 & r^2 & 0 \\ 0 & 0 & 0 &  r^2 sin^2 \theta \end{bmatrix} \\ 
-%\nonumber \\
-%ds^2 = g_{\mu \nu} dx^\mu dx^\nu
-%\end{gather}
-
-%where $r_s$ is the schwarzschild radius of a given heavy body and is given by the equation,
-
-%\begin{gather}
-%r_s = \frac{2GM}{c^2}
-%\end{gather}
-
-%$G$, $M$, and $c$ are gravitational constant, mass of the body and speed of light in vacuum respectively.
-
-Schwarzschild Radius is a limit below which the degree of space-time curvature causes the particle to undergo irreversible gravitational collapse wherein the particle would need a speed greater than speed of light ot escape singularity.
+Schwarzschild Radius is a limit below which the degree of space-time curvature causes the particle to undergo irreversible gravitational collapse wherein the particle would need a speed greater than speed of light to escape singularity.
 
@@
 
-If supplied with initial position and velocity of a particle with negligible mass(in comparision to the central body), we can obtain the geodesics of the particle for a given range of proper time $\tau$, as it boils down to a set of eight differential equations numerically solvable by a class of Runge-Kutta methods.
+If supplied with initial position and velocity of a particle with negligible mass(in comparison to the central body), we can obtain the geodesics of the particle for a given range of proper time $\tau$, as it boils down to a set of eight differential equations numerically solvable by a class of Runge-Kutta methods.
 
-%Here is a working code describing the motion of particle revolving around a black hole of mass approximately equal to mass of the Earth.
-As the trajectory starts from a mere $130m$ from the black hole, we obtain some interesting observations.
+\begin{figure}[ht]
+	\centering
+	\includegraphics[scale=0.7]{figures/perihelion_cropped.png}
+	%\centerline{\includegraphics{ftcbuild2.pdf}}
+	\caption{Plot obtained from the above code showing the phenomenon of perihelion advance}
+	\label{fig:schwarzschild}
+\end{figure}
 
-% \begin{lstlisting}[language=Python, caption=Importing the required modules]
-% >>> import numpy as np
-% >>> import astropy.units as u
-% >>> from einsteinpy.plotting import GeodesicPlotter
-% >>> from einsteinpy.coordinates import SphericalDifferential
-% >>> from einsteinpy.bodies import Body
-% >>> from einsteinpy.geodesic import Geodesic
-% \end{lstlisting}
-
-% \begin{lstlisting}[language=Python, caption=Defining the attractor and the particle and calculating geodesics]
-% >>> Attractor = Body(name="BH", mass=6e24 * u.kg)
-% >>> init_conditions = SphericalDifferential(130*u.m, np.pi/2*u.rad, -np.pi/8*u.rad,
-% ...                                         0*u.m/u.s, 0*u.rad/u.s, 1900*u.rad/u.s)
-% >>> Particle = Body(differential=init_conditions, parent=Attractor)
-% >>> geodesic = Geodesic(body=Particle, end_lambda=0.00205, step_size=5e-8)
-
-% \end{lstlisting}
-% We can see that for each timestep, we obtain eight values : $t$, $r$, $\theta$, $\phi$, $v_t$, $v_r$, $v_\theta$ and $v_\phi$ corrosponding to coordinate time, radial distance from the centre, polar angle, azimuth angle and their respective velocities w.r.t proper time $\tau$.
-
-% Further, we plot the trajectory in 2D for vizualization purposes.
-% \begin{lstlisting}[language=Python, caption=Plotting the trajectory]
-% >>> obj = GeodesicPlotter()
-% >>> obj.plot(geodesic)
-% >>> obj.show()
-% \end{lstlisting}
-
-% \begin{figure}[h]
-% 	\centering
-% 	\includegraphics[scale=0.7]{figures/perihelion_cropped.png}
-% 	%\centerline{\includegraphics{ftcbuild2.pdf}}
-% 	\caption{Plot obtained from the above code showing the phenomenon of perihelion advance}
-% 	\label{fig:schwarzschild}
-% \end{figure}
-
-% We observe the phenomenon of perihelion advance of a particle around a heavy body due to spacetime curavture.
+We observe the phenomenon of perihelion advance of a particle around a heavy body due to spacetime curavture.
 The orbit would have been purely eliptical if plotted in accordance with Newtonian Mechanics, however, the curvature of space-time around the heavy mass shifts the orbit with each revolution.
@@
 
-\subsubsection{Kerr Metric}\label{subsubsec:kerr}
-Kerr metric is a further generalization of Schwarzschild metric and a specific case of Kerr-Newman geometry.
-A spacetime is defined as a "Kerr" spacetime as and when the massive central body posseses an angular momentum.
+\subsubsection{Kerr Metric}
+Kerr metric \citep{Kerr:1963ud} is a further generalization of Schwarzschild metric and a specific case of Kerr-Newman geometry.
+A space-time is defined as a "Kerr" space-time as and when the massive central body possesses an angular momentum.
 The corresponding metric equation which defines the space-time is,
@@
 
-% \begin{lstlisting}[language=Python, caption=Defining the Kerr Body and the particle and calculating geodesics]
-% >>> a = 0.3 * u.m
-% >>> attractor = Body(name="BH", mass=1.989e30 * u.kg, a=a)
-% >>> coordinates = BoyerLindquistDifferential(49.95e5 * u.km, np.pi / 2 * u.rad, np.pi * u.rad, a=a)
-% >>> particle = Body(differential=init_conditions, parent=attractor)
-% >>> geodesic = Geodesic(body=particle, end_lambda=33932.90, step_size=1.2, metric=Kerr)
-% \end{lstlisting}
-% As evident from the code, API across different classes are made to be as homogeneous as possible.
+\begin{figure}[ht]
+	\centering
+	\includegraphics[scale=0.5]{figures/drag.png} %replace this when the actual plot becomes available
+% 	\centerline{\includegraphics{ftcbuild2.pdf}}
+	\caption{Plot obtained from the above geodesics showing the phenomenon of frame dragging}
+	\label{fig:kerr}
+\end{figure}
 
-% As a rotating black hole drags the space-time around it, a freely falling object acquires a angular velocity around the coordinate centre, i.e centre of the black hole.
-This effect is evident from the plot obtained from the above geodesics, in the same way as obtained one in the Schwarzschild example.
-
-% \begin{figure}[h]
-% 	\centering
-% 	\includegraphics[scale=0.1]{figures/blank.jpg} %replace this when the actual plot becomes available
-	%\centerline{\includegraphics{ftcbuild2.pdf}}
-% 	\caption{Plot obtained from the above geodesics showing the phenomenon of frame dragging}
-% 	\label{fig:kerr}
-% \end{figure}
-
-\subsubsection{Kerr-Newman Metric}\label{subsubsec:kerrnewman}
-Kerr-Newman metric presents the most general case within single-body vacuum solutions of Einstein Field Equation.
+\subsubsection{Kerr-Newman Metric}
+Kerr-Newman metric \citep{Adamo:2014baa} presents the most general case within single-body vacuum solutions of Einstein Field Equation.
 It generalizes all the quantities used to describe a black hole, as affirmed by "no hair" theorem, i.e.
@@
 
-All the other symbols convey their usual meanings, as discussed in the previous two sections \ref{subsubsec:sch} and \ref{subsubsec:kerr}.
-For the sake of brevity, we would not go into the specifics of this class as the classes within \textit{Metric} module share very similar APIs as inferred in \ref{subsubsec:kerr}.
+All the other symbols convey their usual meanings, as discussed in the previous two sections Schwarzschild and Kerr Metric.
+For the sake of brevity, we would not go into the specifics of this class as the classes within \textit{Metric} module share very similar APIs as inferred in section for \texttt{Kerr}.
 
-\subsection{COORDINATES}
-The coordinates subpackage provides support for representing and transforming coordinates. Cartesian, Spherical and BoyerLindquist coordinate system can be accessed while using einsteinpy.
+\subsection{Coordinates}
+The coordinates subpackage provides support for representing and transforming coordinates.
+EinsteinPy provides support in Cartesian, Spherical and Boyer-Lindquist Coordinate systems.
+All of these are inter-convertible and can be used anytime.
+All the calculations within the module are majorly done in Spherical system.
+Numba \citep{Lam2015NumbaAL} is used to speed up the coordinate conversions for an extra performance boost.
 
-\subsection{SYMBOLIC}
-General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for cogent description of an arbitrary space-time.
+EinsteinPy is the only actively maintained Python project which supports Boyer-Lindquist Coordinate system \citep{doi:10.1063/1.1705193}.
+Boyer and Lindquist wanted to modify the Kerr metric in a form closer to the usual form of the Schwarzschild metric.
+To do this, they defined a new coordinate system(t, r, $ \theta, \phi$).
+In spherical coordinates where surfaces of constant r are spheres, but in  Boyer-Lindquist coordinates the corresponding surfaces are ellipsoids.
+
+\subsection{Symbolic}
+General Relativity required heavy mathematical formulation to derive and describe various tensors attributing to various features essential for the cogent description of an arbitrary space-time.
 We would describe the various quantities currently supported by this module while maintaining brevity.
-Each quantity has its own class, even scalars, which are treated as 0\textsuperscript{th} order tensors.
+Each quantity has its class, even scalars, which are treated as 0\textsuperscript{th} order tensors.
 
-All the mathematical quantities build upon \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} as derived classes, which is discussed in detail in \ref{subsec:BaseRelativityTensor}.
+All the mathematical quantities build upon \textit{BaseRelativityTensor} as derived classes, which is discussed in detail in section describing \textit{BaseRelativityTensor}.
 
-\subsubsection{MetricTensor}\label{subsubsec:metric}
+\subsubsection{MetricTensor}
 Metric Tensor describes the differential length elements required to measure distance in a curved(also applies to flat) space-time.
 It is a second order tensor and is fundamental to describe any space-time geometry.
-The \textit{MetricTensor} class, being inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} , inherits all its functions and also have some functions and constraints of its own.
+The \textit{MetricTensor} class, being inherited from  \textit{BaseRelativityTensor} , inherits all its functions and also have some functions and constraints of its own.
 For example, metric tensor is bound to be a second order tensor.
@@
 
-Also, the library maintains an ever expanding predefined metrics for direct use in research purposes.
+Also, the library maintains an ever expanding predefined metrics for direct use in research.
 
@@
 
-Although Christoffel Symbols are belong to class of pseudo-tensors, it is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} to maintain homogenity within the module.
-Being inherited from  \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}}, it already supports the functions of its parent class and imposes some restrictions of its own, such as order of the tensor should be 3.
+Although Christoffel Symbols belong to class of pseudo-tensors, it is inherited from \textit{BaseRelativityTensor} to maintain homogeneity within the module.
+Being inherited from \textit{BaseRelativityTensor}, it already supports the functions of its parent class and imposes some restrictions of its own, such as order of the tensor should be 3.
 
@@
 
-This quantity is the most extensive measure of curvature of a sapce-time.
-It is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} and supports all the functions of its parent class.
+This quantity is the most extensive measure of curvature of a space-time. It is inherited from \textit{BaseRelativityTensor} and supports all the functions of its parent class.
 
@@
 
-This tensor is used in solving Eintein's  equation and basically contraction of Riemann Curvature Tensor.
-It is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} and supports all the functions of its parent class.
+This tensor is used in solving Einstein's  equation and is basically contraction of Riemann Curvature Tensor.
+It is inherited from \textit{BaseRelativityTensor} and supports all the functions of its parent class.
 
@@
 It is a scalar quantity obtained by contracting a given Ricci Tensor.
-It is inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}} and supports all the functions of its parent class.
+It is inherited from \textit{BaseRelativityTensor} and supports all the functions of its parent class.
 Being a scalar quantity, it does not support \texttt{change\_config} unlike other tensors as discussed above.
@@
 
-Here is a sample code snippet, using the above discussed Classes
+Here is a sample code snippet, using the above discussed classes :
 
@@
 In congruence to theoretical results, the code outputs a constant negetive scalar curvature for Anti De-Sitter spacetime.
-All the above discussed classes are called in this snippet as \hyperref[subsubsec:riccitensor]{\textit{RicciTensor}} internally calls \hyperref[subsubsec:riemann]{\textit{RiemannCurvatureTensor}}, which in turn calls \hyperref[subsubsec:chl]{\textit{ChristoffelSymbols}}.
+All the above discussed classes are called in this snippet as \textit{RicciTensor} internally calls \textit{RiemannCurvatureTensor}, which in turn calls \textit{ChristoffelSymbols}.
 
@@
 Some other quantities currently supported are listed below.
-The quantities are all inherited from \hyperref[subsec:BaseRelativityTensor]{\textit{BaseRelativityTensor}}, and a similar API (same as that of discussed above) has been implemented to maintain compatiblity and homegenity.
+The quantities are all inherited from \textit{BaseRelativityTensor}, and a similar API (same as that of discussed above) has been implemented to maintain compatiblity and homogeneity.
 The class names denote usual quantities relevant to General Relativity.
@@
 
-\subsection{HYPERSURFACE}
+\subsection{Hypersurface}
 This module provides basic computational functions which are essential for modelling the space-like hypersurface for any space-time geometry.
-Currently module has implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities.
+Currently, the module has an implementation for Schwarzschild geometry with conversion functions from Schwarzschild coordinates to 3-D spherical coordinates and some plotting utilities.
 The whole module is expected to extend for providing a super-class for implementations related to gravitational lensing simulations and numerical calculations of null geodesics on hypersurfaces and deviation angles for systems which are relevant to relativistic astrophysical problems.
@@
 \end{lstlisting}
+\begin{figure}[ht]
+	\centering
+	\includegraphics[scale=0.5]{figures/hypersurface_surface.png} %replace this when the actual plot becomes available
+% 	\centerline{\includegraphics{ftcbuild2.pdf}}
+	\caption{Schwarzschild embedding}
+	\label{fig:hypersurface}
+\end{figure}
 
-\subsection{PLOTTING}
+\subsection{Plotting}
 The plotting ecosystem in EinsteinPy has two back-ends for two type of users.
-A static, matplotlib based plotter for publication quality plots and an interactive plotly based plotter for analysis and interpretation.
+A static, matplotlib based plotter for publication-quality plots and an interactive plotly based plotter for analysis and interpretation.
 \\
-The plotting module is specifically designed keeping in mind the variety of IDEs and tools people working with Python use, for example python scripts, jupyter notebooks, spyder, pycharm etc.
+The plotting module is specifically designed keeping in mind the variety of IDEs and tools people working with Python use, for example, python scripts, jupyter notebooks, spyder, pycharm etc.
 As plotly plots need JavasScript to render plots, it becomes difficult for the first time user to decide which backend to use.
-\texttt{StaticGeodesicPlotter} and \texttt{InteractiveGeodesicPlotter} undergo an internal switching depending on the environment variables and the appropriate environment aware plot is shown to the user for a better user experience and interface.\\
+\texttt{StaticGeodesicPlotter} and \texttt{InteractiveGeodesicPlotter} undergo an internal switching depending on the environment variables and the appropriate environment aware plot is shown to the user for better user experience and interface.\\
 The plotting module throughout the applications follow a very consistent API. \begin{lstlisting}[language=Python, caption=Plotting Module API]
@@
 
-\section{INFRASTRUCTURE} \label{sec:infra}
-\subsection{ Testing} \label{subsec:testing}
+\subsection{Rays}
+The rays module of EinsteinPy tries to focus on how light behaves around heavy mass objects and the 
+The plotting module throughout the applications follow a very consistent API. \begin{lstlisting}[language=Python, caption=Plotting Module API]
+>>> data = Plotter()
+>>> data.plot()
+>>> data.show()
+\end{lstlisting}
+
+\section{Infrastructure} \label{sec:infra}
+\subsection{Testing} \label{subsec:testing}
 The EinsteinPy Project maintains a very high bar in accepting changes and introducing new features.
 Every patch of code that is accepted in the codebase through any pull request has to be well tested using some unit tests unless given an exception after discussion with both the lead developers.
-Currently the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94\% and we hope to improve it in the future.
-The 100\% code coverage for this software at this level is not possible because of lack of accurate data to test the code against.
+Currently, the coverage of unit tests, which means the total fraction of codebase run by at least one unit test is 94\% and we hope to improve it in the future.
+The 100\% code coverage for this software at this level is not possible because of the lack of accurate data to test the code against.
 We deliberately leave some parts of the codebase out of the testing loop because testing those modules is not possible with the current knowledge level and expertise.
-However, 94\% code coverage is good enough when we consider other packages in scientific Python community who face the similar problem.
+However, 94\% code coverage is good enough when we consider other packages in the scientific Python community who face a similar problem.
 
@@
 All the contributions trigger these free services (Codecov, CircleCI, Appveyor, GitHub Actions, Codefactor, Codeclimate, Hound, WIP) which are integrated with GitHub repository.
-All the pull requests are checked for code linting by a pep8speaks bot, which suggests the lines of code which violate the PEP8 standard to the contributor in a human readable way.
-All these services run on three types of operating systems (Windows, MacOS and Linux).
+All the pull requests are checked for code linting by a pep8speaks bot, which suggests the lines of code which violate the PEP8 standard to the contributor in a human-readable way.
+All these services run on three types of operating systems (Windows, macOS and Linux).
 The unit tests run on various versions of Python.
-They test the documentation builds, test coverage, check whether the pull request author has indicated that it is a work in progress (WIP).They also run several code linting checks which further triggers the unit test build.
+They test the documentation builds, test coverage, check whether the pull request author has indicated that it is a work in progress (WIP).
+They also run several code linting checks which further triggers the unit test build.
 
@@
 The EinsteinPy Project strives to provide high quality, up-to-date and accurate documentation of the software.
-The documentation is highly approachable with easy and intuitive user interface.
-The documentation is self-updating with every change in the codebase, and is rendered automatically from the docstrings written for each function and classes.
-Along with the main API, new example codes for different functionalities is added to the repository frequently in the form of jupyter notebooks.
+The documentation is highly approachable with an easy and intuitive user interface.
+The documentation is self-updating with every change in the codebase and is rendered automatically from the docstrings written for each function and classes.
+Along with the main API, new example codes for different functionalities are added to the repository frequently in the form of jupyter notebooks.
 Many sections like User Guide and Developer Guide has been written for easy on-boarding of new users and contributors.
 
-\section{COMMUNITY} \label{sec:COMMUNITY}
-EinsteinPy is being developed as an open source community inside the wide and diverse general scientific python community.
+\section{Community} \label{sec:COMMUNITY}
+EinsteinPy is being developed as an open-source community inside the wide and diverse general scientific python community.
 Our code is freely available, and we have seen a lot of people contributing and joining us since over the past year.
-We touched the landmark of 30 members recently.
+We touched the landmark of 50 contributors recently.
 EinsteinPy is dedicated to problems arising in General Relativity and gravitational physics as well as encouraging open source development.
 EinsteinPy has benefited greatly from summer of code schemes.
-Last year EinsteinPy participated in the ESA Summer of Code In Space (SOCIS).
-This program is inspired by Google Summer Of Code (GSOC) and aims to raise the awareness of open source projects related to space, promote the European Space Agency.
+In 2019 EinsteinPy participated in the ESA Summer of Code In Space (SOCIS).
+This program is inspired by the Google Summer Of Code (GSoC) and aims to raise the awareness of open source projects related to space, promote the European Space Agency.
 The symbolic module in EinsteinPy project was developed during this program.
 
-\section{FUTURE} \label{sec:FUTURE}
+In 2020, EinsteinPy is selected as a sub-organization in Google Summer of Code under OpenAstronomy Umbrella.
+
+\section{Future} \label{sec:FUTURE}
 We intend to add more functionalities to our project, some of which are, 
 \begin{itemize}
-\item \texttt Support for null-geodesics in different geometries, . 
-\item \texttt Relativistic hydrodynamics
-\item \texttt Adaptive Mesh Refinement 
-\item \texttt Providing numerical solutions to Einstein’s equations for arbitrarily complex matter distribution.
+\item Support for null-geodesics in different geometries, . 
+\item Relativistic hydrodynamics
+\item Adaptive Mesh Refinement 
+\item Providing numerical solutions to Einstein’s equations for arbitrarily complex matter distribution.
 \end{itemize}
 
-We have an open community where suggestions from people to add functionalities are welcome. We wish to be as helpful as possible to people using EinsteinPy in.
+We have an open community where we welcome suggestions from people to add functionalities/features and everyone can report bugs and issues.
+We wish to be as helpful as possible to people using EinsteinPy in their research.
 
-\acknowledgments
+\section{Conclusions}
 
+\begin{acknowledgements}
       We thank all the people that have made EinsteinPy what it is today.  
@@
 We would like to thank the awesome poliastro \citep{juan_luis_cano_rodriguez_2019_3588160} for always motivating us and for being the first sponsor for the project.
-We would also like to thank our host university, Indian institute of Technology, Mandi who provided us with significant support and have our deepest thanks.
-We would specially like to thank Prof.Abhay Ashtekar for his motivational email and  Prof. Timothy A. Gonsalves for his constant motivation and support.
+We would also like to thank our host university, Indian Institute of Technology, Mandi who provided us with significant support and have our deepest thanks.
+We would especially like to thank Prof.Abhay Ashtekar for his motivational email and  Prof. Timothy A. Gonsalves for his constant motivation and support.
 Lastly, we thank all our contributors who contributed selflessly for building this amazing software called EinsteinPy.
 
-%% To help institutions obtain information on the effectiveness of their 
-%% telescopes the AAS Journals has created a group of keywords for telescope 
-%% facilities.
+\end{acknowledgements}
+
+% WARNING
+%-------------------------------------------------------------------
+% Please note that we have included the references to the file aa.dem in
+% order to compile it, but we ask you to:
 %
-%% Following the acknowledgments section, use the following syntax and the
-%% \facility{} or \facilities{} macros to list the keywords of facilities used 
-%% in the research for the paper.  Each keyword is check against the master 
-%% list during copy editing.  Individual instruments can be provided in 
-%% parentheses, after the keyword, but they are not verified.
+% - use BibTeX with the regular commands:
+%   \bibliographystyle{aa} % style aa.bst
+%   \bibliography{Yourfile} % your references Yourfile.bib
+%
+% - join the .bib files when you upload your source files
+%-------------------------------------------------------------------
 
-%% Similar to \facility{}, there is the optional \software command to allow 
-%% authors a place to specify which programs were used during the creation of 
-%% the manuscript. Authors should list each code and include either a
-%% citation or url to the code inside ()s when available.
+\bibliographystyle{aa}
+\bibliography{bibliography.bib}
 
-\software{astropy \citep{astropy:2013} \citep{astropy:2018},  
-          Numpy \citep{numpy}, 
-          scipy \citep{2019arXiv190710121V},
-          numba \citep{Lam2015NumbaAL},
-          matplotlib \citep{matplotlib}
-          }
-
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc. The
-%% Figure and Table counter will not reset.
-
-% \appendix
-% \section{Appendix information}
-
-%% For this sample we use BibTeX plus aasjournals.bst to generate the
-%% the bibliography. The sample63.bib file was populated from ADS. To
-%% get the citations to show in the compiled file do the following:
-%%
-%% pdflatex sample63.tex
-%% bibtext sample63
-%% pdflatex sample63.tex
-%% pdflatex sample63.tex
-
-\bibliography{bibliography}{}
-\bibliographystyle{aasjournal}
-
-%% This command is needed to show the entire author+affiliation list when
-%% the collaboration and author truncation commands are used.  It has to
-%% go at the end of the manuscript.
-%\allauthors
-
-%% Include this line if you are using the \added, \replaced, \deleted
-%% commands to see a summary list of all changes at the end of the article.
-%\listofchanges
 \end{document}

### 2020-05-04 paper.tex
Add author

@@
 \and
-Priyanshu Khandelwal\inst{\ref{inst:gatech}}
+Priyanshu Khandelwal\inst{\ref{inst:iitm}}
 \and
@@
 Jialin Ma\inst{\ref{inst:gatech}}
+\and
+Gim Seng Ng\inst{\ref{inst:trinity}}
+\and
+Pratyush Kerhalkar\inst{\ref{inst:elecmani}}
+\and
+Hrishikesh Sudam Sarode\inst{\ref{inst:iitm}}
+\and
+Rishi Sharma\inst{\ref{inst:iitm}}
+\and
+Manvi Gupta\inst{\ref{inst:iitm}}
+\and
+Divya Gupta\inst{\ref{inst:iitm}}
+\and
+Tushar Tyagi\inst{\ref{inst:iitm}}
+\and
+Tanmay Rustagi\inst{\ref{inst:iitm}}
+\and
+Varun Singh\inst{\ref{inst:iitm}}
+\and
+Saurabh Bansal\inst{\ref{inst:iitm}}
+\and
+Naman Tayal\inst{\ref{inst:iitm}}
+\and
+Abhijeet Manhas\inst{\ref{inst:iitm}}
+\and
+Raphael Reyna\inst{\ref{inst:calpoly}}
+\and
+Gaurav Kumar\inst{\ref{inst:iitm}}
+\and
+Govind Dixit\inst{\ref{inst:iiitl}}
+\and
+Ratin Kumar\inst{\ref{inst:nitk}}
+\and
+Sashank Mishra\inst{\ref{inst:iiita}}
+\and
+Alpesh Jamgade\inst{\ref{inst:bharath}}
+\and
+Raahul Singh\inst{\ref{inst:sri}}
+\and
+Rohit Sanjay\inst{\ref{inst:manipal}}
+\and
+Khalid Shaikh\inst{\ref{inst:yadav}}
+\and
+Bhavam Vidyarthi\inst{\ref{inst:manipal}}
+\and
+Shamanth R Nayak K\inst{\ref{inst:manipalit}}
+\and
+Vineet Gandham\inst{\ref{inst:manipalcs}}
+\and
+Nimesh Vashistha\inst{\ref{inst:manipal}}
+\and
+Arnav Das\inst{\ref{inst:hira}}
+\and
+Saurabh\inst{\ref{inst:du}}
+\and
+Shreyas Kalvankar\inst{\ref{inst:wagh}}
+\and
+Ganesh Tarone\inst{\ref{inst:vish}}
+\and
+Atul Mangat\inst{\ref{inst:iitree}}
 }
@@
   \and
+   School of Mathematics and Hamilton Mathematics Institute, Trinity College Dublin, Dublin 2, Ireland  
+   \label{inst:trinity} 
+    \and
    School of Physical Sciences, National Institute of Science Education and Research, Jatni, Khurdha, Odisha, India
    \label{inst:niser}
+   \and
+   Department of Electronics and Communication Engineering, Manipal Institute of Technology, India
+   \label{inst:elecmani}
+   \and
+   California State Polytechnic University, Pomona, USA
+   \label{inst:calpoly}
+   \and
+   Department of Information Technology, Indian Institute of Information Technology Lucknow, India
+   \label{inst:iiitl}
+   \and
+   National Institute of Technology Kurukshetra, India
+   \label{inst:nitk}
+   \and
+   Department of Information Technology, Indian Institute of Information Technology Allahabad, India
+   \label{inst:iiita} 
+   \and
+   Department of Mathematics, Bharath Institute of Higher Education and Research, Chennai, India
+   \label{inst:bharath}  
+   \and
+   Indian Institute of Information Technology, Sri City, India
+   \label{inst:sri} 
+   \and
+   Department of Electronics and Communication Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
+   \label{inst:manipal}
+   \and
+   Department of Computer Engineering, Yadavrao Taskgaonkar Institute of Engineering and Technology, Mumbai University, Mumbai, Maharashtra, India
+   \label{inst:yadav}
+   \and
+   Department of Information and Communication Technology Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
+   \label{inst:manipalit}
+   \and
+   Department of Computer Science and Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
+   \label{inst:manipalcs}
+   \and
+   Hiranandani Foundation, Powai, Mumbai, Maharashtra, India
+   \label{inst:hira}
+   \and
+   Dyal Singh College, University of Delhi, New Delhi, India  
+   \label{inst:du} 
+   \and
+   K. K. Wagh Institute of Engineering Education and Research, Nashik, Maharashtra, India  
+   \label{inst:wagh}
+    \and
+   Department of Computer Engineering,Vishwakarma Institute of Technology,Pune, Maharashtra, India  
+   \label{inst:vish} 
+   \and
+  Department of Electrical Engineering, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
+  \label{inst:iitree}
 }

### 2020-05-04 paper.tex
Add authors and rays

@@
 Atul Mangat\inst{\ref{inst:iitree}}
+\and
+Suyog Garg\inst{\ref{inst:iiitdm}}
+\and
+Bibek Gautam\inst{\ref{inst:xav}}
+\and
+Sitara Srinivasan\inst{\ref{inst:nax}}
+\and
+Aayush Gautam\inst{\ref{inst:tribhu}}
+\and
+Swaastick Kumar Singh\inst{\ref{inst:amity}}
+\and
+Suyash Salampuria\inst{\ref{inst:iitrce}}
+\and
+Zac Yauney\inst{\ref{inst:bri}}
 }
@@
    \and
-   Dyal Singh College, University of Delhi, New Delhi, India  
+   Department of Physics, Dyal Singh College, University of Delhi, New Delhi, India  
    \label{inst:du} 
@@
   \label{inst:iitree}
+  \and
+  Indian Institute of Information Technology, Design and Manufacturing, Kancheepuram, Off Vandalur-Kelambakkam Road, Melakottaiyur, Chennai, Tamil Nadu, India 600127
+  \label{inst:iiitdm}
+  \and
+  Naxxatra Sciences and Collaborative Research, Bangalore, Karnataka, India 
+  \label{inst:nax}
+  \and
+  St. Xavier's College, Maitighar, Kathmandu, Nepal
+  \label{inst:xav}
+  \and
+  Amity University Kolkata, West Bengal, India 
+  \label{inst:amity}
+  \and
+  Department of Physics, Birendra Multiple Campus, Tribhuwan University, Kathmandu, Nepal
+  \label{inst:tribhu}
+  \and
+  Department of Chemical Engineering, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
+  \label{inst:iitrce}
+  \and
+  Brigham Young University, Provo, UT 84602, United States
+  \label{inst:bri}
 }
@@
 The rays module of EinsteinPy tries to focus on how light behaves around heavy mass objects and the 
-The plotting module throughout the applications follow a very consistent API. \begin{lstlisting}[language=Python, caption=Plotting Module API]
->>> data = Plotter()
->>> data.plot()
->>> data.show()
-\end{lstlisting}
+The plotting module throughout the applications follow a very consistent API. 
+The major functionality this module provides is the utility functions for carrying out shadow related computations for different black hole spacetime.
+The module has natural data types to efficiently store impact parameters and use them in further computations related to wavelength shifts, turning point etc.
+The specific assumptions about the accretion process and the emission mechanisms are in accordance with that given in \citep{Bambi_2013}.
+The module also provide functionalities related to intensities of blue shifted and red shifted rays above and below the critical impact parameters.
+For mathematical formalism of the above computations refer to the \citep{Bambi_2013} and \citep{Shaikh_2018}.
 
@@
 \section{Conclusions}
+The paper outlines the package EinsteinPy, a community and open effort for solving problems in general relativity. We discussed all the modules of the library:
+\begin{itemize}
+\item Metric Module
+\item Coordinates Module
+\item Plotting Module
+\item Symbolic Module
+\item Rays Module
+\item Hypersurface Module
+\end{itemize}
+
+We discuss the basic development practices that EinsteinPy follows, and the future goals.
 
@@
 We would also like to thank our host university, Indian Institute of Technology, Mandi who provided us with significant support and have our deepest thanks.
-We would especially like to thank Prof.Abhay Ashtekar for his motivational email and  Prof. Timothy A. Gonsalves for his constant motivation and support.
+We would especially like to thank Prof.Abhay Ashtekar for his motivational email and  Prof.
+Timothy A.
+Gonsalves for his constant motivation and support.
+We would also like to thank Prof.
+Arnav Bhavsar for his constant support.
 Lastly, we thank all our contributors who contributed selflessly for building this amazing software called EinsteinPy.

### 2020-05-18 paper.tex
Last Iteration

@@
 Zac Yauney\inst{\ref{inst:bri}}
+\and
+Nihar Gupte\inst{\ref{inst:uf}}
+\and
+Gagan Shenoy\inst{\ref{inst:manipalcs}}
+\and
+Micky Yun Chan\inst{\ref{inst:lat}}
 }
    \institute{
-  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India
+  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India 175005
   \label{inst:iitm}
@@
   \label{inst:bri}
+  \and
+  Department of Physics, University of Florida, Gainesville, FL, USA
+  \label{inst:uf}
+  \and
+  Latvia University of Life Sciences and Technologies, Lielā iela 2, Jelgava, LV-3001, Latvia
+  \label{inst:lat}
 }
@@
 \subsection{Rays}
-The rays module of EinsteinPy tries to focus on how light behaves around heavy mass objects and the 
-The plotting module throughout the applications follow a very consistent API. 
-The major functionality this module provides is the utility functions for carrying out shadow related computations for different black hole spacetime.
+The rays module of EinsteinPy tries to focus on how light behaves around heavy mass object.
+The major functionality this module provides is the utility functions for carrying out shadow related computations for different black hole spacetimes.
 The module has natural data types to efficiently store impact parameters and use them in further computations related to wavelength shifts, turning point etc.
@@
 For mathematical formalism of the above computations refer to the \citep{Bambi_2013} and \citep{Shaikh_2018}.
+
+This module is under heave developement since past February 2020, and we expect significant contributions to this module thanks to Google Summer of Code 2020.
 

### 2020-05-18 paper_two.tex
Add a refree version and a print version

--- 2020-05-18 paper.tex
@@
 %
-\documentclass[onecolumn]{aa}  
+\documentclass[refree]{aa}  
 %\documentclass[bibyear]{aa}
@@
 \and
-Pratyush Kerhalkar\inst{\ref{inst:elecmani}}
+Pratyush Kerhalkar\inst{\ref{inst:manipal}}
 \and
@@
 \and
-Shamanth R Nayak K\inst{\ref{inst:manipalit}}
+Shamanth R Nayak K\inst{\ref{inst:manipal}}
 \and
-Vineet Gandham\inst{\ref{inst:manipalcs}}
+Vineet Gandham\inst{\ref{inst:manipal}}
 \and
@@
 \and
-Atul Mangat\inst{\ref{inst:iitree}}
+Atul Mangat\inst{\ref{inst:iitr}}
 \and
@@
 \and
-Suyash Salampuria\inst{\ref{inst:iitrce}}
+Suyash Salampuria\inst{\ref{inst:iitr}}
 \and
@@
 \and
-Gagan Shenoy\inst{\ref{inst:manipalcs}}
+Gagan Shenoy\inst{\ref{inst:manipal}}
 \and
@@
    \institute{
-  School of Computing and Electrical Engineering, Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India 175005
+  Indian Institute of Technology Mandi, Mandi, Himachal Pradesh, India 175005
   \label{inst:iitm}
     \and
-  Department of Earth Sciences, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
+  Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
   \label{inst:iitr}
@@
    \and
-   Department of Electronics and Communication Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
-   \label{inst:manipal}
-   \and
-   Department of Computer Engineering, Yadavrao Taskgaonkar Institute of Engineering and Technology, Mumbai University, Mumbai, Maharashtra, India
+   Yadavrao Taskgaonkar Institute of Engineering and Technology, Mumbai University, Mumbai, Maharashtra, India
    \label{inst:yadav}
    \and
-   Department of Information and Communication Technology Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
-   \label{inst:manipalit}
-   \and
-   Department of Computer Science and Engineering, Manipal Institute of Technology, Manipal, Karnataka, India
-   \label{inst:manipalcs}
+   Manipal Institute of Technology, Manipal, Karnataka, India
+   \label{inst:manipal}
    \and
@@
   \and
-  Department of Electrical Engineering, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
-  \label{inst:iitree}
-  \and
-  Indian Institute of Information Technology, Design and Manufacturing, Kancheepuram, Off Vandalur-Kelambakkam Road, Melakottaiyur, Chennai, Tamil Nadu, India 600127
+  Indian Institute of Information Technology, Design and Manufacturing, Chennai, Tamil Nadu, India 600127
   \label{inst:iiitdm}
@@
   \label{inst:tribhu}
-  \and
-  Department of Chemical Engineering, Indian Institute of Technology Roorkee, Roorkee, Uttarakhand, India
-  \label{inst:iitrce}
   \and
@@
 Specifically, a lot of recent studies show that the use of Python in Astrophysics and general physics has increased exponentially.
-Many great frameworks came as Python packages which provide a very high level of abstraction over the dirty nitty-gritty of complex algorithms and provide an easy to use interface and pleasing user experience.
-One such example is Keras - a framework for deep learning which has made deep learning so easy that a person with zero programming knowledge can also train a neural network classifier.
-This example demonstrates the power of abstraction which is achievable in Python.
-The aim of the EinsteinPy is no different and is developed keeping in mind the state of a theoretical gravitational physicist with little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.
+We aim to provide a very high level of abstraction, an easy to use interface and pleasing user experience.
+EinsteinPy is developed keeping in mind the state of a theoretical gravitational physicist with little or no background in computer programming and trying to work in the field of numerical relativity or trying to use simulations in their research.
 Currently, EinsteinPy supports simulation of time-like and null geodesics and calculates trajectories in different background geometries some of which are Schwarzschild, Kerr, and KerrNewmann along with coordinate inter-conversion pipeline.
@@
 One of the unique features of EinsteinPy is a sufficiently developed symbolic tensor manipulation utilities which are a great tool in itself for teaching yourself tensor algebra which for many beginner students can be overwhelmingly tricky.
-EinsteinPy also provides few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.
-The current version of the library is in a state that can be used by any serious student of general relativity trying to get the essence of this beautiful subject but is somewhere lost in the heavy mathematical formalism of the subject.
-EinsteinPy provides such students to really see through the equations and visualize what's really happening.}
+EinsteinPy also provides few utility functions for hypersurface embedding of Schwarzschild spacetime which further will be extended to model gravitational lensing simulation.}
 
